### 2016-12-04 Const_design_TVT.tex
Pre-release version

%% LyX 2.1.5 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[letterpaper,english,10pt]{article}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{array}
\usepackage{float}
\usepackage{units}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[dvips]{graphicx}
\usepackage{setspace}
\usepackage{wasysym}
\usepackage{nomencl}
% the following is useful when we have the old nomencl.sty package
\providecommand{\printnomenclature}{\printglossary}
\providecommand{\makenomenclature}{\makeglossary}
\makenomenclature
\doublespacing

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
\special{papersize=\the\paperwidth,\the\paperheight}

%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}
%% A simple dot to overcome graphicx limitations
\newcommand{\lyxdot}{.}

\floatstyle{ruled}
\newfloat{algorithm}{tbp}{loa}
\providecommand{\algorithmname}{Algorithm}
\floatname{algorithm}{\protect\algorithmname}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{babel}

\usepackage{cite}
\usepackage{color}
\usepackage{bigdelim,multirow}
\usepackage{tikz}
\usetikzlibrary[arrows,calc,decorations.pathmorphing,backgrounds,positioning,fit,petri,shapes,decorations.markings]
\usepackage{pgfplots}
\usepackage{babel}
\usepackage{multirow}

\usepackage{algpseudocode}
\usepackage{algorithm}

\usepackage{nicefrac}

\usepackage{setspace}

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

%\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
%\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
%\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

% unnumbered footnote
\makeatletter
\newcommand{\unfootnote}[1]{
  \renewcommand{\@makefnmark}{}
  \footnotetext{#1}
  \renewcommand{\@makefnmark}{\mbox{$^{\@thefnmark}$}}
}
\makeatother

\newcommand{\jj}{\operatorname{j}}      % imaginary unit

\makeatother

\usepackage{babel}
\begin{document}

\title{Design of Adaptive Constellations and Error Protection Coding for
Wireless Network Coding in 5-node Butterfly Networks}

\author{Pavel Prochazka, Tomas Uricar, David Halls and Jan Sykora}

\maketitle
{\footnotesize{}The corresponding author D. Halls is with the Toshiba
-- Telecommunication Research Laboratory (email: david.halls@toshiba-trel.com).
Pavel Prochazka, Tomas Uricar and Jan Sykora were with the Czech Technical
University in Prague, Czech Republic (e-mail: \textbackslash{}\{prochp10,
uricatom, Jan.Sykora\textbackslash{}\}@fel.cvut.cz). }{\footnotesize \par}

\thispagestyle{empty}

\pagebreak{}
\begin{abstract}
In this paper we focus on the design of a reliable communication scheme
for generic 5-node Wireless Butterfly Networks (WBN). Since the WBN
represents a natural extension of the basic 2-way relay communication
channel, we follow the paradigm of \emph{Wireless Physical Layer Network
Coding} (WNC) and we show that the design of novel adaptive constellations\emph{
}is desirable to exploit the promising performance of WNC in WBN.
We introduce a \emph{systematic constellation design} algorithm and
we show that the proposed constellations are capable of outperforming
conventional point-to-point modulations in WBN over the whole range
of channel SNRs. To further support the applicability of the proposed
constellations in a practical system, we integrate a simple binary
channel coding scheme, providing a robust \emph{adaptive modulation
and coding scheme} for relaying in symmetric WBNs with arbitrary channel
conditions.
\end{abstract}

\subsubsection*{Keywords:}Wireless Network Coding, Butterfly Network, Relaying, Superposition
Coding and Modulation

\pagebreak
\nomenclature{WBN}{Wireless Butterfly Network}\nomenclature{WNC}{Wireless Network
Coding}\nomenclature{HW}{Hardware}\nomenclature{SNR}{Signal to Noise
Ratio}\nomenclature{SC}{Superposition Coding}\nomenclature{HSI}{Hierarchical Side
Information}\nomenclature{DEM}{Demodulator}\nomenclature{IC}{Interference
Cancellation}\nomenclature{MA}{Multiple Access}\nomenclature{AWGN}{Additive White Gaussian
Channel}\nomenclature{ASK}{Amplitude Shift Keying}\nomenclature{QAM}{Quadrature Amplitude
Modulation}\nomenclature{SER}{Symbol Error Rate}\nomenclature{FER}{Frame Error
Rate}\nomenclature{SDR}{Software Defined Radio}\nomenclature{USRP}{Universal Software Radio
Peripherals}\nomenclature{UHD}{USRP Hardware Driver }\nomenclature{CP}{Cyclic
Prefix}\nomenclature{ODFD}{Orthogonal Frequency Division Multiplexing}\nomenclature{DC}{Direct
Current}\nomenclature{MIMO}{Multiple Input Multiple Output}\nomenclature{QPSK}{Quadrature Phase
Shift Keying}\nomenclature{UDP}{User Datagram Protocol}\nomenclature{BC}{Broadcast
Channel}\nomenclature{MAC}{Multiple Access Channel}\nomenclature{SODEM}{Soft Output Demodulator}\nomenclature{CC}{Constellation
Constrained}%\settowidth{\nomlabelwidth}{AWGN} 
\printnomenclature{} 
\pagebreak

\section{Introduction}

The invention of Wireless Network Coding\emph{ }(WNC) has indeed provided
a means for a significant enhancement in wireless system performance
\cite{Popovski-Yomo_2007a,Nazer-Gastpar_2011-IEEE-P,Zhang-Liew-Lu_2012}.
However, WNC processing has also revealed several non-trivial research
problems which do not have counterparts in conventional point-to-point
or multi-user systems, like the sensitivity to channel parameterization
\cite{Koike-Popovski-Tarokh_2008,Liu-Tao-Xu_2011-ICC,Yasami-Razi-Abedi_2011,Uricar-Sykora_2011}
or challenging multi-source transmission synchronization \cite{Zhang-Liew-Lam_2006b-ITW,Rosetto-Zorzi_2009-SPAWC,Huang-Wang-Song-Guo-Jamalipour_2012-IEEE-T-WC}.
Furthermore, the specific characteristics of multi-node WNC systems
can call also for novel constellation design approaches (see e.g.
\cite{Uricar-Sykora_2011,Prochazka-Uricar-Halls-Sykora_2015-ICC}).

In WNC the transmitted information symbols are allowed to interact
directly in the constellation space, inducing a specific set of requirements
on the constellations' properties and characteristics (see e.g. \cite{Uricar-Sykora_2011,Prochazka-Uricar-Halls-Sykora_2015-ICC}).
Generally we can declare \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
that any constellation suitable for the specific nature of WNC processing
should be able to form\emph{ a superimposed constellation} with an
appropriate structure at all receiving nodes (allowing direct decoding
of specific WNC functions of user data from the received non-orthogonal
signals \cite{Nazer-Gastpar_2008-ISIT,Sykora-Burr_2011-TVT}) and
simultaneously it should be able to exploit the \emph{broadcast nature
}of wireless channels (allowing a reduction in the consumption of
channel resources in the system \cite{Popovski-Yomo_2007a}). Since
both of these properties hinge on the actual SNR conditions in the
system, the constellation design itself can become a relatively challenging
task.
\begin{figure}
\centering{}\includegraphics[width=0.6\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_v4}
\caption{Symmetric WBN model with half-duplex constraint and 2-phase communication.\label{fig:CTUpp_Information_flows}}
\end{figure}

One of the first attempts to design a suitable multi-source constellation
for communication in a multi-node WNC system was introduced in our
previous work \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}, where
the \emph{adaptive 2-source constellations} for WNC-based communication
in a 5-node \emph{Wireless Butterfly Network} (WBN) were developed.
However, the results presented in \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
are limited to an uncoded system, which significantly limits its practical
applicability.

In this paper we extend the communication scheme from \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
by appending appropriate \emph{error protection coding} to the system,
resulting in a practical channel-coded adaptive communication scheme
for WBN. We provide the following results and contributions:
\begin{enumerate}
\item We summarize the \emph{systematic constellation design algorithm}
from \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC} and we provide
additional numerical results analysing its promising performance.
\item We revise and extend the results discussing the \emph{adaptive capabilities
of the constellations, }including \emph{the constellation mapping
regions} for adaptive WBN relaying\emph{.}
\item We validate the proposed design in a \emph{real-world HW setup}, including
the HW evaluation of adaptive system performance.
\item We show how the \emph{channel coding} can be integrated into the proposed
constellation design, including the analysis of proper source transmission
rates.
\item We evaluate numerically the performance of the resulting \emph{adaptive
modulation and coding} scheme for a wide range of channel conditions
in the WBN.
\item We show that the proposed design is viable even if the real-world
conditions induce some deviation from the assumed system model.
\end{enumerate}
The rest of the paper is organized as follows. The system model, including
all necessary definitions and details about WNC processing in WBNs
is summarized in Section~\ref{sec:CTUpp_SystemModel}. A systematic
\emph{constellation design algorithm} for WBNs is revised in Section~\ref{sec:CTUpp_Euclidean-Distance-based-Constel}.
The performance analysis of the proposed constellations (including
the HW evaluation) in an uncoded system is available in Section~\ref{sec:CTUpp_Performance-Analysis-Uncoded}.
Section~\ref{sec:CTUpp_Adaptive-Constellation-Design} discusses
an adaptive constellation design and Section~\ref{sec:CTUpp_Channel-Coding}
introduces the channel coding extension to the system. The performance
of the novel adaptive modulation and coding scheme is analyzed in
Section~\ref{sec:CTUpp_Performance-Analysis-Coded}, including a
simple robustness analyzis. Concluding remarks are summarized in Section~\ref{sec:CTUpp_DiscussionConclusions-etc}.

\section{WNC Relaying in Wireless Butterfly Network\label{sec:CTUpp_SystemModel}}

We assume a \emph{symmetric} WBN model \cite{Uricar-Qian-Sykora-Mow_2013-WCNC,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}
with a half-duplex constraint (Fig. \ref{fig:CTUpp_Information_flows}).
An example practical scenario complying with the WBN model is a communication
among vehicles and road-side infrastructure nodes for traffic information
exchange on a bidirectional highway within two time slots \cite{Ho-Liew-Lu}.
The direct channels between the intended source$\rightarrow$destination
pairs are not available in WBN and thus the help of the intermediate
relay node is necessary to enable end-to-end communication. Please
note that in this paper we do not limit our attention to the above
mentioned special example of a high-speed, vehicle-based WBN.

\subsection{Relaying Strategy}

An information-theoretic relaying strategy (based on Superposition
Coding (SC) \cite{Cover-Thomas_ElemInfTheory,Han-Kobayashi_1981,Shende-Rajan-2012-NCC,Popovski-Carvalho_2008})
for WBNs was proposed in \cite{Uricar-Qian-Sykora-Mow_2013-WCNC,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}.
The fundamental idea of the SC-approach is to split each data symbol
$\mathbf{d}_{i}$ at source $i\in\left\{ A,B\right\} $ into the \emph{basic
part} $\mathbf{d}_{i}^{b}=[d_{i,0}^{b},\dots,d_{i,N_{b}-1}^{b}]$
and the \emph{superposed part} $\mathbf{d}_{i}^{s}=[d_{i,0}^{s},\dots,d_{i,N_{s}-1}^{s}]$,
$d_{i,n}^{b},\,d_{i,n}^{s}\in\left\{ 0,1\right\} $, and then process
each of the resulting data streams separately throughout the system
(see Fig. \ref{fig:CTUpp_Information_flows}). While the basic part
represents a \textquotedbl{}true WNC\textquotedbl{} information stream
(limited by the amount of available HSI) in the system, the superposed
part defines the \textquotedbl{}routed\textquotedbl{} information
which is appended on top of the WNC stream to exploit any potential
spare capacity of related channels in the system (see \cite{Uricar-Qian-Sykora-Mow_2013-WCNC,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}
for more details). A simplified description of SC-based relaying in
an uncoded WBN system is summarized in Table~\ref{tab:CTUpp_SC-relaying-scheme}
and depicted in Fig.~\ref{fig:CTUpp_Information-flow-uncoded-block-scheme}.
\begin{figure*}
\begin{centering}
\includegraphics[width=1\textwidth]{fig/butterfly-2level_processing_principleTWC-uncoded}
\par\end{centering}
\caption{Relaying scheme for the uncoded WBN
system. DEM stands for a hard decision demodulator, IC is the interference
canceler.\label{fig:CTUpp_Information-flow-uncoded-block-scheme}}
\end{figure*}
\begin{table}
\centering{}%
\begin{tabular}{|>{\raggedright}p{0.95\columnwidth}|}
\hline 
\textbf{Step 1: Source transmission}
\begin{itemize}
\item Source $S_{i},\,i\in\left\{ A,B\right\} $ maps its data symbol $\mathbf{d}_{i}=\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]$
into a $\left(N_{b}+N_{s}\right)$-bit superposition modulation symbol
\begin{equation}
s_{i}=\mathcal{A}^{i}\left(\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]\right),\label{eq:CTUpp_OverallSourceStreams}
\end{equation}

\item $S_{A},\,S_{B}$ simultaneously transmit their signals to the relay
and unintended destinations (Fig.~\ref{fig:CTUpp_Information_flows}).
\item Relay receives
\begin{equation}
x=h_{AR}\mathcal{A}^{A}\left(\left[\mathbf{d}_{A}^{b};\mathbf{d}_{A}^{s}\right]\right)+h_{BR}\mathcal{A}^{B}\left(\left[\mathbf{d}_{B}^{b};\mathbf{d}_{B}^{s}\right]\right)+w_{R}
\end{equation}

and decodes $\left[\mathbf{d}_{A}^{s};\mathbf{d}_{B}^{s};f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})\right]$,
where $f$ is a hierarchical WNC function \cite{Sykora-Burr_2011-TVT}.

\item $D_{j}$ receives
\begin{equation}
z_{j}=h_{ij}\mathcal{A}^{i}\left(\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]\right)+w_{j},\label{eq:CTUpp_Dj_received}
\end{equation}
where $i,\,j\in\left\{ A,B\right\} ,\,i\neq j$ and stores the signal
for further processing.\end{itemize}
\tabularnewline
\hline 
\textbf{Step 2: Relay broadcast}
\begin{itemize}
\item Relay sends $N_{R}=2N_{s}+N_{b}$-bit modulation symbol to both destinations:
\begin{equation}
s_{R}=\mathcal{A}^{R}\left(\left[\mathbf{d}_{A}^{s};\mathbf{d}_{B}^{s};f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})\right]\right).\label{eq:CTUpp_relay_output}
\end{equation}

\item $D_{j}$ ($i,\,j\in\left\{ A,B\right\} ,\,i\neq j$) decodes:

\begin{itemize}
\item $\left[\mathbf{d}_{A}^{s};\mathbf{d}_{B}^{s};f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})\right]$
(from the relay signal (\ref{eq:CTUpp_relay_output}))
\item $\mathbf{d}_{i}^{b}$ (from the stored signal $z_{j}$ (\ref{eq:CTUpp_Dj_received}),
after interference cancellation (IC) of known $\mathbf{d}_{i}^{s}$)
\item $\mathbf{d}_{j}^{b}$ (from $\mathbf{d}_{i}^{b}$ and $f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})$,
using a standard WNC decoding \cite{Sykora-Burr_2011-TVT})
\end{itemize}
\item $D_{j}$ merges $\mathbf{d}_{j}^{b}$ with $\mathbf{d}_{j}^{s}$ to
obtain the desired $\left[\mathbf{d}_{j}^{b};\mathbf{d}_{j}^{s}\right]$.\end{itemize}
\tabularnewline
\hline 
\end{tabular}\vskip1ex\caption{SC-based relaying scheme in uncoded WBN}.\label{tab:CTUpp_SC-relaying-scheme}
\end{table}

\subsection{System Model}

For the sake of simplicity of the constellation design analysis, we
provisionally assume that the system is uncoded\footnote{ Modification of the system model for the coded case will be provided
in Section~\ref{sec:CTUpp_Channel-Coding}, together with a discussion
on the design of individual channel encoders for particular information
streams in the system.}. The signal space representations of the transmitted channel symbols
are $s_{A}=\mathcal{A}^{A}\left(\mathbf{d}_{A}\right)$, $s_{B}=\mathcal{A}^{B}\left(\mathbf{d}_{B}\right)$,
where $\mathcal{A}^{i}\left(\centerdot\right)$ is the memoryless
constellation mapper and $\mathbf{d}_{i}$ is the source $i\in\left\{ A,B\right\} $
data symbol. Each communication round can be divided into two phases
(Fig. \ref{fig:CTUpp_Information_flows}). In the first phase (Multiple
Access \textendash{} MA phase) both sources $S_{A},\,S_{B}$ simultaneously
transmit their signal to the relay, which receives a noisy superimposed
constellation:
\begin{equation}
x=h_{AR}s_{A}+h_{BR}s_{B}+w_{R}.\label{eq:CTUpp_relay-received}
\end{equation}
Additionally, the source $S_{i}$ ($i\in\{A,B\}$) transmission is
overheard (at no cost) by its \textquotedbl{}unintended\textquotedbl{}
destination $D_{j}$ ($j\in\{A,B\},\,j\neq i$) as:
\begin{align}
z_{j} & =h_{ij}s_{i}+w_{j}\label{eq:CTUpp_HSI_observation}
\end{align}
Even though the overheard information (\ref{eq:CTUpp_HSI_observation})
does not carry the desired data for the respective destination, it
can be efficiently exploited to enable WNC-based processing in WBNs
\cite{Uricar-Qian-Sykora-Mow_2013-WCNC}. We denote the specific overheard
information as the \emph{Hierarchical Side Information} (HSI) \cite{Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}.

The relay performs WNC-based decoding \cite{Sykora-Burr_2011-TVT}
of the received signal and broadcasts the decoded WNC (hierarchical)
information as $s_{R}$ to $D_{A},\,D_{B}$ in the second phase (Broadcast
\textendash{} BC phase). Both destinations are able to decode the
desired data using the relay's (hierarchical) signal (\ref{eq:CTUpp_relay-received})
and the overheard HSI (\ref{eq:CTUpp_HSI_observation}) if a proper
WNC processing is employed in the system.

Scalar complex channel coefficients $h_{ij}$, $i,j\in\{A,B,R\}$,
$i\neq j$ are assumed to be constant during the communication round
and known at the respective receiving node. Zero mean i.i.d. complex
Gaussian noise sample $w_{i}$, $i\in\{A,B,R\}$ has variance $\sigma_{i}^{2}$.
Signal to Noise Ratios (SNRs) in the system are given by ($\gamma_{{\rm {MAC}}}$,
$\gamma_{{\rm {HSI}}}$, $\gamma_{{\rm {BC}}}$), where $\gamma_{{\rm {MAC}}}$
is the SNR on the source$\rightarrow$relay multiple-access channel
\textendash{} MAC ($\left(S_{A},\,S_{B}\right)\rightarrow R$), $\gamma_{{\rm {HSI}}}$
is the SNR on the unintended source$\rightarrow$destination (HSI)
channels ($S_{A}\rightarrow D_{B}$, $S_{B}\rightarrow D_{A}$) and
$\gamma_{{\rm {BC}}}$ is the SNR on the relay$\rightarrow$sources
broadcast channel ($R\rightarrow\left(D_{A},\,D_{B}\right)$).

\section{Superposition Modulation Design\label{sec:CTUpp_Euclidean-Distance-based-Constel}}

In this section we summarize the design of constellation mappers $\mathcal{A}^{A},\,\mathcal{A}^{B}$
as presented in \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}. The
output constellation is created as
\begin{equation}
s=\mathcal{A}\left(\left[\mathbf{d}^{b};\mathbf{d}^{s}\right]\right)=\sum_{n_{s}=0}^{N_{s}-1}L_{n_{s}}^{s}(2d_{n_{s}}^{s}-1)+\sum_{n_{b}=0}^{N_{b}-1}L_{n_{b}}^{b}(2d_{n_{b}}^{b}-1),\label{eq:CTUpp_superpositionModulation}
\end{equation}
where $L_{n}^{b},\,L_{n}^{s}$ are \emph{Superposition Modulation}
\cite{Hoeher-Wo_2011-IEEE-M-COM} \emph{scaling coefficients.}

The coefficients $L_{n}^{b},\,L_{n}^{s}$ (\ref{eq:CTUpp_superpositionModulation})
are generally taken from the set of complex numbers. However, for
the sake of simplicity we limit the scaling coefficients $L_{n}^{b},\,L_{n}^{s}$
to a purely imaginary or real numbers. Even though that this simplified
approach can potentially result in a sub-optimal performance in fading
channels (complex channel coefficients $h_{iR}$, $i\in\{A,B\}$ can
rotate the component superposition constellations), we follow this
simplification to show the basic ideas of the proposed superposition
modulation design. The extension to general complex $L_{n}^{b},\,L_{n}^{s}$
can naturally embrace the source phase pre-rotation \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008},
which virtually reverts the fading channel to the conventional Additive
White Gaussian Noise (AWGN) channel with $\varangle h_{ij}=0$.

As shown in Table~\ref{tab:CTUpp_SC-relaying-scheme}, the basic
and superposed parts of the source information are processed in a
different way through the system and so we will discuss the constellation
design for these two specific information streams separately. We briefly
introduce the incentives and main ideas of the design for the superposed
and basic parts, and then we summarize the complete multi-source constellation
design in a systematic algorithm.

\subsection{Constellation Design: Basic part\label{sub:CTUpp_basic-part}}

A specific WNC function $f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})$
has to be decoded by the relay (Table~\ref{tab:CTUpp_SC-relaying-scheme})
and hence some overlapping of symbols in the superimposed constellation
(observed by the relay node) can be allowed, resulting in improved
Euclidean distance properties. More precisely, two (or more) pairs
of basic information symbols $\left(\mathbf{d}_{A}^{b},\,\mathbf{d}_{B}^{b}\right)$,
$\left(\mathbf{d'}_{A}^{b},\,\mathbf{d'}_{B}^{b}\right)$ can be allowed
to fall into the same point in the superimposed constellation:
\begin{equation}
s_{A}\left(\mathbf{d}_{A}^{b}\right)+s_{B}\left(\mathbf{d}_{B}^{b}\right)=s'_{A}\left(\mathbf{d'}_{A}^{b}\right)+s'_{B}\left(\mathbf{d'}_{B}^{b}\right),\label{eq:CTUpp_exclusive-law}
\end{equation}
if and only if they belong to the same WNC function output, i.e. iff
$f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})=f(\mathbf{d'}_{A}^{b},\mathbf{d'}_{B}^{b})$,
where $f(\centerdot,\centerdot)$ is the hierarchical WNC function\cite{Sykora-Burr_2011-TVT}.
In this case the overlapping symbols produce the \emph{same hierarchical
output}, which can be successfully resolved by the destination, if
matching HSI information is available (Table~\ref{tab:CTUpp_SC-relaying-scheme}).
The particular choice of the scaling coefficients $L_{A,n}^{b},\,L_{B,n}^{b}$
generally depends on the particular choice of the hierarchical WNC
function\footnote{Modulo-sum \cite{Hekrdla-Sykora_2013,Prochazka-Uricar-Halls-Sykora_2015-ICC,Prochazka-2016}
and bit-wise exclusive-or (XOR) \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew-Lu_2012}
hierarchical functions are commonly discussed in the WNC literature,
however, unlike the bit-wise XOR, implementation of channel coding
for the Modulo-sum mapping is a standalone research problem and hence
it is out of the scope of this paper.}. In the rest of this paper we discuss the constellation design for
the \emph{bit-wise exclusive-or} WNC function ($f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})=\mathbf{d}_{A}^{b}\oplus\mathbf{d}_{B}^{b}$,
where $\oplus$ is the bit-wise XOR operation) \cite{Zhang-Liew-Lu_2012}.

Suitable overlapping of constellation symbols at the relay is provided
by letting both sources transmit at the same power level, i.e. $L_{A,n}^{b}=L_{B,n}^{b}$
\cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}. It can be easily shown
that if these superposition modulation (\ref{eq:CTUpp_superpositionModulation})
coefficients are chosen as $L_{A,n}^{b}=L_{B,n}^{b}=3^{\left\lfloor n/2\right\rfloor }$
(for even $n$) and $L_{A,n}^{b}=L_{B,n}^{b}=\jj3^{\left\lfloor n/2\right\rfloor }$
(for odd $n$), the received superimposed constellation at the relay
will have overlaps only among those constellation symbols (\ref{eq:CTUpp_exclusive-law})
which have the same hierarchical WNC output i.e. $f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})=f(\mathbf{d'}_{A}^{b},\mathbf{d'}_{B}^{b})=\mathbf{d}_{A}^{b}\oplus\mathbf{d}_{B}^{b}=\mathbf{d'}_{A}^{b}\oplus\mathbf{d'}_{B}^{b}$.

\subsection{Constellation Design: Superposed part\label{sub:CTUpp_superposed-part}}

The superposed information given by $\mathbf{d}_{A}^{s},\,\mathbf{d}_{B}^{s}$
has to be decoded separately by the relay (Table~\ref{tab:CTUpp_SC-relaying-scheme}),
and hence a source constellation avoiding all potential overlaps in
the superimposed constellation (observed by the relay node) is desirable.
In an AWGN channel ($h_{AR}=h_{BR}=1$ in Fig.~\ref{fig:CTUpp_Information_flows})
this can be simply achieved by mapping the information bits to the
real-valued Amplitude Shift Keying (ASK) constellation at $S_{A}$
and purely imaginary-valued ASK constellation at $S_{B}$ (or vice
versa). Hence, in AWGN, the resulting superimposed constellation at
the relay will form a regular QAM constellation without any overlapping
of constellation symbols. For the assumed superposition modulation
(\ref{eq:CTUpp_superpositionModulation}), this can be easily achieved
by setting the coefficients as $L_{A,n}^{s}=2^{n}$ and $L_{B,n}^{s}=\jj\cdot2^{n}$.
\begin{algorithm}[H]
\input{alg4_final_TWC.tex}\caption{Constellation design for fixed $N_{b},\,N_{s}$.\label{alg:CTUpp_ButterflyConstellationDesign} }
\end{algorithm}

\subsection{Systematic Constellation Design Algorithm\label{sub:CTUpp_const_design}}

To accommodate both the basic and superposed information streams into
a joint source constellation, the scaling coefficients of basic information
streams ($L_{n}^{b}$) must be pre-scaled by a factor $2^{N_{s}}$
to ensure that they lie above the largest scaling coefficient of the
superposed part. The basic stream (WNC) is thus preferred over the
superposed one (routing) in order to maximize the overall throughput
of the system. The systematic constellation design for arbitrary $N_{b},\,N_{s}$
is summarized in Algorithm~\ref{alg:CTUpp_ButterflyConstellationDesign}.

The basic principle of source constellation design is illustrated
in Fig.~\ref{fig:CTUpp_ConstellationDesignExample} ($N_{b}=2,\,N_{s}=1$)
and some example sets of source constellations with constant $N_{b}+N_{s}=2$
are depicted in Fig.~\ref{fig:CTUpp_ConstellationDesign_NbNs2}.

\section{Performance Analysis I: Uncoded System\label{sec:CTUpp_Performance-Analysis-Uncoded}}

For the sake of simplicity of the theoretical performance analysis,
we assume that source$\rightarrow$relay channels in WBN are AWGN\footnote{Note that this also includes the system with perfect source phase
prerotation \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008},
which can be obtained by a generalization of the scaling coefficients
as $L'_{n}=L_{n}e^{-\jj\measuredangle h_{SR}}$, where $h_{SR}$ is
the corresponding source$\rightarrow$relay channel.} (i.e. $h_{iR}=1$ for $i\in\{A,B\}$). We evaluate the throughput
analytically as $(N_{b}+N_{s})\cdot(1-P_{e}^{\mathrm{FER}})$, where
$P_{e}^{\mathrm{FER}}$ denotes the frame error rate. Due to the system
symmetry we evaluate the throughput of $S_{A}\to D_{A}$ only. We
set the frame length to $M=768$ symbols (to match the HW evaluation)
and the relay output mapper $\mathcal{A}^{R}$ will be defined as
a conventional ($2^{N_{b}+2N_{s}}$$)$-QAM constellation. All performance
metrics in the symmetric WBN are evaluated as a function of the actual
SNRs ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}},\,\gamma_{{\rm {BC}}}$).
\begin{figure*}
\centering{}\includegraphics[width=0.8\textwidth]{fig/d2_1}\caption{Source constellation design example for $N_{b}=2,\,N_{s}=1$. Resulting
constellations are depicted as blue circles ($S_{A}$ output constellation),
red circles ($S_{B}$ output constellation) and squares (received
superimposed constellation at $R$). Hierarchical function is $f\left(\mathbf{d}_{A}^{b},\,\mathbf{d}_{B}^{b}\right)=\mathbf{d}_{A}^{b}\oplus\mathbf{d}_{B}^{b}$.\label{fig:CTUpp_ConstellationDesignExample} }
\end{figure*}
\begin{figure*}
\begin{centering}
\includegraphics[width=1\textwidth]{fig/const_all_2}
\par\end{centering}

\caption{Proposed constellation design for $\left(N_{b},N_{s}\right)=\left\{ \left(2,0\right);\left(1,1\right);\left(0,2\right)\right\} $.\label{fig:CTUpp_ConstellationDesign_NbNs2} }
\end{figure*}

\subsection{Analytical Performance Evaluation\label{sub:CTUpp_Numerical_Evaluation_uncoded}}

Since all constellations points lie on a regular QAM grid, it is straightforward
to evaluate the exact Symbol Error Rate (SER) for all channels analytically.
The symbol error probability $P_{e}^{\mathrm{SER}}$ can be approximated
by its upper-bound\footnote{The evaluated $P_{e,\mathrm{UB}}^{SER}$ is an upper-bound of $P_{e}^{\mathrm{SER}}$,
since an error in MA/BC phase does not necessarily induce an error
in the overall communication chain of the uncoded system. This is
especially true if the error occurs in the superposed bits $\mathbf{d}_{B}^{s}$
used for interference cancellation processing at $D_{A}$.} $P_{e,\mathrm{UB}}^{\mathrm{SER}}=1-((1-P_{e}^{{\rm MAC}})(1-P_{e}^{{\rm HSI}})(1-P_{e}^{\mathrm{BC}}))$,
where $P_{e}^{{\rm MAC}}$, $P_{e}^{{\rm HSI}}$ and $P_{e}^{{\rm BC}}$
are the probabilities of symbol error in the MAC, HSI and BC channels
(respectively). Since the system is memoryless, the overall FER is
given by $P_{e}^{\mathrm{FER}}=1-(1-P_{e}^{\mathrm{SER}})^{M}$, which
can be approximated by $P_{e,\mathrm{UB}}^{\mathrm{FER}}=1-(1-P_{e,\mathrm{UB}}^{\mathrm{SER}})^{M}$.
Nearest neighbor pairwise error approximation can be used for efficient
error rate evaluation. The lower-bound of the throughput can be then
evaluated analytically as:
\begin{equation}
T_{\mathrm{LB}}=(N_{b}+N_{s})\cdot(1-P_{e,\mathrm{UB}}^{\mathrm{FER}}).\label{eq:CTUpp_T-LB}
\end{equation}

\subsection{Hardware Implementation\label{sub:CTUpp_Hardware_Verification}}

In addition to the analytical evaluation of throughput, we validate
the results in a real-world setup. The hardware performance is evaluated
using Ettus Research Universal Software Radio Peripherals (USRPs)
which are computer-hosted Software Defined Radios (SDRs). The USRPs
connect to a host computer via a Gigabit Ethernet link, which the
host-based software uses to receive and transmit the baseband IQ stream.
The host controls the USRP using USRP Hardware Driver (UHD) commands,
including setting parameters such as amplifier gain. The USRP then
performs the necessary baseband processing then up/down-conversion
and transmission/reception. The Ettus Research N210 USRP is used,
which consists of a motherboard and a Radio Frequency (RF) daughterboard;
more details can be found in \cite{Ettus_flyer}. In these experiments
the XCVR2450 daughterboards are used, these are dual-band transceivers
with 100 mW output at 2.4 - 2.5 GHz and 50 mW output at 4.9 - 5.85
GHz. In this paper GNURadio \cite{GNURadio}, which is an open-source
tool-kit, is used as the host-processing software.
\begin{figure}
\centering{}\includegraphics[width=0.95\columnwidth]{fig/20150109_143009}\caption{Setup for HW evaluation (Ettus Research
USRPs). Source transmissions are prerotated \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008}
to imitate the AWGN channel conditions (as used in the numerical evaluation).
To allow a strict control of HSI channels SNR in the HW
setup, the HSI channels are emulated by adding a Gaussian noise to
the respective source signal and the resulting emulated HSI is passed
to destinations via UDP. This also avoids the problem of node visibility
where direct links $S_{A}\rightarrow D_{A}$ and $S_{B}\rightarrow D_{B}$
exist in the laboratory environment.\label{fig:CTUpp_HW_setup}}
\end{figure}

\subsubsection{OFDM Parameters}

An OFDM solution is employed with $N_{FFT}=64$ subcarriers. There
are 48 data subcarriers, with a DC carrier, 11 guard carriers and
4 pilot carriers at -21, -7, 7 and 21. A CP of $\frac{1}{4}$, i.e.
16 samples, is employed and a center frequency of $f_c=2.4$GHz is
used. The USRP N210 is limited (by the Gigabit Ethernet link) to support
an RF bandwidth up to 25 MHz with 14-bit resolution, though a 1 MHz
bandwidth, i.e. 1 MS/s sampling rate, is used here. Each packet contains
16 OFDM symbols of payload with 48 data carriers per symbol and constellation
parameters $N_{b}$,~$N_{s}$ are set to the desired values. The
payload is random data and no channel coding is currently implemented
in the system.

\subsubsection{Node Placement, Synchronization and Channel Estimation\label{sub:CTUpp_frame-1-2}}

A 5-node, 2x1x2 topology with two sources, one relay and two destinations,
is used as shown in Fig. \ref{fig:CTUpp_HW_setup}. The USRPs each
have a single 3dBi omni-directional antenna (at 2.4 - 2.5 GHz and
4.9 - 5.85 GHz). The first source transmitter ($S_A$) USRP is connected
to a powerful Core i7 laptop, running a single instance of GNURadio,
by a Gigabit Ethernet link. The second source transmitter ($S_B$)
USRP is connected to the first by the MIMO expansion cable. This provides
the second transmitter with baseband data from GNURadio as well as
synchronization signals from the first transmitter. The relay, $D_{A}$
and $D_{B}$ USRPs are connected to further laptops running GNURadio
by Gigabit Ethernet links. More details about synchronization, carrier
frequency offset and timing offset estimation can be found in \cite{Hynek-etal_2014-EW}.
In this paper, the MIMO cable is used to synchronize the frequency
of the two source USRPs, as well as to achieve sample-level timing
synchronization. The latter avoids asynchronism in the superimposed
constellations at the relays; more details about the impact of asynchronism
in WNC can be found in \cite{Diwine_D512}. Furthermore an Ettus Octoclock
clock distribution system \cite{Ettus_OctoClock} is used to provide
external frequency synchronization signals to all nodes. This allows
us to show system performance, and compare with the theoretical and
simulation cases, without the impact of asynchronism affecting the
results. Results with additional real-world impairments are a focus
for future work, as discussed in the final section of this paper.
Channel tracking using pilots is implemented as detailed in \cite{Hynek-etal_2014-EW},
however, due to the static indoor environment (used to mimic the AWGN
channel used in the theoretical work as closely as possible) the channel
does not change significantly over the frame duration. The USRPs are
closely located in line-of-sight to ensure the channel between them
is fairly static, without fading, thus mimicking the channel used
in the theoretical work. Moreover as cabled synchronisation is used,
it is desirable to minimize the cable length. Low SNRs are achieved
between the USRPs using low transmit powers.

\subsection{Uncoded System Throughput}

To analyze the performance of the proposed constellations, we evaluate
the throughput for fixed $\gamma_{{\rm {MAC}}}$ and $\gamma_{{\rm {BC}}}$
as a function of $\gamma_{{\rm {HSI}}}$. We analyze all permissible
constellations for a fixed $N_{b}+N_{s}=2$ (see Fig.~\ref{fig:CTUpp_ConstellationDesign_NbNs2})
and compare their performance with the throughput $T_{\mathrm{ref}}$
of the \emph{reference} ``conventional\textquotedbl{} multi-user
detection with regular QAM constellation. Note again that the hierarchical
function is set to the bit-wise XOR, i.e. $f\left(\mathbf{d}_{A}^{b},\,\mathbf{d}_{B}^{b}\right)=\mathbf{d}_{A}^{b}\oplus\mathbf{d}_{B}^{b}$
in the evaluations.

In addition to the analytically evaluated throughput (lower-bound)
$T_{\mathrm{LB}}$ (\ref{eq:CTUpp_T-LB}) we also include the result
of a numerical Monte-Carlo evaluation of throughput ($T_{\mathrm{sim}}$)
over $10^{4}$ frames (Figs.~\ref{fig:CTUpp_Throughput16_20},~\ref{fig:CTUpp_Throughput17_17},~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16})
and throughput $T_{\mathrm{USRP}}$ evaluated by the HW
real world setup (Figs.~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16}).
The particular related assumptions employed in the evaluations are
summarized in Table~\ref{tab:UncodedSystemSummary} to improve the
reader's perception. One can see that the reference scenario with
conventional QPSK (4-QAM) provides zero throughput ($T_{\mathrm{ref}}$)
in the whole range of analyzed SNRs in all plots\footnote{In AWGN channel, the resulting superimposed constellation has too
many overlaps for the reference source QPSK constellations, preventing
a successful multi-user decoding of both of the separate user data
streams in the uncoded system.}. The performance of conventional WNC (in the specific 4-ary case
the conventional WNC constellations are identical to $(N_{b},N_{s})=(2,0)$
\cite{Koike-Popovski-Tarokh_2008}) is, on the other hand, inevitably
limited to high $\gamma_{{\rm {HSI}}}$ regions in WBN as it requires
perfect HSI to enable the decoding of WNC functions at the destination
nodes \cite{Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}. Remarkably, the
novel proposed constellations provide a \emph{non-zero throughput}
even in the \emph{low-to-medium SNR} region of HSI channels. The resulting
SNR and throughput gains are highlighted in Figs.~\ref{fig:CTUpp_Throughput16_20},~\ref{fig:CTUpp_Throughput17_17},~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16}.
Note also extremely close agreement of HW performance evaluation $T_{\mathrm{USRP}}$
in all cases (Figs.~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16}).
Even in this simple case ($N_{b}+N_{s}$ fixed to $2$) there are
several interesting phenomena which can be observed in the throughput
performance:
\begin{table*}
\begin{centering}
{\small{}}%
\begin{tabular}{|l|c|c|c|}
\cline{2-4} 
\multicolumn{1}{l|}{} & {\small{}$T_{\mathrm{LB}}$ } & {\small{}$T_{\mathrm{sim}}$} & {\small{}$T_{\mathrm{USRP}}$ }\tabularnewline
\hline 
{\small{}Communication channel} & {\small{}AWGN} & {\small{}AWGN} & {\small{}Wireless channel}\tabularnewline
\hline 
{\small{}Time synchronization} & {\small{}Perfect} & {\small{}Perfect} & {\small{}External (Octoclock)}\tabularnewline
\hline 
{\small{}Phase pre-rotation} & {\small{}Perfect} & {\small{}Perfect} & {\small{}Feedback channel (UDP)}\tabularnewline
\hline 
{\small{}Direct link} & {\small{}Not considered} & {\small{}Not considered} & {\small{}Bridged by cable}\tabularnewline
\hline 
{\small{}Channel symmetry} & {\small{}Perfect} & {\small{}Perfect} & {\small{}Node placement}\tabularnewline
\hline 
{\small{}Throughput evaluation} & {\small{}Lower bound} & {\small{}Numerical} & {\small{}Numerical}\tabularnewline
\hline 
\end{tabular}{\small{}\vspace{1ex}
}
\par\end{centering}{\small \par}

\caption{Summary of assumptions in the uncoded system analysis.\label{tab:UncodedSystemSummary}}
{\small{}\vspace*{-3ex}
}{\small \par}
\end{table*}

\begin{itemize}
\item The constellations with ($N_{b}=0,\,N_{s}>0$) assume full multi-user
detection at the relay and hence they do not exploit the HSI channels
(Table~\ref{tab:CTUpp_SC-relaying-scheme}). Consequently, their
throughput does not depend on $\gamma_{{\rm {HSI}}}$. However, their
performance worsens with decreasing $\gamma_{{\rm {MAC}}}$ (compare
Figs.~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput16_20})
and deteriorates quite dramatically with decreasing $\gamma_{{\rm {BC}}}$
(compare Figs.~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16}).
\item The constellations with ($N_{b}>0,\,N_{s}=0$) require a reliable
HSI channel and hence their throughput is zero for low $\gamma_{{\rm {HSI}}}$
and grows up to $N_{b}$ for high $\gamma_{{\rm {HSI}}}$ and sufficiently
high $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$ (all Figs.~\ref{fig:CTUpp_Throughput16_20},~\ref{fig:CTUpp_Throughput17_17},~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16}).
\item The performance of all constellations with ($N_{b}>0,\,N_{s}>0$)
is influenced by all system SNRs ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$).
Remarkably, for some particular values of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$
these constellations significantly outperform those with $N_{b}=0$
or $N_{s}=0$ in the medium $\gamma_{{\rm {HSI}}}$ region (Figs.~\ref{fig:CTUpp_Throughput17_17},~\ref{fig:CTUpp_Throughput20_16}).
Note that this is a direct consequence of superior $\rho_{\mathrm{HSI}}^{2}$
performance of these constellations\footnote{It can be shown that for constant $N_{b}+N_{s}$ the minimum Euclidean
distance $\rho_{\mathrm{HSI}}^{2}$ grows with decreasing $N_{b}$,
resulting in a more efficient utilization of \textquotedbl{}imperfect\textquotedbl{}
HSI channels \cite{Uricar-Sykora_2012,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}
and consequently in a more reliable overheard HSI for the constellations
with lower (non-zero) $N_{b}$.} for constant $N_{b}+N_{s}$, i.e. for constant bits/constellation
symbol transmitted by the sources.
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC16_BC20_N2}\vskip-2ex
\par\end{centering}

\caption{Comparison of throughput as a function of $\gamma_{{\rm {HSI}}}$
for $\gamma_{{\rm {MAC}}}=16\,\mathrm{dB},\,\gamma_{{\rm {BC}}}=20\,\mathrm{dB}$
and given $(N_{b},N_{s})$. \label{fig:CTUpp_Throughput16_20}}
\end{figure}
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC17_BC17_N2}\vskip-2ex
\par\end{centering}

\caption{Comparison of throughput as a function of $\gamma_{{\rm {HSI}}}$
for $\gamma_{{\rm {MAC}}}=17\,\mathrm{dB},\,\gamma_{{\rm {BC}}}=17\,\mathrm{dB}$
and given $(N_{b},N_{s})$.\label{fig:CTUpp_Throughput17_17}}
\end{figure}
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC20_N2}\vskip-2ex
\par\end{centering}

\caption{Comparison of throughput as a function of $\gamma_{{\rm {HSI}}}$
for $\gamma_{{\rm {MAC}}}=20\,\mathrm{dB},\,\gamma_{{\rm {BC}}}=20\,\mathrm{dB}$
and given $(N_{b},N_{s})$. \label{fig:CTUpp_Throughput20_20}}
\end{figure}
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}\includegraphics[clip,width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC16_N2}\vskip-2ex
\par\end{centering}

\caption{Comparison of throughput as a function of $\gamma_{{\rm {HSI}}}$
for $\gamma_{{\rm {MAC}}}=20\,\mathrm{dB},\,\gamma_{{\rm {BC}}}=16\,\mathrm{dB}$
and given $(N_{b},N_{s})$. \label{fig:CTUpp_Throughput20_16}}
\end{figure}

\end{itemize}

\section{Adaptive Constellation Design\label{sec:CTUpp_Adaptive-Constellation-Design}}

As discussed in the previous section, the throughput of the system
depends heavily on the actual SNR conditions (given by $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$).
By itself, this observation calls naturally for an\emph{ adaptive
constellation design}. To generate a multi-source constellation able
to \emph{maximize the throughput} given the current SNR conditions
in the WBN system, the source nodes $S_{A},\,S_{B}$ must be acquainted
with the particular mapping operation $(\hat{\gamma}_{{\rm {MAC}}},\,\hat{\gamma}_{{\rm {BC}}},\,\hat{\gamma}_{{\rm {HSI}}})\mapsto(N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}),$
providing the constellation parameters $N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}$
(input arguments to the Algorithm~\ref{alg:CTUpp_ButterflyConstellationDesign})
for the given (available) SNR estimates\footnote{The estimated SNR parameters ($\hat{\gamma}_{{\rm {MAC}}},\,\hat{\gamma}_{{\rm {BC}}},\,\hat{\gamma}_{{\rm {HSI}}}$)
must be delivered to both sources by a feedback channel from the relay
and/or destinations. The particular implementation of this feedback
transmission is beyond the scope of this paper and hence (for the
sake of simplicity) we assume that these parameters are made available
at both sources by a genie. Note that in the HW evaluation, the required
feedback is provided via UDP connection.} ($\hat{\gamma}_{{\rm {MAC}}},\,\hat{\gamma}_{{\rm {BC}}},\,\hat{\gamma}_{{\rm {HSI}}}$).
The desired \emph{SNR mapping regions} (a three-dimensional look-up
table in WBN) can be generated numerically in advance and stored at
both source nodes to enable the adaptive constellation mapping.

Due to the numerical complexity of Monte-Carlo evaluation of throughput
$T_{\text{sim}}$ we use the analytically evaluated lower bound $T_{\text{LB}}$
(\ref{eq:CTUpp_T-LB}) to generate the SNR mapping regions for a wide
range of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$.
The optimal constellation parameters (maximizing the throughput $T_{\mathrm{LB}}$
for a given SNR triplet $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$)
are found by performing an exhaustive search over the constellation
parameters as $(N_{b}^{{\rm I}},\,N_{s}^{{\rm I}})=\arg\max_{(N_{b},N_{s})}T_{\mathrm{LB}}(\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}})$.

The SNR mapping regions, including the resulting throughput for the
optimal choice of $N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}$, are shown
as a function of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$ for
$\gamma_{{\rm {BC}}}\in\{15\,\mathrm{dB},\,17\,\mathrm{dB},20\,\mathrm{dB},25\,\mathrm{dB}\}$
in Fig.~\ref{fig:CTUpp_SNR_map_BC15-17-20-25}. Several interesting
phenomenas can be again observed in the figure:
\begin{itemize}
\item Since the transmission schemes with ($N_{b}=0,\,N_{s}>0$) constellations
can ignore the HSI channels (Table~\ref{tab:CTUpp_SC-relaying-scheme}),
these constellations are optimal in the low $\gamma_{{\rm {HSI}}}$
region ($\gamma_{{\rm {HSI}}}<8\,\mathrm{dB}$), regardless of the
other channels' SNRs $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$.
\item The constellations with ($N_{b}>0,\,N_{s}=0$) provide the best performance
in a substantial part of the medium-to-high $\gamma_{{\rm {HSI}}}$
regions, depending on the actual $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$.
\item The \textquotedbl{}combined\textquotedbl{} constellations ($N_{b}>0,\,N_{s}>0$)
provide the maximal throughput (for sufficiently high $\gamma_{{\rm {BC}}}$)
in relatively large regions of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$
(see the dominant throughput regions of $(N_{b}^{{\rm I}},\,N_{s}^{{\rm I}})=(2,1)$
for $\gamma_{{\rm {BC}}}=\left\{ 20\,\mathrm{dB},\,25\,\mathrm{dB}\right\} $).
Note that these constellations have a great potential for application
in systems with limited or partial HSI (see \cite{Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}).
\begin{figure*}
\begin{centering}
\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC15}\quad\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC17}
\par\end{centering}

\centering{}\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC20}\quad\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC25}\caption{Throughput performance $T_{\mathrm{LB}}$ and SNR mapping regions
(including the optimal const. parameters ($N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}$))
for $\gamma_{{\rm {BC}}}\in\{15\,\mathrm{dB},\,17\,\mathrm{dB},20\,\mathrm{dB},25\,\mathrm{dB}\}$.\label{fig:CTUpp_SNR_map_BC15-17-20-25}}
\end{figure*}
\begin{figure*}
\centering{}\includegraphics[width=0.48\textwidth]{fig/XOR_map_Througput_BC20}\quad\includegraphics[width=0.48\textwidth]{fig/XOR_map_Througput_USRP_BC20}\caption{Comparison of $T_{\mathrm{LB}}$ and the throughput performance evaluated
in a real world adaptive HW setup ($T_{\mathrm{USRP}}$) for $\gamma_{{\rm {BC}}}=20\,\mathrm{dB}$.
The SNR mapping regions (including the optimal const. parameters ($N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}$))
used in the HW evaluation are also emphasized in the figure.\label{fig:CTUpp_SNR_map_BC20_USRP}}
\vspace*{-4ex}
\end{figure*}

\item The BC channel SNR ($\gamma_{{\rm {BC}}}$) can significantly limit
the performance of the system, even in the case where both $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$
are relatively high (compare the results for $\gamma_{{\rm {BC}}}=15\,\mathrm{dB}$
and $\gamma_{{\rm {BC}}}=20\,\mathrm{dB}$ for $\gamma_{{\rm {MAC}}}=\gamma_{{\rm {HSI}}}\apprge15\,\mathrm{dB}$).
This behavior originates in the fact that $\rho_{\mathrm{BC}}^{2}$
decreases with growing $N_{b}+2N_{s}$ and hence low $\gamma_{{\rm {BC}}}$
essentially limits the maximum efficiently applicable cardinality
of the relay output ($2^{N_{b}+2N_{s}}$-QAM) constellation. Equivalently,
the optimal source constellation parameters ($N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}$)
can become limited by the bottleneck induced by weak relay$\rightarrow$destination
(BC) channels. 
\item The constellations with odd $N_{b}$ are rarely dominant over the
other strategies with identical $N_{b}+N_{s}$. This is a direct consequence
of their relatively poor $\rho_{\mathrm{MAC}}^{2}$ Euclidean distance
properties.
\end{itemize}
To support a viability of the adaptive constellation mapping scheme,
we again evaluate the system performance in the HW real world setup.
Since the HW evaluation is heavily time-consuming, we analyze the
throughput $T_{\mathrm{USRP}}$ only for $\gamma_{{\rm {BC}}}=20\,\mathrm{dB}$
and $0\,\mathrm{dB}\leq\gamma_{{\rm {MAC}}},\gamma_{{\rm {HSI}}}\leq30\,\mathrm{dB}$
with a step-size $3\,\mathrm{dB}$. The measured $T_{\mathrm{USRP}}$
performance is available in Fig.~\ref{fig:CTUpp_SNR_map_BC20_USRP}.
Close agreement between the $T_{\mathrm{USRP}}$ and $T_{\text{LB}}$
can be observed again in the whole range of analyzed $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$
(see Fig.~\ref{fig:CTUpp_SNR_map_BC20_USRP}).

\section{Channel Coding\label{sec:CTUpp_Channel-Coding}}

We have shown that Algorithm~\ref{alg:CTUpp_ButterflyConstellationDesign}
is a strong tool for the design of source constellations suitable
for arbitrary channel SNRs in the WBN system. However, even though
the proposed constellations provide promising performance in the uncoded
scenario, the extension to a coded system is desirable for practical
wireless applications.

Considering the communication in uncoded WBNs (Fig.~\ref{fig:CTUpp_Information-flow-uncoded-block-scheme}),
there are many ways to improve its reliability through channel coding.
In this paper we propose one particular solution, based on the assumption
that each source node splits its data into the basic and superposed
part and then encodes these parts separately by two constituent channel
encoders\footnote{In a more general approach, each source data word is split into $N_{b}+N_{s}$
parallel data sub-words that are encoded separately using the principles
of multilevel coding (see e.g. \cite{Wachsmann-Fischer-Huber-1999-IEEE-T-IT}).
However, the development of a general multilevel coding scheme for
WBN is beyond the scope of this paper.}. We believe that this approach provides the best insight into the
channel-coding extension of WBN systems and hence we focus on its
development in the rest of this section.

\subsection{Per-link Channel Coding Scheme for Symmetric WBN
with Superposition Modulations}

In general, it is desirable to protect\emph{ all individual transmissions}
in the system with error correction coding\footnote{Alternatively, a primitive end-to-end coding scheme can be designed,
performing the channel coding solely at sources $S_{A},\,S_{B}$ and
channel decoding (potentially computationally intensive) solely at
destinations $D_{A},\,D_{B}$, while leaving the relay $R$ to operate
on a symbol-by-symbol basis (as in the uncoded system). Unfortunately,
this approach is only sub-optimal, as in this case the particular
transmissions on source$\rightarrow$relay and relay$\rightarrow$destination
channels are not individually protected by channel coding.}. Accordingly, the relay node has to decode the desired data (including
the particular WNC function) from its observation and then it should
perform an additional re-encoding in order to protect the subsequent
relay$\rightarrow$destinations transmission. The resulting channel
coding scheme (see Fig.~\ref{fig:CTUpp_Information-flow-coded-block-scheme})
is introduced in the following text.

\subsubsection{Source processing}

Source $S_{A}$ (likewise for $S_{B}$) wants to transmit a binary
data word $\mathbf{D}_{A}$ of length $\left|\mathbf{D}_{A}\right|=\left|\mathbf{D}_{B}\right|=k_{\mathbf{D}}$
to its respective destination $D_{A}$. Each data word $\mathbf{D}_{A}$
is split into the basic and superposed part (similarly as in the uncoded
case), i.e.: 
\[
\mathbf{D}_{A}=[\mathbf{D}_{A}^{b},\mathbf{D}_{A}^{s}]=[d_{A,0}^{b},d_{A,1}^{b},\dots d_{A,k_{\mathbf{D}}^{b}-1}^{b},d_{A,0}^{s},d_{A,1}^{s},\dots d_{A,k_{\mathbf{D}}^{s}-1}^{s}],
\]
where $d_{A,n}^{b},\,d_{A,n}^{s}\in\left\{ 0,1\right\} $ and $k_{\mathbf{D}}^{b},\,k_{\mathbf{D}}^{s}$
are the lengths of the basic and superposed data sub-words $\mathbf{D}_{A}^{b},\,\mathbf{D}_{A}^{s}$
(respectively).

Subsequently, individual $\mathbf{D}_{A}^{b},\mathbf{\,D}_{A}^{s}$
are encoded by two separate linear binary encoders $\mathcal{C}_{b}(\centerdot),\,\mathcal{C}_{s}(\centerdot)$
(assumed identical at both sources), producing the constituent codewords
as:
\begin{align}
\mathcal{C}_{b}(\mathbf{D}_{A}^{b}) & =\mathbf{C}_{A}^{b}=[\mathbf{c}_{A,0}^{b},\mathbf{c}_{A,1}^{b},\dots,\mathbf{c}_{A,\mathcal{N}-1}^{b}],\\
\mathcal{C}_{s}(\mathbf{D}_{A}^{s}) & =\mathbf{C}_{A}^{s}=[\mathbf{c}_{A,0}^{s},\mathbf{c}_{A,1}^{s},\dots,\mathbf{c}_{A,\mathcal{N}-1}^{s}],
\end{align}
where $\mathcal{N}$ is the number of codeword symbols (equivalently
the number of channel uses required to transmit the codeword) and
$$\mathbf{c}_{A,j}^{b}=[c_{A,j_{0}}^{b},\dots,c_{A,j_{N_{b}-1}}^{b}],$$
$$\mathbf{c}_{A,j}^{s}=[c_{A,j_{0}}^{s},\dots,c_{A,j_{N_{s}-1}}^{s}]$$
are codeword symbols of length $N_{b}$ (respectively $N_{s}$) bits.
The dimensionality of binary codewords is thus $\left|\mathbf{C}_{A}^{b}\right|=\left|\mathbf{C}_{B}^{b}\right|=n_{\mathbf{C}}^{b}=\mathcal{N}\cdot N_{b}$,
$\left|\mathbf{C}_{A}^{s}\right|=\left|\mathbf{C}_{B}^{s}\right|=n_{\mathbf{C}}^{s}=\mathcal{N}\cdot N_{s}$.

The constituent codewords \textbf{$\mathbf{C}_{A}^{b},\,\mathbf{C}_{A}^{s}$}
are then forwarded to the joint constellation mapper $\mathcal{A}^{A}\left(\centerdot\right)$
(provided by Algorithm~\ref{alg:CTUpp_ButterflyConstellationDesign}),
which produces a sequence of $(N_{s}+N_{b})$-bit constellation symbols
$s_{A,j}=\mathcal{A}^{A}\left(\left[\mathbf{c}_{A,j}^{b};\mathbf{c}_{A,j}^{s}\right]\right)$.
Note that in the encoded system it is the codeword symbols that are
mapped to the desired constellation (instead of data symbols), but
since $\left|\mathbf{c}_{A}^{b}\right|=\left|\mathbf{c}_{B}^{b}\right|=N_{b}$
and $\left|\mathbf{c}_{A}^{s}\right|=\left|\mathbf{c}_{B}^{s}\right|=N_{s}$,
it is sufficient to formally substitute the codeword symbol $\mathbf{c}_{i}=\left[\mathbf{c}_{i}^{b};\mathbf{c}_{i}^{s}\right]$
for the data symbol $\mathbf{d}_{i}=\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]$
in Algorithm~\ref{alg:CTUpp_ButterflyConstellationDesign} (lines~\ref{alg_line:CTUpp_input_data},~\ref{alg_line:CTUpp_const_symbols}).
The resulting constellation symbols are successively transmitted by
$S_{A}$ (simultaneously with $s_{B,j}$ from $S_{B}$) towards the
relay node.

\subsubsection{Relay processing}

The crucial part of the encoded WBN system processing is based at
the relay node. Like the uncoded case, the relay must decode jointly
the \emph{superposed} data sub-words ($\mathbf{D}_{A}^{s},\,\mathbf{D}_{B}^{s}$)
along with the \emph{WNC function }of \emph{basic} data sub-words
($f(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})=\mathbf{D}_{A}^{b}\oplus\mathbf{D}_{B}^{b}$).
Whilst both $\mathbf{D}_{A}^{s},\,\mathbf{D}_{B}^{s}$ can be decoded
straightforwardly by the relay (using conventional single user decoders
$\mathcal{C}_{s}^{-1}$), the fundamental question is how to decode
the WNC function $f(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})$ since
both $\mathbf{D}_{A}^{b},\,\mathbf{D}_{B}^{b}$ are encoded separately
at sources $S_{A},\,S_{B}$\footnote{Note that separate decoding of $\mathbf{D}_{A}^{b},\,\mathbf{D}_{B}^{b}$
and subsequent evaluation of $f(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})$
(i.e. conventional joint/multi-user decoding concatenated with traditional
network coding\cite{Yeung-Li-etal_NetworkCodingTheory}) can significantly
limit the performance of the system \cite{Sykora-Burr_2011-TVT}.}. Fortunately, as proven in \cite{Sykora-Burr_2011-TVT}, the WNC
function $f(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})$ can be decoded
directly from the relay observation (\ref{eq:CTUpp_relay-received}),
if the particular source data words are encoded by the same linear
encoder $\mathcal{C}_{b}$, since
\begin{align}
\mathcal{C}_{b}\left(f(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})\right) & =\mathcal{C}_{b}\left(\mathbf{D}_{A}^{b}\oplus\mathbf{D}_{B}^{b}\right)\nonumber \\
 & =\mathcal{C}_{b}(\mathbf{D}_{A}^{b})\oplus\mathcal{C}_{b}(\mathbf{D}_{B}^{b})\nonumber \\
 & =\mathbf{C}_{A}^{b}\oplus\mathbf{C}_{B}^{b},
\end{align}
where $\mathbf{C}_{A}^{b}\oplus\mathbf{C}_{B}^{b}$ itself is again
a valid codeword and hence the WNC function $f(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})$
can be decoded directly from the relay observation (using a conventional
single user decoder $\mathcal{C}_{b}^{-1}$).

After decoding all required data streams ($\mathbf{\hat{D}}_{A}^{s},\,\hat{\mathbf{D}}_{B}^{s},\,\hat{f}(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})$),
the relay creates a joint data word $\mathbf{D}_{R}=[\mathbf{\hat{D}}_{A}^{s},\hat{\mathbf{D}}_{B}^{s},\hat{f}(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})]$
and re-encodes it as $\mathcal{C}_{R}(\mathbf{D}_{R})=\mathbf{C}_{R}=[\mathbf{c}_{R,0},\mathbf{c}_{R,1},\dots,\mathbf{c}_{R,\mathcal{N}-1}]$.
The encoded data are then mapped to the output $2^{N_{R}}$-QAM (where
$N_{R}=2N_{s}+N_{b}$) constellation symbols $s_{R,j}=\mathcal{A}^{R}\left(\mathbf{c}_{r,j}\right)$,
$j\in\{0,1,\dots,\mathcal{N}-1\}$ and broadcast by the relay to both
destination nodes.
\begin{figure*}
\begin{centering}
\includegraphics[width=1\textwidth]{fig/butterfly-2level_processing_principleTWC-coded}
\par\end{centering}

\caption{Relaying scheme in the encoded WBN system. SODEM stands for a soft-output
demodulator, IC is the interference canceler. The channel encoders/decoders
which are appended to the uncoded system are emphasized. \label{fig:CTUpp_Information-flow-coded-block-scheme}}
\vspace*{-3ex}
\end{figure*}

\subsubsection{Destination processing}

As in the uncoded case, destinations $D_{A},\,D_{B}$ firstly store
the signal received in the MA phase, and then, after decoding the
relay data word $\mathbf{D}_{R}$ (from the signal received in the
BC phase), both destinations can perform IC to remove the unintended
superposed codewords from the MA phase signal to get the desired HSI
and then finally recover the desired data (see Fig.~\ref{fig:CTUpp_Information-flow-coded-block-scheme}
for the details).

\subsection{Analysis of Transmission Rates}

The last step in the design of a feasible modulation and coding scheme
for WBN (see Fig.~\ref{fig:CTUpp_Information-flow-coded-block-scheme})
is to identify the range of permissible transmission rates for the
basic ($r_{b}$), superposed ($r_{s}$) and relay output ($r_{R}$)
data streams. To achieve this goal, we analyze the Constellation Constrained
(CC) capacities \cite{Biglieri_CodWirelessChan} of the proposed source
constellations, including the CC capacity of the conventional relay
output $2^{N_{R}}$-QAM alphabets (used in the BC phase of communication).

The transmission rates are defined in bits per channel use, and hence
$r_{i}=N_{i}\cdot\nicefrac{k_{\mathbf{D}}^{i}}{n_{\mathbf{C}}^{i}}$,
where $N_{i}$ is the number of bits per channel symbol/use in the
data stream $i,$ $i\in\{b,s,R\}$. In accordance with the definition
of source and relay codewords, we assume that each communication round
requires $2\mathcal{N}$ channel uses, where the length of both MA
and BC phase is set to $\mathcal{N}$ channel uses. Note that the
assumption that BC and MA phases have identical length is generally
only suboptimal (see e.g. \cite{Popovski-Yomo_2007a,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}),
but nevertheless it is a common assumption in practical systems and
hence we limit our attention to this particular case.

\subsubsection{Relay observation}

After splitting the source data streams, the whole system can be interpreted
as a 4-user system where the relay has to decode the data $\mathbf{D}_{A}^{s},\,\mathbf{D}_{B}^{s},\,f(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})$
from the \emph{virtual 3-user }($S_{A}^{s},\,S_{B}^{s},\,S_{AB}^{b}$)
\emph{multiple-access channel} observation (see Fig.~\ref{fig:CTUpp_Information-flow-coded-block-scheme}).
Unfortunately, since one of the users ($S_{AB}^{b}$) is only virtual,
we cannot simply claim that the region of achievable rates in this
virtual channel can be derived directly from the conventional cut-set
bound analysis (see e.g. \cite{Cover-Thomas_ElemInfTheory,Harshan-Rajan-2011-IEEE-T-IT}),
but rather a careful information-theoretic analysis would be required
to identify the exact rate region. However, such analysis is far beyond
the scope of this paper, and hence, for simplicity reasons, we only
conjecture that the eligible source rates ($r_{b},\,r_{s}$) are limited
by the conventional CC multiple-access capacity region \cite{Cover-Thomas_ElemInfTheory,Harshan-Rajan-2011-IEEE-T-IT},
which can be defined by the following set of mutual informations $I(\centerdot;\centerdot)$:
\begin{align}
2r_{s}+r_{b} & \leq I(x;\mathbf{c}_{A}^{s},\mathbf{c}_{B}^{s},f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})),\label{eq:CTUpp_CSB_3}\\
2r_{s} & \leq I(x;\mathbf{c}_{A}^{s},\mathbf{c}_{B}^{s}|f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})),\label{eq:CTUpp_CSB_2a}\\
r_{s}+r_{b} & \leq I(x;\mathbf{c}_{A}^{s},f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})|\mathbf{c}_{B}^{s}),\label{eq:CTUpp_CSB_2b}\\
r_{s}+r_{b} & \leq I(x;\mathbf{c}_{B}^{s},f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})|\mathbf{c}_{A}^{s}),\label{eq:CTUpp_CSB_2c}\\
r_{s} & \leq I(x;\mathbf{c}_{A}^{s}|\mathbf{c}_{B}^{s},f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})),\label{eq:CTUpp_CSB_1a}\\
r_{s} & \leq I(x;\mathbf{c}_{B}^{s}|\mathbf{c}_{A}^{s},f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})),\label{eq:CTUpp_CSB_1b}\\
r_{b} & \leq I(x;f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})|\mathbf{c}_{A}^{s},\mathbf{c}_{B}^{s}),\label{eq:CTUpp_CSB_1c}
\end{align}
where (\ref{eq:CTUpp_CSB_3}), (\ref{eq:CTUpp_CSB_2a})-(\ref{eq:CTUpp_CSB_2c})
and (\ref{eq:CTUpp_CSB_1a})-(\ref{eq:CTUpp_CSB_1c}) are the corresponding
third, second and first order cut-set bounds (respectively). As we
show later, the CC MAC region (as defined by (\ref{eq:CTUpp_CSB_3})-(\ref{eq:CTUpp_CSB-HSI-A}))
provides a reasonable estimate of the maximal achievable source transmission
rate pair ($r_{b},\,r_{s}$) in WBN.

Since the superposed data sub-words $\mathbf{D}_{A}^{s},\,\mathbf{D}_{B}^{s}$
are mapped to orthogonal ASK sets (Algorithm~\ref{alg:CTUpp_ButterflyConstellationDesign}),
the 2nd order cut-set bound $I(x;\mathbf{c}_{A}^{s},\mathbf{c}_{B}^{s}|f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b}))$
(\ref{eq:CTUpp_CSB_2a}) is equivalent to $I(x;\mathbf{c}_{A}^{s}|\mathbf{c}_{B}^{s},f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b}))+I(x;\mathbf{c}_{B}^{s}|\mathbf{c}_{A}^{s},f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b}))$
(defined in eqs. (\ref{eq:CTUpp_CSB_1a}) and (\ref{eq:CTUpp_CSB_1b})),
which can be proven easily by the chain rule for mutual information
of orthogonal signal sets (see \cite{Cover-Thomas_ElemInfTheory}).
Moreover, due to the assumed WBN system symmetry, the cut-set bounds
defined in equations (\ref{eq:CTUpp_CSB_1a}), (\ref{eq:CTUpp_CSB_1b})
are identical, and the same is true for the pair of cut-set bounds
defined in (\ref{eq:CTUpp_CSB_2b}), (\ref{eq:CTUpp_CSB_2c}). Consequently,
the CC multiple-access capacity region is completely defined by the
four inequalities in (\ref{eq:CTUpp_CSB_3}), (\ref{eq:CTUpp_CSB_2b}),
(\ref{eq:CTUpp_CSB_1a}) and (\ref{eq:CTUpp_CSB_1c}).

\subsubsection{Effective HSI channels}

In addition to the successful relay decoding, the transmission rate
of the basic information stream $r_{b}$ must guarantee that the HSI
(given by the unintended data sub-words $\mathbf{D}_{A}^{b}$ at $D_{B}$
and $\mathbf{D}_{B}^{b}$ at $D_{A}$) can be decoded at both destinations
(after perfect IC of superposed data codewords $\mathbf{C}_{A}^{s}$
at $D_{B}$ and $\mathbf{C}_{B}^{s}$ at $D_{A}$ from the stored
MA phase signal). Note that since we assume that the relay has already
successfully decoded $f(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})$ at
this step, it can be efficiently exploited in the decoding process,
resulting in the following upper-bounds on the source rate $r_{b}$:
\begin{align}
r_{b} & \leq I(z_{B}^{\text{IC}};\mathbf{c}_{A}^{b}|f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})),\label{eq:CTUpp_CSB-HSI-B}\\
r_{b} & \leq I(z_{A}^{\text{IC}};\mathbf{c}_{B}^{b}|f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})),\label{eq:CTUpp_CSB-HSI-A}
\end{align}
where $z_{A}^{\text{IC}},\,z_{B}^{\text{IC}}$ are the efficient HSI
observations (after perfect IC) at $D_{A},\,D_{B}$ (respectively)
\textendash{} see Fig.~\ref{fig:CTUpp_Information-flow-coded-block-scheme}.
Both (\ref{eq:CTUpp_CSB-HSI-B}), (\ref{eq:CTUpp_CSB-HSI-A}) are
identical in the symmetric WBN system.
\begin{figure*}
\begin{centering}
\hspace*{-1.5em}\includegraphics[width=0.7\columnwidth]{fig/Rate_Regions_XOR_map_BC10_MAC12_HSI8}
\par\end{centering}

\begin{centering}
\includegraphics[width=0.7\textwidth]{fig/Rate_Regions_XOR_map_BC5_MAC5_HSI0}
\par\end{centering}

\caption{Numerically evaluated cut-set bounds (mutual information for finite
input constellations) for $(N_{b}=2,N_{s}=1)$ source constellations
and $16$-QAM at the relay. The particular SNR conditions are available
in the titles of both sub-figures.\label{fig:CTUpp_CSB_eval}}
\end{figure*}

\subsubsection{Relay broadcast channel}

The relay rate $r_{R}$ must guarantee that its data word $\mathbf{D}_{R}=[\mathbf{\hat{D}}_{A}^{s},\hat{\mathbf{D}}_{B}^{s},\hat{f}(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})]$
with length $\left|\mathbf{D}_{R}\right|=2k_{\mathbf{D}}^{s}+k_{\mathbf{D}}^{b}=\mathcal{N}(2r_{s}+r_{b})$
can be sent to both destinations in $\mathcal{N}$ channel uses. In
addition to this, to enable successful decoding of the relay data
at both destinations, the relay transmission rate $r_{R}$ must be
below the CC capacities of the corresponding relay$\rightarrow$destination
channels. Thus, the relay rate should be set to $r_{R}=r_{b}+2r_{s}$,
which gives us the last two inequalities for $r_{b},\,r_{s}$:
\begin{align}
r_{R}=2r_{s}+r_{b} & \leq I(y_{A};\mathbf{c}_{R}),\label{eq:CTUpp_CSB-D_A}\\
r_{R}=2r_{s}+r_{b} & \leq I(y_{B};\mathbf{c}_{R}),\label{eq:CTUpp_CSB-D_B}
\end{align}
where both cut-set bounds (\ref{eq:CTUpp_CSB-D_A}), (\ref{eq:CTUpp_CSB-D_B})
are identical due to the system symmetry.

\subsection{Transmission Rate Region for Fixed Source Constellation\label{sub:CTUpp_Transmission-Rate-Region}}

To identify the region $\left(r_{b},\,r_{s}\right)\in\mathcal{R}^{(N_{b},N_{s})}$
of eligible transmission rates for a fixed $(N_{b},N_{s})$ source
constellation, we can evaluate numerically\footnote{The (conditional) probability density function $p(x|\mathbf{c}_{A}^{s},\mathbf{c}_{B}^{s},f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b}))$
which is required for the evaluation of particular mutual information
in (\ref{eq:CTUpp_CSB_3})-(\ref{eq:CTUpp_CSB-HSI-A}) can be obtained
by a proper marginalization operation $p(x|\mathbf{c}_{A}^{s},\mathbf{c}_{B}^{s},f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b}))=\mathrm{Pr}\left\{ f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})\right\} \cdot\sum_{\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b}:f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})}p\left(x|\mathbf{c}_{A}^{s},\mathbf{c}_{B}^{s},\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b}\right)$,
where $p(x|\mathbf{c}_{A}^{s},\mathbf{c}_{B}^{s},\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})$
is the likelihood function. For more details on the evaluation of
CC capacity for finite input constellations see e.g. \cite{Harshan-Rajan-2011-IEEE-T-IT,Sykora-Burr_2011-TVT}.} the set of relevant cut-set bounds (i.e. (\ref{eq:CTUpp_CSB_3}),
(\ref{eq:CTUpp_CSB_2b}), (\ref{eq:CTUpp_CSB_1a}), (\ref{eq:CTUpp_CSB_1c}),
(\ref{eq:CTUpp_CSB-HSI-B}) and (\ref{eq:CTUpp_CSB-D_A})) for given
SNR conditions in the symmetric WBN system ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$).
An example analysis of the source transmission rate region $\mathcal{R}^{(2,1)}$
for the $(N_{b}=2,\,N_{s}=1)$ source constellation is visualized
in Fig.~\ref{fig:CTUpp_CSB_eval} for two different SNR setups. The
cut-set bound rate region $\mathcal{R}^{(N_{b},N_{s})}$ is emphasized
by the shaded area and the rate pair with maximal $r_{b}+r_{s}$ is
identified in the figure. We have assumed that the source$\rightarrow$relay
channels are AWGN (or equivalently that perfect source phase prerotation
\cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008}
is implemented) in the numerical evaluation.

\section{Performance Analysis II: Adaptive Encoded System\label{sec:CTUpp_Performance-Analysis-Coded}}

As shown in Fig.~\ref{fig:CTUpp_CSB_eval}, the performance of the
encoded WBN system is, like in the uncoded case, influenced by the
immediate SNR conditions (given by $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$)
and hence an \emph{adaptive modulation and coding scheme }is again
of interest. However, before we introduce the\emph{ SNR mapping operation}
for the encoded system, we show that the cut-set bound rate regions
$\mathcal{R}^{(N_{b},N_{s})}$ (as introduced in the preceding section)
provide a reasonable approximation of achievable source transmission
rate pairs in the symmetric WBN system. In the whole section we assume
(for simplicity reasons) that perfect source phase prerotation \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008}
is implemented in the system, virtually reverting the source$\rightarrow$relay
channels to the AWGN case.

\subsection{Numerical Simulation of Encoded WBN System Throughput\label{sub:Numerical-Simulation-of}}

We implement all constituent channel encoders in the WBN system (see
Fig.~\ref{fig:CTUpp_Information-flow-coded-block-scheme}) as parallel
concatenated turbo codes with random interleavers of length $\mathcal{N}=10^{5}$
symbols. By proper puncturing \cite{Schlegel-Perez_TrellisTurboCoding}
of the channel encoders' outputs we are able to set the source transmission
rates (separately for the basic and superposed streams) to an almost
arbitrary value in the range ($\nicefrac{1}{3}\rightarrow1$). We
set the initial source transmission rates to the maximum $r_{b}+r_{s}\in\mathcal{R}^{(N_{b},N_{s})}$
(as evaluated in Fig.~\ref{fig:CTUpp_CSB_eval}) and by proper adjustment
of the puncturing operation we successively decrease the source transmission
rates $r_{b},\,r_{s}$ until the SER performance drops to zero. As
one can see in Fig.~\ref{fig:CTUpp_CSB_eval}, the achieved transmission
rate pairs are relatively close to the maximal permissible values
and hence we can consider the cut-set bound rate region $\mathcal{R}^{(N_{b},N_{s})}$
(as discussed in Section \ref{sub:CTUpp_Transmission-Rate-Region})
to be a reasonable approximation of the achievable source transmission
rate region.

\subsection{Maximal Throughput of the Adaptive Modulation-Coding Scheme\label{sub:Maximal-Throughput-of}}

As in the uncoded case, the source nodes $S_{A},\,S_{B}$ in the adaptive
modulation-coding WBN system must be aware of the particular mapping
operation $(\hat{\gamma}_{{\rm {MAC}}},\,\hat{\gamma}_{{\rm {BC}}},\,\hat{\gamma}_{{\rm {HSI}}})\mapsto\left(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}};\,r_{b}^{\mathrm{II}},\,r_{s}^{\mathrm{II}}\right),$
providing the set of optimal (in the sense of maximal throughput)
constellation/encoder parameters for the given SNR conditions ($\hat{\gamma}_{{\rm {MAC}}},\,\hat{\gamma}_{{\rm {BC}}},\,\hat{\gamma}_{{\rm {HSI}}}$).
Note that, in general, all adaptive system parameters are functions
of the actual SNR conditions in the system. However, we mostly omit
the explicit notation in the following text for to aid readability.

The desired adaptive system parameters can be obtained in the following
two-step procedure. First of all, we analyze the cut-set bound rate
regions $\mathcal{R}^{(N_{b},N_{s})}$ (as discussed in Section \ref{sub:CTUpp_Transmission-Rate-Region})
to identify the maximal encoded system throughput $T_{C}^{(N_{b},N_{s})}$
for a fixed source constellation $(N_{b},N_{s})$:
\begin{align}
T_{C}^{(N_{b},N_{s})}(\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}) & =\max_{r_{b},r_{s}\in\mathcal{R}^{(N_{b},N_{s})}}(r_{b}+r_{s}),\\
 & =r_{b}^{\mathrm{max}}(N_{b},N_{s})+r_{s}^{\mathrm{max}}(N_{b},N_{s}).\label{eq:CTUpp_opt_rates}
\end{align}
 Then, an exhaustive search over the constellation parameters $N_{b},\,N_{s}$
can be performed to find the maximum encoded system throughput $T_{C}^{\mathrm{max}}$
for the given SNR conditions ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$):
\begin{equation}
T_{C}^{\mathrm{max}}(\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}})=T_{C}^{(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}})}=\max_{(N_{b},N_{s})}T_{C}^{(N_{b},N_{s})},\label{eq:CTUpp_Throughput_encoded}
\end{equation}
where $(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}})$ are the \emph{optimal
source constellation parameters}. The corresponding \emph{optimal
source transmission rates} (\ref{eq:CTUpp_opt_rates}) are given simply
by \emph{$r_{b}^{\mathrm{II}}=r_{b}^{\mathrm{max}}(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}})$,
$r_{s}^{\mathrm{II}}=r_{s}^{\mathrm{max}}(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}})$.}
\begin{figure*}
\centering{}\includegraphics[width=0.45\textwidth]{fig/Adaptive_Maps_overall_BC_7\lyxdot 5}~~~\includegraphics[width=0.45\textwidth]{fig/Adaptive_Maps_overall_BC_15\lyxdot 0}\caption{Maximal encoded system throughput $T_{C}^{\mathrm{max}}$ for $\gamma_{{\rm {BC}}}=7.5\,\mathrm{dB}$
and $\gamma_{{\rm {BC}}}=15\,\mathrm{dB}$.\label{fig:CTUpp_Coded_SNR_map} }
\end{figure*}
\begin{figure*}
\centering{}\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_coding_Gain7\lyxdot 5}~~~\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_coding_Gain15\lyxdot 0}\caption{Throughput enhancement $\Delta T_{C}=T_{C}^{\mathrm{max}}-T_{\mathrm{LB}}$
{[}bits/channel use{]} of the coded over uncoded WBN system for $\gamma_{{\rm {BC}}}=7.5\,\mathrm{dB}$
and $\gamma_{{\rm {BC}}}=15\,\mathrm{dB}$. Note that $0.75\leq\Delta T_{C}\leq2$
in the analyzed range of channel SNRs.\label{fig:CTUpp_Coded_ThroughputGain}}
\end{figure*}

The SNR mapping regions (including the throughput $T_{C}^{\mathrm{max}}$)
for the adaptive modulation and coding scheme in WBN are evaluated
as a function of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$ in
Fig.~\ref{fig:CTUpp_Coded_SNR_map} for $\gamma_{{\rm {BC}}}\in\{7.5\,\mathrm{dB},\,15\,\mathrm{dB}\}$.
As one can see in Fig.~\ref{fig:CTUpp_Coded_ThroughputGain}, the
increased reliability of transmissions on all individual channels
in WBN (as compared to the uncoded system) translates directly into
a significant enhancement of throughput performance in the whole range
of observed SNRs. This observation justifies the viability of the
proposed channel coding scheme.

\subsection{Robustness Analysis}

In this section we show that the proposed modulation and coding scheme
is viable even if the real world conditions induce some deviations
from the system model assumed in this paper. From a practical point
of view, we would be interested mainly in the situation, where a direct
channel between a source and its desired destination is present (see
Fig.~\ref{fig:CTUpp_DirectChannel}). Even though that this \textquotedbl{}direct\textquotedbl{}
channel can be relatively weak, it inevitably affects the destinations'
HSI observations. In addition to this, we analyse the system where
source phase pre-rotation is switched off (or ineffective due to rapid
channel dynamics), and thus the relay faces a multiple-access channel
with a varying source channel phase offset. This assumption is valid
for a practical system where the applicability of source phase pre-rotation
is limited due to the unavailable ideal feedback channel or because
of the undesirable delay induced by the feedback in the pre-rotation
operation. To demonstrate the robustness of the proposed modulation
and coding strategy, we compare the WBN performance results achieved
by the Monte-Carlo numerical evaluation (see section \ref{sub:Numerical-Simulation-of})
with USRP HW measurements. While in the numerical evaluation we still
keep the idealized assumptions as defined by our system model (i.e.
no direct source$\rightarrow$destination channels, perfect channel
phase pre-rotation), in the HW measurements we now let all data communication
to be performed through real wireless channels (compare with the HW
setup in section~\ref{sub:CTUpp_Hardware_Verification}), introducing
inevitably some direct channel observation at both destinations. In
addition, we allow the source phase pre-rotation to be switched off
in the HW measurements. The channel SNRs $\gamma_{{\rm {MAC}}},\gamma_{{\rm {HSI}}}$
in the HW measurements can be controlled by the source transmit power
adjustment and similarly, particular values of $\gamma_{{\rm {BC}}}$
can be set up by the adjustment of the relay transmit power.
\begin{figure}
\begin{centering}
\includegraphics[width=0.75\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_directLink}
\par\end{centering}

\centering{}\caption{Direct channel at destination $D_{B}$ in the robustness analysis
(likewise, a direct channel is assumed to be present also at $D_{A}$).\label{fig:CTUpp_DirectChannel}}
\end{figure}

To perform a comparison of the idealized numerical evaluation with
the HW robustness measurements, we evaluate the range of SNRs where
a zero error rate performance can be achieved for fixed constellations
and channel encoder rates $(N_{b},N_{s},r_{b},r_{s})$. To achieve
this, we identify the triplet of SNRs ($\gamma_{{\rm {MAC}}},\gamma_{{\rm {HSI}}}$,
$\gamma_{{\rm {BC}}}$) providing a zero-error rate performance at
both destinations. This SNR triplet then defines the lower-most corner
of the SNR region where a zero error rate performance can be achieved
(see Fig. \ref{fig:CTUpp_Robustenss_analysis}). We can conclude that:
\begin{itemize}
\item The presence of direct links requires only a slightly increased values
of ($\gamma_{{\rm {MAC}}},\gamma_{{\rm {HSI}}}$, $\gamma_{{\rm {BC}}}$)
to ensure a zero error-rate performance for the fixed $(N_{B},N_{S},r_{b},r_{s})$.
However, it is evident that a modification of the proposed modulation
and coding scheme could be desirable to fully harness the information
transmitted over direct source destination channels.
\item The source channel phase asynchrony in the system with direct links
further degrades the performance on the sources$\rightarrow$relay
channel and thus an additional increase of the source transmission
power (and consequently $\gamma_{{\rm {MAC}}}$) is required to provide
a zero-error rate. However, $\gamma_{{\rm {BC}}}$ is not affected
in this case, as the channel pre-rotation does not have any impact
on the relay$\rightarrow$destination performance.
\end{itemize}

\section{Conclusions and Future Work\label{sec:CTUpp_DiscussionConclusions-etc}}

In this paper we have proposed a systematic algorithm for the design
of two-source constellations in the WBN system. The Algorithm~\ref{alg:CTUpp_ButterflyConstellationDesign}
allows the matching of the constellation parameters to virtually any
SNR conditions in the system, enabling a direct implementation of
the adaptive constellation mapping scheme. The viability of the proposed
constellation design was verified by a means of numerical analysis
and simulations and also by a real-world HW experiment (based on Ettus
Research USRPs), including a HW-based robustness analysis.

Even in the uncoded scenario, the proposed constellations are able
to significantly boost the WBN system throughput, and hence even their
uncoded implementation can be interesting, especially in some basic
wireless networks where channel coding is avoided to reduce complexity
(e.g. in sensor networks). Furthermore, we have shown that the proposed
source constellation design can be readily extended with appropriately
designed channel encoding/decoding operations, significantly improving
the reliability (including the throughput) of the resulting adaptive
modulation-coding scheme.

In future work, we would like to focus on a full adaptive HW implementation
of the proposed system, where the impact of several other parameters
(e.g. channel fading and dynamics, asymmetry of channel gains etc.)
can significantly affect the system performance and possibly even
require some modifications of the adaptive system design.
\begin{figure*}
\centering{\includegraphics[width=1\textwidth]{fig/Robust_20}
\includegraphics[width=1\textwidth]{fig/Robust_21}}
\caption{Robustness analysis for two fixed $(N_{b},N_{s},r_{b},r_{s})$ scenarios.
\label{fig:CTUpp_Robustenss_analysis}}
\end{figure*}

\pagebreak{}

\section*{Declarations}

This work was partly reported in IEEE ICC \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}.

\section*{Funding}

This work has been performed in the framework of the European research
project DIWINE, which is partly funded by the European Union under
its FP7 ICT Objective 1.1 - The Network of the Future. Work of Pavel
Prochazka and Tomas Uricar was also partially supported by the Grant
Agency of the Czech Technical University in Prague, SGS project SGS16/094/OHK3/1T/13.

\bibliographystyle{ieeetr}
\bibliography{bib/bib,bib/uricar,bib/uricar-papers,bib/uricar-books,bib/sykora,bib/books}

\end{document}

### 2016-12-04 alg4_final_TWC.tex
Pre-release version

 \begin{algorithmic}[1]
    \State \algorithmicrequire{ $\left(N_{b},\,N_{s}\right)$}  
    \State \textbf{for} $n_s \in \{0,\dots,N_s-1\}$ \Comment{"superposed levels"} 
      \State  ~~~$L_{A,n_s}^s \gets 2^{n_s}$,  $L_{B,n_s}^s\gets \jj 2^{n_s}$
      \label{alg_line:CTUpp_LAAssignment}
    \State \textbf{end}
    \State \textbf{for} $n_b \in \{0,\dots,N_b-1\}$ \Comment{"basic levels"} 
    \State ~~~~~~$L_{A,n_b}^b=L_{B,n_b}^b \gets 2^{N_s} \cdot 3^{\left\lfloor \nicefrac{n_b}{2}\right\rfloor }$ for even $n_b$     
    \label{alg_line:CTUpp_LAXORAssignment}
    \State ~~~~~~$L_{A,n_b}^b=L_{B,n_b}^b \gets \jj 2^{N_s} \cdot 3^{\left\lfloor \nicefrac{n_b}{2}\right\rfloor }$ for odd $n_b$ 
    \label{alg_line:CTUpp_LBXORAssignment}
    \State \textbf{end}
    \State $\alpha^{2}=\sum_{n_s=0}^{N_{s}-1}|L_{i,n_s}^{s}|^{2}+\sum_{n_b=0}^{N_{b}-1}|L_{i,n_b}^{b}|^{2}$ \Comment{"norm. coefficient"} \label{alg_line:CTUpp_normalization}
    \State \textbf{for} $i \in \{A,B\}$ and $\forall \mathbf{d}_{i}=\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]$, $d^b_{i,n_b},\,d^s_{i,n_s}\in\{0,1\}$: \label{alg_line:CTUpp_input_data}
    \State ~~~\textbf{for} $n_s \in \{0,N_s-1\}$,\, $n_b \in \{0,N_b-1\}$
	\State ~~~~~~$s_{i,n_s}^{s}=L_{i,n_s}^{s}\left(2d_{i,n_s}^{s}-1\right)$
	\State ~~~~~~$s_{i,n_b}^{b}=L_{i,n_b}^{b}\left(2d_{i,n_b}^{b}-1\right)$
      \State ~~~\textbf{end}
      \State ~~~$s_{i}=\mathcal{A}^{i}\left(\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]\right)=\alpha^{-1}\left(\sum_{n_s=0}^{N_{s}-1}s_{i,n_s}^{s}+\sum_{n_b=0}^{N_{b}-1}s_{i,n_b}^{b}\right)$  \Comment{"constellation symbols"}  \label{alg_line:CTUpp_const_symbols}
	 \State \textbf{end}

	\State \algorithmicensure{ Constellation alphabets $\mathcal{A}^A,\,\mathcal{A}^B$.}
  \end{algorithmic}

### 2016-12-04 nomen.tex
Pre-release version

%% LyX 2.1.5 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{nomencl}
% the following is useful when we have the old nomencl.sty package
\providecommand{\printnomenclature}{\printglossary}
\providecommand{\makenomenclature}{\makeglossary}
\makenomenclature
\usepackage{babel}
\begin{document}

\title{Nomenclature}

\maketitle
\nomenclature{WBN}{Wireless Butterfly Network}\nomenclature{WNC}{Wireless Network Coding}\nomenclature{HW}{Hardware}\nomenclature{SNR}{Signal to Noise Ratio}\nomenclature{SC}{Superposition Coding}\nomenclature{HSI}{Hierarchical Side Information}\nomenclature{DEM}{Demodulator}\nomenclature{IC}{Interference Cancellation}\nomenclature{MA}{Multiple Access}\nomenclature{AWGN}{Aditive White Gaussian Channel}\nomenclature{ASK}{Amplitude Shift Keying}\nomenclature{QAM}{Quadrature Amplitude Modulation}\nomenclature{SER}{Symbol Error Rate}\nomenclature{FER}{Frame Error Rate}\nomenclature{SDR}{Software Defined Radio}\nomenclature{USRP}{Universal Software Radio Peripherals}\nomenclature{UHD}{USRP Hardware Driver }\nomenclature{CP}{Cyclic Prefix}\nomenclature{ODFD}{Orthogonal Frequency Division Multiplexing}\nomenclature{DC}{Direct Current}\nomenclature{MIMO}{Multiple Input Multiple Output}\nomenclature{QPSK}{Quadrature Phase Shift Keying}\nomenclature{UDP}{User Datagram Protocol}\nomenclature{BC}{Broadcast Channel}\nomenclature{MAC}{Multiple Access Channel}\nomenclature{CC}{Constellation Constrained}\settowidth{\nomlabelwidth}{AWGN}
\printnomenclature{}
\end{document}

### 2016-12-12 Const_design.tex
Renamed main body + added basic web presentation

--- 2016-12-04 Const_design_TVT.tex
@@
 %% Do not edit unless you really know what you are doing.
-\documentclass[letterpaper,english,10pt]{article}
+\documentclass[letterpaper,english,10pt]{bmc_template/bmcart}
 \usepackage{mathptmx}
@@
 \begin{document}
+\begin{frontmatter}
+
+\begin{fmbox}
+\dochead{Research Article}
 
@@
 
-\author{Pavel Prochazka, Tomas Uricar, David Halls and Jan Sykora}
-
-\maketitle
-{\footnotesize{}The corresponding author D. Halls is with the Toshiba
--- Telecommunication Research Laboratory (email: david.halls@toshiba-trel.com).
-Pavel Prochazka, Tomas Uricar and Jan Sykora were with the Czech Technical
-University in Prague, Czech Republic (e-mail: \textbackslash{}\{prochp10,
-uricatom, Jan.Sykora\textbackslash{}\}@fel.cvut.cz). }{\footnotesize \par}
-
-\thispagestyle{empty}
-
-\pagebreak{}
-\begin{abstract}
+\author[
+   addressref={aff1},
+   email={pavel@prochazka.info}
+]{\inits{PP}\fnm{Pavel} \snm{Prochazka}}
+\author[
+   addressref={aff1},
+   email={uricatom@fel.cvut.cz}
+]{\inits{TU}\fnm{Tomas} \snm{Uricar}}
+\author[
+   addressref={aff2},                   % id's of addresses, e.g. {aff1,aff2}
+   corref={aff2},                       % id of corresponding address, if any
+   %noteref={n1},                        % id's of article notes, if any
+   email={david.halls@toshiba-trel.com}   % email address
+]{\inits{DH}\fnm{David} \snm{Halls}}
+\author[
+   addressref={aff1},
+   email={jan.sykora@fel.cvut.cz}
+]{\inits{JS}\fnm{Jan} \snm{Sykora}}
+
+\address[id=aff1]{%                           % unique id
+  \orgname{Czech Technical University in Prague}, % university, etc
+  \street{Technicka 2},                     %
+  \postcode{16627}                                % post or zip code
+  \city{Prague},                              % city
+  \cny{CZ}                                    % country
+}
+\address[id=aff2]{%
+  \orgname{Toshiba -- Telecommunication Research Laboratory},
+  \street{32 Queen Square},
+  \postcode{BS1 4ND}
+  \city{Bristol,},
+  \cny{UK}
+}
+\end{fmbox}% comment this for two column layout
+
+\begin{abstractbox}
+
+\begin{abstract} % abstract
 In this paper we focus on the design of a reliable communication scheme
@@
 channel, we follow the paradigm of \emph{Wireless Physical Layer Network
-Coding} (WNC) and we show that the design of novel adaptive constellations\emph{
-}is desirable to exploit the promising performance of WNC in WBN.
+Coding} and we show that the design of novel adaptive constellations\emph{
+} is desirable to exploit the promising performance of wireless network coding in WBN.
 We introduce a \emph{systematic constellation design} algorithm and
@@
 conventional point-to-point modulations in WBN over the whole range
-of channel SNRs. To further support the applicability of the proposed
+of channel signal to noise ratios. To further support the applicability of the proposed
 constellations in a practical system, we integrate a simple binary
@@
 
-\subsubsection*{Keywords:}Wireless Network Coding, Butterfly Network, Relaying, Superposition
-Coding and Modulation
-
-\pagebreak
-\nomenclature{WBN}{Wireless Butterfly Network}\nomenclature{WNC}{Wireless Network
-Coding}\nomenclature{HW}{Hardware}\nomenclature{SNR}{Signal to Noise
-Ratio}\nomenclature{SC}{Superposition Coding}\nomenclature{HSI}{Hierarchical Side
-Information}\nomenclature{DEM}{Demodulator}\nomenclature{IC}{Interference
-Cancellation}\nomenclature{MA}{Multiple Access}\nomenclature{AWGN}{Additive White Gaussian
-Channel}\nomenclature{ASK}{Amplitude Shift Keying}\nomenclature{QAM}{Quadrature Amplitude
-Modulation}\nomenclature{SER}{Symbol Error Rate}\nomenclature{FER}{Frame Error
-Rate}\nomenclature{SDR}{Software Defined Radio}\nomenclature{USRP}{Universal Software Radio
-Peripherals}\nomenclature{UHD}{USRP Hardware Driver }\nomenclature{CP}{Cyclic
-Prefix}\nomenclature{ODFD}{Orthogonal Frequency Division Multiplexing}\nomenclature{DC}{Direct
-Current}\nomenclature{MIMO}{Multiple Input Multiple Output}\nomenclature{QPSK}{Quadrature Phase
-Shift Keying}\nomenclature{UDP}{User Datagram Protocol}\nomenclature{BC}{Broadcast
-Channel}\nomenclature{MAC}{Multiple Access Channel}\nomenclature{SODEM}{Soft Output Demodulator}\nomenclature{CC}{Constellation
-Constrained}%\settowidth{\nomlabelwidth}{AWGN} 
-\printnomenclature{} 
-\pagebreak
+\begin{keyword}
+\kwd{wireless network coding}
+\kwd{butterfly network}
+\kwd{relaying}
+\kwd{superposition coding}
+\kwd{superposition modulation}
+\end{keyword}
+
+% MSC classifications codes, if any
+%\begin{keyword}[class=AMS]
+%\kwd[Primary ]{}
+%\kwd{}
+%\kwd[; secondary ]{}
+%\end{keyword}
+
+\end{abstractbox}
+
+\end{frontmatter}
 
@@
 \hline 
-\end{tabular}\vskip1ex\caption{SC-based relaying scheme in uncoded WBN}.\label{tab:CTUpp_SC-relaying-scheme}
+\end{tabular}vskip1ex\caption{SC-based relaying scheme in uncoded WBN}.\label{tab:CTUpp_SC-relaying-scheme}
 \end{table}
@@
 \begin{centering}
-\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC16_BC20_N2}\vskip-2ex
+\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC16_BC20_N2}
 \par\end{centering}
@@
 \begin{centering}
-\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC17_BC17_N2}\vskip-2ex
+\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC17_BC17_N2}
 \par\end{centering}
@@
 \begin{centering}
-\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC20_N2}\vskip-2ex
+\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC20_N2}
 \par\end{centering}
@@
 \begin{centering}
-\hspace*{-0.04\columnwidth}\includegraphics[clip,width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC16_N2}\vskip-2ex
+\hspace*{-0.04\columnwidth}\includegraphics[clip,width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC16_N2}
 \par\end{centering}
@@
 
-\pagebreak{}
+\begin{backmatter}
+
+\nomenclature{WBN}{Wireless Butterfly Network}\nomenclature{WNC}{Wireless Network
+Coding}\nomenclature{HW}{Hardware}\nomenclature{SNR}{Signal to Noise
+Ratio}\nomenclature{SC}{Superposition Coding}\nomenclature{HSI}{Hierarchical Side
+Information}\nomenclature{DEM}{Demodulator}\nomenclature{IC}{Interference
+Cancellation}\nomenclature{MA}{Multiple Access}\nomenclature{AWGN}{Additive White Gaussian
+Channel}\nomenclature{ASK}{Amplitude Shift Keying}\nomenclature{QAM}{Quadrature Amplitude
+Modulation}\nomenclature{SER}{Symbol Error Rate}\nomenclature{FER}{Frame Error
+Rate}\nomenclature{SDR}{Software Defined Radio}\nomenclature{USRP}{Universal Software Radio
+Peripherals}\nomenclature{UHD}{USRP Hardware Driver }\nomenclature{CP}{Cyclic
+Prefix}\nomenclature{ODFD}{Orthogonal Frequency Division Multiplexing}\nomenclature{DC}{Direct
+Current}\nomenclature{MIMO}{Multiple Input Multiple Output}\nomenclature{QPSK}{Quadrature Phase
+Shift Keying}\nomenclature{UDP}{User Datagram Protocol}\nomenclature{BC}{Broadcast
+Channel}\nomenclature{MAC}{Multiple Access Channel}\nomenclature{SODEM}{Soft Output Demodulator}\nomenclature{CC}{Constellation
+Constrained}%\settowidth{\nomlabelwidth}{AWGN} 
+\printnomenclature{}
 
@@
 
+\section*{Competing Interests}
+The authors hereby confirm, having read SpringerOpen's guidance on competing interests, that we have no competing interests in the manuscript.
+
 \section*{Funding}
-
 This work has been performed in the framework of the European research
@@
 
-\bibliographystyle{ieeetr}
+\section*{Availability of Data and Materials}
+
+\bibliographystyle{bmc_template/bmc-mathphys}
 \bibliography{bib/bib,bib/uricar,bib/uricar-papers,bib/uricar-books,bib/sykora,bib/books}
 
+\end{backmatter}
 \end{document}

### 2016-12-12 web_pres/Constellation_Design_lib.py

@@ -1,0 +1,299 @@
+import numpy as np
+
+
+def find_levels(i, levels, const, const_el):
+    if (len(levels) == 0):
+        return np.array([0]) # Empty constellation --- zero point
+    else:
+        const_out = np.asarray([c + levels[i] * el for c in const for el in const_el])
+#    print np.sort(const_out)
+        i += 1
+        if (i < len(levels)):
+            return find_levels(i, levels, const_out, const_el)
+        else:
+            return const_out
+
+
+def eval_levels_XOR(Nb, Ns):  # Evaluate BPSK levels for given Nb, Ns -- complex channel
+    odd = np.mod(Nb, 2)
+    Ls = np.asarray([2**i for i in np.arange(0, Ns)]) # superposed levels
+    Lbt = 2**Ns * np.asarray([np.asarray([3**i, 1j*3**i]) for i in np.arange(0, Nb/2)]).flatten() # basic levels
+#  print np.abs(Ls), np.abs(Lb)
+    if odd == 1:
+        Lb = np.hstack([Lbt, 2**Ns * 3**((Nb-1)/2)])
+    else:
+        Lb = Lbt
+    return (Lb, Ls) # Basic and superposed levels
+
+def const_design_XOR(Nb, Ns, h = 1.): # Relative Channel Parameterization
+    (Lb, Ls) = eval_levels_XOR(Nb, Ns)
+    en = np.sum(np.abs(Lb)**2) + np.sum(np.abs(Ls)**2)
+    alpha = 1./np.sqrt(en)
+    sourceA_const = find_levels(0, np.hstack([Ls, Lb]), [0], [-1., 1.])*alpha
+    sourceB_const = find_levels(0, np.hstack([1j*Ls, Lb]), [0], [-1., 1.])*alpha
+    basic_part = find_levels(0,Lb, [0], [-1., 1.])*alpha
+    superposed_part = find_levels(0,Ls, [0], [-1., 1.])*alpha
+    relay_const = np.asarray([x + y * h for x in sourceA_const for y in sourceB_const])
+    return (sourceA_const, sourceB_const, basic_part, superposed_part, relay_const, alpha)
+
+
+
+#plt.plot(np.real(relay_const), np.imag(relay_const), 'ok', ms=10)
+
+
+#%%
+def intersect(lin, lin_vec):
+    '''
+    intersection of lines
+    '''
+    [a, b, c] = lin
+    res = []
+    for L2 in lin_vec:
[…]

### 2016-12-21 web_pres/Constellation_Design_lib.py
Almost working numerical simulation

@@ -358,18 +358,19 @@ def Draw_Received_Dest_MAC(ax, Nb, Ns, node='A'):
     ax.set_ylim([-1.5,1.5])
 
 def Draw_Received_Dest_MAC_IC(ax, Nb, Ns):
-    (sourceA_const, sourceB_const, basic_part, superposed_part, relay_const, alpha) = const_design_XOR(Nb, Ns, 1.)    
-    base_hatch_SRC = ['/','-', '+', 'x']
-    hatches_SRC = [''.join([base_hatch_SRC[int(i)] for i in np.base_repr(ind,len(base_hatch_SRC))]) for ind in range(2**Nb)]
-    C2B = np.arange(len(basic_part))
-    bords = Get_Dec_Region_Boundaries(basic_part, 1.5) #prepare decision regions for relay constellation
-    ax.axis('equal')
-    ax.set_xlim([-1.5,1.5])
-    ax.grid()    
-    #ax.set_ylim([-1.5,1.5])
-    Draw_dec_Boundaries(ax, bords, hatches_SRC, C2B, np.zeros(len(sourceA_const), bool))    
+    if Nb > 0:
+        (sourceA_const, sourceB_const, basic_part, superposed_part, relay_const, alpha) = const_design_XOR(Nb, Ns, 1.)    
+        base_hatch_SRC = ['/','-', '+', 'x']
+        hatches_SRC = [''.join([base_hatch_SRC[int(i)] for i in np.base_repr(ind,len(base_hatch_SRC))]) for ind in range(2**Nb)]
+        C2B = np.arange(len(basic_part))
+        bords = Get_Dec_Region_Boundaries(basic_part, 1.5) #prepare decision regions for relay constellation
+        ax.axis('equal')
+        ax.set_xlim([-1.5,1.5])
+        ax.grid()    
+        #ax.set_ylim([-1.5,1.5])
+        Draw_dec_Boundaries(ax, bords, hatches_SRC, C2B, np.zeros(len(sourceA_const), bool))    
 
-    ax.plot(np.real(basic_part), np.imag(basic_part), 'o', color='k', mew=3, ms=16, fillstyle='none')
+        ax.plot(np.real(basic_part), np.imag(basic_part), 'o', color='k', mew=3, ms=16, fillstyle='none')
 
 def insert_legend(Nb, Ns, ax):
[…]

### 2016-12-23 Const_design.tex
Prerelease

@@
 \usepackage{nomencl}
+\usepackage{url}
 % the following is useful when we have the old nomencl.sty package
@@
 pairs are not available in WBN and thus the help of the intermediate
-relay node is necessary to enable end-to-end communication. Please
-note that in this paper we do not limit our attention to the above
-mentioned special example of a high-speed, vehicle-based WBN.
+relay node is necessary to enable end-to-end communication. Note that some partial 
+source material from the implementation of this model can be found in
+\cite{Prochazka_Tutorial_WNC}.
 
@@
 \hline 
-\end{tabular}vskip1ex\caption{SC-based relaying scheme in uncoded WBN}.\label{tab:CTUpp_SC-relaying-scheme}
+\end{tabular}\caption{SC-based relaying scheme in uncoded WBN}.\label{tab:CTUpp_SC-relaying-scheme}
 \end{table}
@@
 \section*{Availability of Data and Materials}
+We are aware that the presented topic is difficult to understand without very specific background in wireless
+network coding. To help the reader to overcame this problem, we created a short tutorial \cite{Prochazka_Tutorial_WNC}.
+The tutorial first motivates the constellation design, then it shortly introduces the wireless
+network coding principle, its relation to conventional network coding. Many visual demonstrations of
+the proposed constellation design can be also found there. In addition to this, the supplementary
+Python code is available to the reader so that one can touch the topic also by means of implemented
+algorithms.
 

### 2016-12-23 web_pres/Constellation_Design_lib.py

@@ -537,6 +537,107 @@ def draw_Constellations_IC_withErrCirc(Nb, Ns, h, gMAC, gBC, gHSI):
     ax_DB_BC.set_title('Received $D_B$ - BC')
     Draw_Error_Circles(ax_DB_BC, QAM(Nb+2*Ns)[0], gBC)
 
+def to_ind(dAs, dBs, db, Aq_b, Aq_s):
+    return dAs*(Aq_b*Aq_s) + dBs*Aq_b + db
+
+def to_streams(ind, Aq_b, Aq_s):
+    return (ind / (Aq_b * Aq_s), ((ind % (Aq_b * Aq_s)) / Aq_b), ind % Aq_b)
+
+def run_chain(Nb, Ns, h, gMAC, gBC, gHSI, L = 1000, hAR = 1., hBR = 1., hRA = 1., hBA = 1.):
+    Aq_b = 2**Nb # Cardinality of alphabet in sources
+    Aq_s = 2**Ns # Cardinality of alphabet in sources
+    
+    # Evaluation of Gaussian variances
+    sigma2wMAC = SNR2sigma2w(gMAC)
+    sigma2wBC = SNR2sigma2w(gBC)
+    sigma2wHSI = SNR2sigma2w(gHSI)
+
+    # Evaluation of proper constellations
+    (sA_const, sB_const, basic_part, superposed_part, relay_const, alpha) = \
+                const_design_XOR(Nb, Ns, hBR/hAR)
+    # Source data
+    dAb = np.random.randint(Aq_b, size=L)  # basic part of source A data
+    dAs = np.random.randint(Aq_s, size=L)  # superposed part of source A data
+    dBb = np.random.randint(Aq_b, size=L)  # basic part of source B data
+    dBs = np.random.randint(Aq_s, size=L)  # superposed part of source B data
+    dA = (dAs, dAb) # source A data
+    dB = (dBs, dBb) # source B data
+
+    # Constellation mappers in sources
+    sAb = basic_part[dAb]
+    sBb = basic_part[dBb]
+    sAs = superposed_part[dAs]
+    sBs = 1j*superposed_part[dBs]
+    sA = sAs + sAb # Modulated data sA
+    sB = sBs + sBb # Modulated data sB
+
+    # Sources to relay channel
+    wR = np.sqrt(sigma2wMAC/2) * (np.random.randn(L) + 1j * np.random.randn(L))
+    xR = hAR * sA + hBR * sB + wR 
+
+    # Site Link 
[…]

### 2016-12-28 Const_design.tex
Presubmission v2

@@
 \begin{figure}
-\centering{}\includegraphics[width=0.6\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_v4}
+\centering{}
+\includegraphics[width=0.6\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_v4}
 \caption{Symmetric WBN model with half-duplex constraint and 2-phase communication.\label{fig:CTUpp_Information_flows}}
@@
 \begin{centering}
-\includegraphics[width=1\textwidth]{fig/butterfly-2level_processing_principleTWC-uncoded}
+\includegraphics[width=0.95\textwidth]{fig/butterfly-2level_processing_principleTWC-uncoded}
 \par\end{centering}
@@
 \begin{figure*}
-\centering{}\includegraphics[width=0.8\textwidth]{fig/d2_1}\caption{Source constellation design example for $N_{b}=2,\,N_{s}=1$. Resulting
+\centering{}
+\includegraphics[width=0.8\textwidth]{fig/d2_1}
+\caption{Source constellation design example for $N_{b}=2,\,N_{s}=1$. Resulting
 constellations are depicted as blue circles ($S_{A}$ output constellation),
@@
 \begin{centering}
-\includegraphics[width=1\textwidth]{fig/const_all_2}
+\includegraphics[width=0.95\textwidth]{fig/const_all_2}
 \par\end{centering}
@@
 \begin{figure}
-\centering{}\includegraphics[width=0.95\columnwidth]{fig/20150109_143009}\caption{Setup for HW evaluation (Ettus Research
+\centering{}
+\includegraphics[width=0.95\columnwidth]{fig/20150109_143009}
+\caption{Setup for HW evaluation (Ettus Research
 USRPs). Source transmissions are prerotated \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008}
@@
 \begin{centering}
-\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC16_BC20_N2}
+\hspace*{-0.04\columnwidth}
+\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC16_BC20_N2}
 \par\end{centering}
@@
 \begin{centering}
-\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC17_BC17_N2}
+\hspace*{-0.04\columnwidth}
+\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC17_BC17_N2}
 \par\end{centering}
@@
 \begin{centering}
-\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC20_N2}
+\hspace*{-0.04\columnwidth}
+\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC20_N2}
 \par\end{centering}
@@
 \begin{centering}
-\hspace*{-0.04\columnwidth}\includegraphics[clip,width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC16_N2}
+\hspace*{-0.04\columnwidth}
+\includegraphics[clip,width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC16_N2}
 \par\end{centering}
@@
 \begin{centering}
-\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC15}\quad\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC17}
+\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC15}
+\quad
+\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC17}
 \par\end{centering}
 
-\centering{}\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC20}\quad\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC25}\caption{Throughput performance $T_{\mathrm{LB}}$ and SNR mapping regions
+\centering{}
+\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC20}
+\quad
+\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC25}
+\caption{Throughput performance $T_{\mathrm{LB}}$ and SNR mapping regions
 (including the optimal const. parameters ($N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}$))
@@
 \begin{figure*}
-\centering{}\includegraphics[width=0.48\textwidth]{fig/XOR_map_Througput_BC20}\quad\includegraphics[width=0.48\textwidth]{fig/XOR_map_Througput_USRP_BC20}\caption{Comparison of $T_{\mathrm{LB}}$ and the throughput performance evaluated
+\centering{}
+\includegraphics[width=0.45\linewidth]{fig/XOR_map_Througput_BC20}
+\,
+\includegraphics[width=0.45\linewidth]{fig/XOR_map_Througput_USRP_BC20}
+\caption{Comparison of $T_{\mathrm{LB}}$ and the throughput performance evaluated
 in a real world adaptive HW setup ($T_{\mathrm{USRP}}$) for $\gamma_{{\rm {BC}}}=20\,\mathrm{dB}$.
@@
 \begin{centering}
-\includegraphics[width=1\textwidth]{fig/butterfly-2level_processing_principleTWC-coded}
+\includegraphics[width=0.95\textwidth]{fig/butterfly-2level_processing_principleTWC-coded}
 \par\end{centering}
@@
 \begin{centering}
-\hspace*{-1.5em}\includegraphics[width=0.7\columnwidth]{fig/Rate_Regions_XOR_map_BC10_MAC12_HSI8}
+\includegraphics[width=0.7\columnwidth]{fig/Rate_Regions_XOR_map_BC10_MAC12_HSI8}
 \par\end{centering}
@@
 \begin{figure*}
-\centering{}\includegraphics[width=0.45\textwidth]{fig/Adaptive_Maps_overall_BC_7\lyxdot 5}~~~\includegraphics[width=0.45\textwidth]{fig/Adaptive_Maps_overall_BC_15\lyxdot 0}\caption{Maximal encoded system throughput $T_{C}^{\mathrm{max}}$ for $\gamma_{{\rm {BC}}}=7.5\,\mathrm{dB}$
+\centering{}
+\includegraphics[width=0.45\textwidth]{fig/Adaptive_Maps_overall_BC_7\lyxdot 5}~~~
+\includegraphics[width=0.45\textwidth]{fig/Adaptive_Maps_overall_BC_15\lyxdot 0}
+\caption{Maximal encoded system throughput $T_{C}^{\mathrm{max}}$ for $\gamma_{{\rm {BC}}}=7.5\,\mathrm{dB}$
 and $\gamma_{{\rm {BC}}}=15\,\mathrm{dB}$.\label{fig:CTUpp_Coded_SNR_map} }
@@
 \begin{figure*}
-\centering{}\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_coding_Gain7\lyxdot 5}~~~\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_coding_Gain15\lyxdot 0}\caption{Throughput enhancement $\Delta T_{C}=T_{C}^{\mathrm{max}}-T_{\mathrm{LB}}$
+\centering{}
+\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_coding_Gain7\lyxdot 5}~~~
+\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_coding_Gain15\lyxdot 0}
+\caption{Throughput enhancement $\Delta T_{C}=T_{C}^{\mathrm{max}}-T_{\mathrm{LB}}$
 {[}bits/channel use{]} of the coded over uncoded WBN system for $\gamma_{{\rm {BC}}}=7.5\,\mathrm{dB}$
@@
 \bibliographystyle{bmc_template/bmc-mathphys}
-\bibliography{bib/bib,bib/uricar,bib/uricar-papers,bib/uricar-books,bib/sykora,bib/books}
+\bibliography{bib/Const_design}
 

### 2017-05-19 response_letter/response_letter.tex
Initial version of response letter

%% LyX 2.1.3 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
%\RequirePackage[loading]{tracefnt}
\documentclass[10pt,a4paper,titlepage,conference]{article}
\usepackage[T1]{fontenc}
%\usepackage[latin9]{inputenc}
%\usepackage[utf8]{inputenc}
%\usepackage[english]{babel} 
\usepackage{units}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
\special{papersize=\the\paperwidth,\the\paperheight}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
%\documentclass[8pt,titlepage,a4paper]{article}%{/usr/share/texmf-dist/tex/latex/IEEEtran/IEEEtran}
%\documentclass[11pt,titlepage,a4paper]{/usr/share/texmf-dist/tex/latex/IEEEtran/IEEEtran}
%\usepackage[latin2]{inputenc}
%\usepackage{times}
%\renewcommand\baselinestretch{1.5}  % 
\usepackage{color}
\usepackage{wrapfig}
\usepackage{epsfig}
%\usepackage{CoverPage}
\usepackage{multirow}
\usepackage{subfigure}
\usepackage{holtpolt}
\usepackage{turnstile}
\usepackage{tikz}
\usepackage{bm}
\usepackage{cite}
\usepackage[multiple]{footmisc}
%\usepackage{calrsfs}
\usetikzlibrary[arrows,decorations.pathmorphing,backgrounds,positioning,fit,petri]

\def\bo#1{{\bf{#1}}}
\def\E{{\rm{E}}}
\def\grebo#1{\mbox{\boldmath$#1$}}
\def\bold#1{\mbox{\boldmath$#1$}}
\def\conv{*}

\def\date#1{\def\@date{#1}}
\def\version#1{\def\@version{#1}}
\def\author#1{\def\@author{#1}}
\def\title#1{\def\@title{#1}}
\def\assignment#1{\def\@assignment{{\it #1}}}
\newcommand{\var}{\rm{var}}

\newcommand{\unfootnote}[1]{
  \renewcommand{\@makefnmark}{}
  \footnotetext{#1}
  \renewcommand{\@makefnmark}{\mbox{$^{\@thefnmark}$}}
}

% \papertitle[title of the paper][Author(s)][Conference type][date + place] 
%\graphicspath{{fig/}}

\begin{document}

\section{Common Questions and Corresponding Answers}
\begin{itemize}
  \item CQ1: \emph{Lacking novelty compared to ICC}
  \item A1: Quoting the part of the cover letter for IEEE transaction submission:\newline
  \sc{Compared with the conference version, the major contributions and differences of this submitted manuscript are summarized as follows:
  \begin{enumerate} 
  \item We introduce additional performance analysis results for constellations in an uncoded system and an in-depth discussion of the observed results.
  \item We extend the section dealing with the adaptive constellation design in an uncoded system and we supplement additional HW evaluation results for the adaptive system in the whole range of observed channel SNRs. Again a close agreement between between the analytic and measurement results is shown.
  \item We show how the channel coding can be integrated into the proposed constellation design, including the cut-set bound analysis of proper source transmission rates, which provides a hint for the setup of all channel encoders' rates in the system.
  \item We evaluate numerically the performance of the resulting adaptive modulation-coding scheme
  for a wide range of channel conditions in the WBN and we emphasise the performance gains with
    respect to the uncoded system.
  \item We perform a simple robustness analysis, demonstrating that the proposed modulation and coding strategy is viable even in the case when the real world condition induce some deviations from the mathematical system model assumed in the paper.
  \end{enumerate}
  }
  I believe that this answer could be enough. (Actualization -TODO)
\end{itemize}

\begin{itemize}
  \item CQ2: \emph{Better reference scenario?}
  \item A2: Related with two-step vs 3(4) step comparison requiring additional derivations (TODO)
\end{itemize}

\begin{itemize}
  \item CQ2: \emph{Typos and Formating Issues?}
  \item A3: We have proofreaded the manuscript for typos. Regarding the formating issues, we prefer
  to clean final version of the manuscript. (TODO)
\end{itemize}

\subsubsection*{Reviewer 1}
\begin{itemize}
  \item Q: \emph{The weak aspect of this paper is that the current paper is a small variation of a
  previous paper by the authors. The authors should further highlight the difference of this paper.}
  \item A: See A1
\end{itemize}

\begin{itemize}
  \item \emph{The authors should edit the paper more carefully. For example, in Figure 5, the
  references are missing. Please go over the whole the paper and make sure similar issues do not
  exist}
  \item A: See A3
\end{itemize}

\subsubsection*{Reviewer 2}
\begin{itemize}
  \item Q: \emph{Since this work builds upon previous work on the application of wireless network
  coding to the WBN, novelty is slightly lacking}
  \item A: see A1
\end{itemize}

\begin{itemize}
  \item Q: \emph{The proposed scheme appears to be quite specific to the WBN, I wonder if it is
  possible to generalize to other similar networks where linear codes yield a good performance.}
  \item A: We should stress that the modulation design covers both
  wireless network coding and processing the signal from multiple stages. Join generalization of
  both phenomenons in the way we did would be extremely challenging, because of synchronization,
  pre-rotation, etc. Also note that our approach is basically a practical instance of a well known
  theoretical principle with application of WNC to approximately equal power levels and
  interference cancellation on significantly different power levels. So that its generalization in
  theoretical level is already known. This answers also general comments.
\end{itemize}

\begin{itemize}
  \item Q: \emph{The authors should also provide more insight or intuition on the design of the
  constellation and explain why the challenges to apply to other linear networks.}
  \item A: The intuition beyond the design could be partly found in ICC (TODO)
\end{itemize}

\begin{itemize}
  \item Q: \emph{-It might be useful to the reader to add a figure for the butterfly network in the
  setting of algebraic network coding for comparison.}
  \item A: see A2
\end{itemize}

\subsubsection*{Reviewer 3}
\begin{itemize}
  \item Q: \emph{In figure 6, 7, 8, 9, the reference scheme using QPSK always has a zero throughput,
  which demonstrates that this reference modulation scheme does not work at all in WBN under the
  proposed SNRs. Then the proposed communication scheme is claimed to have performance enhancement
  for sure. However, logically, this only demonstrates that the proposed algorithm gives positive
    throughput in WBN instead of not working. But it is not enough to say it gives a "performance
    enhancement" comparing with a previous working scheme. So it would be better if the author can
    further compare some other modulation schemes which can also give some positive throughput in
    WBN.}
  \item A: partly see A2 for join decoding. Partly I remove throughput gain for (1,1) strategy
  compared to QPSK (TODO) 
\end{itemize}

\begin{itemize}
  \item Q: \emph{As far as we know, according to the 3GPP protocol, there is a Channel Quality Index
  (CQI) vs. modulation format table, which suggests the modulation scheme with respect to difference
  SNR range. According to this table, for example, for the SNR varying from 6dB to 20dB, the
  protocol suggests using 16QAM and 64QAM instead of QPSK. In WBN, it could be different from 3GPP,
  but I suggest the author to test some other reference modulation format and compare the
  difference. }
  \item A: The channel quality index is 3-dimensional (MAC, BC and HSI) in our case and we
    have it basically presented in the manuscript in form some cuts shown in figures. Its comparison
    with P2P case can be conducted in multiple ways (e.g. one can consider 4-step conventional P2P),
    but we solve again the problem two-step versus 4-step stage (see A2).
\end{itemize}

\begin{itemize}
  \item Q: \emph{Although, in the future work, the authors have mentioned the fading channel case, it would still be better that the case of fading channels or of longer communication distance could be simulated and experimented. AWGN channel seems to be too ideal. If some initial results on the fading channel case can be added into the paper, it would be better.}
  \item A: TODO (possible to play with in the tutorial)
\end{itemize}

\begin{itemize}
  \item Q: \emph{The robustness analysis is important, and the authors have done some simulations on this aspect. However, it would be more appreciated if a hardware experiment can be done on this aspect.}
  \item A: It actually is - check Figure 17
\end{itemize}

\begin{itemize}
  \item Q: \emph{In Fig. 15, the throughput enhancmence for the coding scheme is shown. It is
  interesting to see that the throughput enhancment has some "peak" and "valley" as the γ\_MAC
  increases. If possible, please give some explanation. Or this is just a random instance that
  happens to be shown by the hardware experiment, that is also fine.}
  \item A: The explanation here is quite straightforward, as it follows from the steep
  gradients of the uncoded throughput as function of SNRs shown in Figure 10. On the other hand the
  coded throughput as a function of SNRs is much smoother (Figure 14) and therefore their difference
  induces peeks and valleys
\end{itemize}

\begin{itemize}
  \item Q: \emph{There are also some minor context error or typos found}
  \item A: See A3
\end{itemize}

\section{Major Changes Summary}
\begin{itemize}
\item
\end{itemize}

\end{document}

### 2017-05-19 Const_design_final.tex
Added gitignore, figures, template and bibfile

--- 2016-12-28 Const_design.tex
@@
 \centering{}
-\includegraphics[width=0.6\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_v4}
 \caption{Symmetric WBN model with half-duplex constraint and 2-phase communication.\label{fig:CTUpp_Information_flows}}
@@
 \begin{centering}
-\includegraphics[width=0.95\textwidth]{fig/butterfly-2level_processing_principleTWC-uncoded}
 \par\end{centering}
@@
 \centering{}
-\includegraphics[width=0.8\textwidth]{fig/d2_1}
 \caption{Source constellation design example for $N_{b}=2,\,N_{s}=1$. Resulting
@@
 \begin{centering}
-\includegraphics[width=0.95\textwidth]{fig/const_all_2}
 \par\end{centering}
@@
 \centering{}
-\includegraphics[width=0.95\columnwidth]{fig/20150109_143009}
 \caption{Setup for HW evaluation (Ettus Research
@@
 \hspace*{-0.04\columnwidth}
-\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC16_BC20_N2}
 \par\end{centering}
@@
 \hspace*{-0.04\columnwidth}
-\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC17_BC17_N2}
 \par\end{centering}
@@
 \hspace*{-0.04\columnwidth}
-\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC20_N2}
 \par\end{centering}
@@
 \hspace*{-0.04\columnwidth}
-\includegraphics[clip,width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC16_N2}
 \par\end{centering}
@@
 \begin{centering}
-\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC15}
 \quad
-\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC17}
 \par\end{centering}
@@
 \centering{}
-\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC20}
 \quad
-\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC25}
 \caption{Throughput performance $T_{\mathrm{LB}}$ and SNR mapping regions
@@
 \centering{}
-\includegraphics[width=0.45\linewidth]{fig/XOR_map_Througput_BC20}
 \,
-\includegraphics[width=0.45\linewidth]{fig/XOR_map_Througput_USRP_BC20}
 \caption{Comparison of $T_{\mathrm{LB}}$ and the throughput performance evaluated
@@
 \begin{centering}
-\includegraphics[width=0.95\textwidth]{fig/butterfly-2level_processing_principleTWC-coded}
 \par\end{centering}
@@
 \begin{centering}
-\includegraphics[width=0.7\columnwidth]{fig/Rate_Regions_XOR_map_BC10_MAC12_HSI8}
 \par\end{centering}
@@
 \begin{centering}
-\includegraphics[width=0.7\textwidth]{fig/Rate_Regions_XOR_map_BC5_MAC5_HSI0}
 \par\end{centering}
@@
 \centering{}
-\includegraphics[width=0.45\textwidth]{fig/Adaptive_Maps_overall_BC_7\lyxdot 5}~~~
-\includegraphics[width=0.45\textwidth]{fig/Adaptive_Maps_overall_BC_15\lyxdot 0}
 \caption{Maximal encoded system throughput $T_{C}^{\mathrm{max}}$ for $\gamma_{{\rm {BC}}}=7.5\,\mathrm{dB}$
@@
 \centering{}
-\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_coding_Gain7\lyxdot 5}~~~
-\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_coding_Gain15\lyxdot 0}
 \caption{Throughput enhancement $\Delta T_{C}=T_{C}^{\mathrm{max}}-T_{\mathrm{LB}}$
@@
 \begin{centering}
-\includegraphics[width=0.75\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_directLink}
 \par\end{centering}
@@
 \begin{figure*}
-\centering{\includegraphics[width=1\textwidth]{fig/Robust_20}
-\includegraphics[width=1\textwidth]{fig/Robust_21}}
 \caption{Robustness analysis for two fixed $(N_{b},N_{s},r_{b},r_{s})$ scenarios.

### 2017-05-19 all_figures.tex
Added gitignore, figures, template and bibfile

--- 2016-12-04 Const_design_TVT.tex
@@
-%% LyX 2.1.5 created this file.  For more info, see http://www.lyx.org/.
-%% Do not edit unless you really know what you are doing.
-\documentclass[letterpaper,english,10pt]{article}
-\usepackage{mathptmx}
+\documentclass{article}
 \usepackage[T1]{fontenc}
@@
 \usepackage[dvips]{graphicx}
-\usepackage{setspace}
-\usepackage{wasysym}
-\usepackage{nomencl}
-% the following is useful when we have the old nomencl.sty package
-\providecommand{\printnomenclature}{\printglossary}
-\providecommand{\makenomenclature}{\makeglossary}
-\makenomenclature
-\doublespacing
-
-\makeatletter
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-\special{papersize=\the\paperwidth,\the\paperheight}
-
-%% Because html converters don't know tabularnewline
-\providecommand{\tabularnewline}{\\}
-%% A simple dot to overcome graphicx limitations
-\newcommand{\lyxdot}{.}
-
-\floatstyle{ruled}
-\newfloat{algorithm}{tbp}{loa}
-\providecommand{\algorithmname}{Algorithm}
-\floatname{algorithm}{\protect\algorithmname}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-\usepackage{babel}
-
-\usepackage{cite}
-\usepackage{color}
-\usepackage{bigdelim,multirow}
 \usepackage{tikz}
@@
 \usepackage{pgfplots}
-\usepackage{babel}
-\usepackage{multirow}
+\newcommand{\lyxdot}{.}
 
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-
-\usepackage{nicefrac}
-
-\usepackage{setspace}
-
-\renewcommand{\algorithmicrequire}{\textbf{Input:}}
-\renewcommand{\algorithmicensure}{\textbf{Output:}}
-
-%\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-%\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-%\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-
-% unnumbered footnote
-\makeatletter
-\newcommand{\unfootnote}[1]{
-  \renewcommand{\@makefnmark}{}
-  \footnotetext{#1}
-  \renewcommand{\@makefnmark}{\mbox{$^{\@thefnmark}$}}
-}
-\makeatother
-
-\newcommand{\jj}{\operatorname{j}}      % imaginary unit
-
-\makeatother
-
-\usepackage{babel}
 \begin{document}
-
-\title{Design of Adaptive Constellations and Error Protection Coding for
-Wireless Network Coding in 5-node Butterfly Networks}
-
-\author{Pavel Prochazka, Tomas Uricar, David Halls and Jan Sykora}
-
-\maketitle
-{\footnotesize{}The corresponding author D. Halls is with the Toshiba
--- Telecommunication Research Laboratory (email: david.halls@toshiba-trel.com).
-Pavel Prochazka, Tomas Uricar and Jan Sykora were with the Czech Technical
-University in Prague, Czech Republic (e-mail: \textbackslash{}\{prochp10,
-uricatom, Jan.Sykora\textbackslash{}\}@fel.cvut.cz). }{\footnotesize \par}
-
-\thispagestyle{empty}
-
-\pagebreak{}
-\begin{abstract}
-In this paper we focus on the design of a reliable communication scheme
-for generic 5-node Wireless Butterfly Networks (WBN). Since the WBN
-represents a natural extension of the basic 2-way relay communication
-channel, we follow the paradigm of \emph{Wireless Physical Layer Network
-Coding} (WNC) and we show that the design of novel adaptive constellations\emph{
-}is desirable to exploit the promising performance of WNC in WBN.
-We introduce a \emph{systematic constellation design} algorithm and
-we show that the proposed constellations are capable of outperforming
-conventional point-to-point modulations in WBN over the whole range
-of channel SNRs. To further support the applicability of the proposed
-constellations in a practical system, we integrate a simple binary
-channel coding scheme, providing a robust \emph{adaptive modulation
-and coding scheme} for relaying in symmetric WBNs with arbitrary channel
-conditions.
-\end{abstract}
-
-\subsubsection*{Keywords:}Wireless Network Coding, Butterfly Network, Relaying, Superposition
-Coding and Modulation
-
-\pagebreak
-\nomenclature{WBN}{Wireless Butterfly Network}\nomenclature{WNC}{Wireless Network
-Coding}\nomenclature{HW}{Hardware}\nomenclature{SNR}{Signal to Noise
-Ratio}\nomenclature{SC}{Superposition Coding}\nomenclature{HSI}{Hierarchical Side
-Information}\nomenclature{DEM}{Demodulator}\nomenclature{IC}{Interference
-Cancellation}\nomenclature{MA}{Multiple Access}\nomenclature{AWGN}{Additive White Gaussian
-Channel}\nomenclature{ASK}{Amplitude Shift Keying}\nomenclature{QAM}{Quadrature Amplitude
-Modulation}\nomenclature{SER}{Symbol Error Rate}\nomenclature{FER}{Frame Error
-Rate}\nomenclature{SDR}{Software Defined Radio}\nomenclature{USRP}{Universal Software Radio
-Peripherals}\nomenclature{UHD}{USRP Hardware Driver }\nomenclature{CP}{Cyclic
-Prefix}\nomenclature{ODFD}{Orthogonal Frequency Division Multiplexing}\nomenclature{DC}{Direct
-Current}\nomenclature{MIMO}{Multiple Input Multiple Output}\nomenclature{QPSK}{Quadrature Phase
-Shift Keying}\nomenclature{UDP}{User Datagram Protocol}\nomenclature{BC}{Broadcast
-Channel}\nomenclature{MAC}{Multiple Access Channel}\nomenclature{SODEM}{Soft Output Demodulator}\nomenclature{CC}{Constellation
-Constrained}%\settowidth{\nomlabelwidth}{AWGN} 
-\printnomenclature{} 
-\pagebreak
-
-\section{Introduction}
-
-The invention of Wireless Network Coding\emph{ }(WNC) has indeed provided
-a means for a significant enhancement in wireless system performance
-\cite{Popovski-Yomo_2007a,Nazer-Gastpar_2011-IEEE-P,Zhang-Liew-Lu_2012}.
-However, WNC processing has also revealed several non-trivial research
-problems which do not have counterparts in conventional point-to-point
-or multi-user systems, like the sensitivity to channel parameterization
-\cite{Koike-Popovski-Tarokh_2008,Liu-Tao-Xu_2011-ICC,Yasami-Razi-Abedi_2011,Uricar-Sykora_2011}
-or challenging multi-source transmission synchronization \cite{Zhang-Liew-Lam_2006b-ITW,Rosetto-Zorzi_2009-SPAWC,Huang-Wang-Song-Guo-Jamalipour_2012-IEEE-T-WC}.
-Furthermore, the specific characteristics of multi-node WNC systems
-can call also for novel constellation design approaches (see e.g.
-\cite{Uricar-Sykora_2011,Prochazka-Uricar-Halls-Sykora_2015-ICC}).
-
-In WNC the transmitted information symbols are allowed to interact
-directly in the constellation space, inducing a specific set of requirements
-on the constellations' properties and characteristics (see e.g. \cite{Uricar-Sykora_2011,Prochazka-Uricar-Halls-Sykora_2015-ICC}).
-Generally we can declare \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
-that any constellation suitable for the specific nature of WNC processing
-should be able to form\emph{ a superimposed constellation} with an
-appropriate structure at all receiving nodes (allowing direct decoding
-of specific WNC functions of user data from the received non-orthogonal
-signals \cite{Nazer-Gastpar_2008-ISIT,Sykora-Burr_2011-TVT}) and
-simultaneously it should be able to exploit the \emph{broadcast nature
-}of wireless channels (allowing a reduction in the consumption of
-channel resources in the system \cite{Popovski-Yomo_2007a}). Since
-both of these properties hinge on the actual SNR conditions in the
-system, the constellation design itself can become a relatively challenging
-task.
 \begin{figure}
@@
 
-One of the first attempts to design a suitable multi-source constellation
-for communication in a multi-node WNC system was introduced in our
-previous work \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}, where
-the \emph{adaptive 2-source constellations} for WNC-based communication
-in a 5-node \emph{Wireless Butterfly Network} (WBN) were developed.
-However, the results presented in \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
-are limited to an uncoded system, which significantly limits its practical
-applicability.
-
-In this paper we extend the communication scheme from \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
-by appending appropriate \emph{error protection coding} to the system,
-resulting in a practical channel-coded adaptive communication scheme
-for WBN. We provide the following results and contributions:
-\begin{enumerate}
-\item We summarize the \emph{systematic constellation design algorithm}
-from \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC} and we provide
-additional numerical results analysing its promising performance.
-\item We revise and extend the results discussing the \emph{adaptive capabilities
-of the constellations, }including \emph{the constellation mapping
-regions} for adaptive WBN relaying\emph{.}
-\item We validate the proposed design in a \emph{real-world HW setup}, including
-the HW evaluation of adaptive system performance.
-\item We show how the \emph{channel coding} can be integrated into the proposed
-constellation design, including the analysis of proper source transmission
-rates.
-\item We evaluate numerically the performance of the resulting \emph{adaptive
-modulation and coding} scheme for a wide range of channel conditions
-in the WBN.
-\item We show that the proposed design is viable even if the real-world
-conditions induce some deviation from the assumed system model.
-\end{enumerate}
-The rest of the paper is organized as follows. The system model, including
-all necessary definitions and details about WNC processing in WBNs
-is summarized in Section~\ref{sec:CTUpp_SystemModel}. A systematic
-\emph{constellation design algorithm} for WBNs is revised in Section~\ref{sec:CTUpp_Euclidean-Distance-based-Constel}.
-The performance analysis of the proposed constellations (including
-the HW evaluation) in an uncoded system is available in Section~\ref{sec:CTUpp_Performance-Analysis-Uncoded}.
-Section~\ref{sec:CTUpp_Adaptive-Constellation-Design} discusses
-an adaptive constellation design and Section~\ref{sec:CTUpp_Channel-Coding}
-introduces the channel coding extension to the system. The performance
-of the novel adaptive modulation and coding scheme is analyzed in
-Section~\ref{sec:CTUpp_Performance-Analysis-Coded}, including a
-simple robustness analyzis. Concluding remarks are summarized in Section~\ref{sec:CTUpp_DiscussionConclusions-etc}.
-
-\section{WNC Relaying in Wireless Butterfly Network\label{sec:CTUpp_SystemModel}}
-
-We assume a \emph{symmetric} WBN model \cite{Uricar-Qian-Sykora-Mow_2013-WCNC,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}
-with a half-duplex constraint (Fig. \ref{fig:CTUpp_Information_flows}).
-An example practical scenario complying with the WBN model is a communication
-among vehicles and road-side infrastructure nodes for traffic information
-exchange on a bidirectional highway within two time slots \cite{Ho-Liew-Lu}.
-The direct channels between the intended source$\rightarrow$destination
-pairs are not available in WBN and thus the help of the intermediate
-relay node is necessary to enable end-to-end communication. Please
-note that in this paper we do not limit our attention to the above
-mentioned special example of a high-speed, vehicle-based WBN.
-
-\subsection{Relaying Strategy}
-
-An information-theoretic relaying strategy (based on Superposition
-Coding (SC) \cite{Cover-Thomas_ElemInfTheory,Han-Kobayashi_1981,Shende-Rajan-2012-NCC,Popovski-Carvalho_2008})
-for WBNs was proposed in \cite{Uricar-Qian-Sykora-Mow_2013-WCNC,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}.
-The fundamental idea of the SC-approach is to split each data symbol
-$\mathbf{d}_{i}$ at source $i\in\left\{ A,B\right\} $ into the \emph{basic
-part} $\mathbf{d}_{i}^{b}=[d_{i,0}^{b},\dots,d_{i,N_{b}-1}^{b}]$
-and the \emph{superposed part} $\mathbf{d}_{i}^{s}=[d_{i,0}^{s},\dots,d_{i,N_{s}-1}^{s}]$,
-$d_{i,n}^{b},\,d_{i,n}^{s}\in\left\{ 0,1\right\} $, and then process
-each of the resulting data streams separately throughout the system
-(see Fig. \ref{fig:CTUpp_Information_flows}). While the basic part
-represents a \textquotedbl{}true WNC\textquotedbl{} information stream
-(limited by the amount of available HSI) in the system, the superposed
-part defines the \textquotedbl{}routed\textquotedbl{} information
-which is appended on top of the WNC stream to exploit any potential
-spare capacity of related channels in the system (see \cite{Uricar-Qian-Sykora-Mow_2013-WCNC,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}
-for more details). A simplified description of SC-based relaying in
-an uncoded WBN system is summarized in Table~\ref{tab:CTUpp_SC-relaying-scheme}
-and depicted in Fig.~\ref{fig:CTUpp_Information-flow-uncoded-block-scheme}.
 \begin{figure*}
@@
 \end{figure*}
-\begin{table}
-\centering{}%
-\begin{tabular}{|>{\raggedright}p{0.95\columnwidth}|}
-\hline 
-\textbf{Step 1: Source transmission}
-\begin{itemize}
-\item Source $S_{i},\,i\in\left\{ A,B\right\} $ maps its data symbol $\mathbf{d}_{i}=\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]$
-into a $\left(N_{b}+N_{s}\right)$-bit superposition modulation symbol
-\begin{equation}
-s_{i}=\mathcal{A}^{i}\left(\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]\right),\label{eq:CTUpp_OverallSourceStreams}
-\end{equation}
 
-\item $S_{A},\,S_{B}$ simultaneously transmit their signals to the relay
-and unintended destinations (Fig.~\ref{fig:CTUpp_Information_flows}).
-\item Relay receives
-\begin{equation}
-x=h_{AR}\mathcal{A}^{A}\left(\left[\mathbf{d}_{A}^{b};\mathbf{d}_{A}^{s}\right]\right)+h_{BR}\mathcal{A}^{B}\left(\left[\mathbf{d}_{B}^{b};\mathbf{d}_{B}^{s}\right]\right)+w_{R}
-\end{equation}
-
-and decodes $\left[\mathbf{d}_{A}^{s};\mathbf{d}_{B}^{s};f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})\right]$,
-where $f$ is a hierarchical WNC function \cite{Sykora-Burr_2011-TVT}.
-
-\item $D_{j}$ receives
-\begin{equation}
-z_{j}=h_{ij}\mathcal{A}^{i}\left(\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]\right)+w_{j},\label{eq:CTUpp_Dj_received}
-\end{equation}
-where $i,\,j\in\left\{ A,B\right\} ,\,i\neq j$ and stores the signal
-for further processing.\end{itemize}
-\tabularnewline
-\hline 
-\textbf{Step 2: Relay broadcast}
-\begin{itemize}
-\item Relay sends $N_{R}=2N_{s}+N_{b}$-bit modulation symbol to both destinations:
-\begin{equation}
-s_{R}=\mathcal{A}^{R}\left(\left[\mathbf{d}_{A}^{s};\mathbf{d}_{B}^{s};f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})\right]\right).\label{eq:CTUpp_relay_output}
-\end{equation}
-
-\item $D_{j}$ ($i,\,j\in\left\{ A,B\right\} ,\,i\neq j$) decodes:
-
-\begin{itemize}
-\item $\left[\mathbf{d}_{A}^{s};\mathbf{d}_{B}^{s};f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})\right]$
-(from the relay signal (\ref{eq:CTUpp_relay_output}))
-\item $\mathbf{d}_{i}^{b}$ (from the stored signal $z_{j}$ (\ref{eq:CTUpp_Dj_received}),
-after interference cancellation (IC) of known $\mathbf{d}_{i}^{s}$)
-\item $\mathbf{d}_{j}^{b}$ (from $\mathbf{d}_{i}^{b}$ and $f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})$,
-using a standard WNC decoding \cite{Sykora-Burr_2011-TVT})
-\end{itemize}
-\item $D_{j}$ merges $\mathbf{d}_{j}^{b}$ with $\mathbf{d}_{j}^{s}$ to
-obtain the desired $\left[\mathbf{d}_{j}^{b};\mathbf{d}_{j}^{s}\right]$.\end{itemize}
-\tabularnewline
-\hline 
-\end{tabular}\vskip1ex\caption{SC-based relaying scheme in uncoded WBN}.\label{tab:CTUpp_SC-relaying-scheme}
-\end{table}
-
-\subsection{System Model}
-
-For the sake of simplicity of the constellation design analysis, we
-provisionally assume that the system is uncoded\footnote{ Modification of the system model for the coded case will be provided
-in Section~\ref{sec:CTUpp_Channel-Coding}, together with a discussion
-on the design of individual channel encoders for particular information
-streams in the system.}. The signal space representations of the transmitted channel symbols
-are $s_{A}=\mathcal{A}^{A}\left(\mathbf{d}_{A}\right)$, $s_{B}=\mathcal{A}^{B}\left(\mathbf{d}_{B}\right)$,
-where $\mathcal{A}^{i}\left(\centerdot\right)$ is the memoryless
-constellation mapper and $\mathbf{d}_{i}$ is the source $i\in\left\{ A,B\right\} $
-data symbol. Each communication round can be divided into two phases
-(Fig. \ref{fig:CTUpp_Information_flows}). In the first phase (Multiple
-Access \textendash{} MA phase) both sources $S_{A},\,S_{B}$ simultaneously
-transmit their signal to the relay, which receives a noisy superimposed
-constellation:
-\begin{equation}
-x=h_{AR}s_{A}+h_{BR}s_{B}+w_{R}.\label{eq:CTUpp_relay-received}
-\end{equation}
-Additionally, the source $S_{i}$ ($i\in\{A,B\}$) transmission is
-overheard (at no cost) by its \textquotedbl{}unintended\textquotedbl{}
-destination $D_{j}$ ($j\in\{A,B\},\,j\neq i$) as:
-\begin{align}
-z_{j} & =h_{ij}s_{i}+w_{j}\label{eq:CTUpp_HSI_observation}
-\end{align}
-Even though the overheard information (\ref{eq:CTUpp_HSI_observation})
-does not carry the desired data for the respective destination, it
-can be efficiently exploited to enable WNC-based processing in WBNs
-\cite{Uricar-Qian-Sykora-Mow_2013-WCNC}. We denote the specific overheard
-information as the \emph{Hierarchical Side Information} (HSI) \cite{Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}.
-
-The relay performs WNC-based decoding \cite{Sykora-Burr_2011-TVT}
-of the received signal and broadcasts the decoded WNC (hierarchical)
-information as $s_{R}$ to $D_{A},\,D_{B}$ in the second phase (Broadcast
-\textendash{} BC phase). Both destinations are able to decode the
-desired data using the relay's (hierarchical) signal (\ref{eq:CTUpp_relay-received})
-and the overheard HSI (\ref{eq:CTUpp_HSI_observation}) if a proper
-WNC processing is employed in the system.
-
-Scalar complex channel coefficients $h_{ij}$, $i,j\in\{A,B,R\}$,
-$i\neq j$ are assumed to be constant during the communication round
-and known at the respective receiving node. Zero mean i.i.d. complex
-Gaussian noise sample $w_{i}$, $i\in\{A,B,R\}$ has variance $\sigma_{i}^{2}$.
-Signal to Noise Ratios (SNRs) in the system are given by ($\gamma_{{\rm {MAC}}}$,
-$\gamma_{{\rm {HSI}}}$, $\gamma_{{\rm {BC}}}$), where $\gamma_{{\rm {MAC}}}$
-is the SNR on the source$\rightarrow$relay multiple-access channel
-\textendash{} MAC ($\left(S_{A},\,S_{B}\right)\rightarrow R$), $\gamma_{{\rm {HSI}}}$
-is the SNR on the unintended source$\rightarrow$destination (HSI)
-channels ($S_{A}\rightarrow D_{B}$, $S_{B}\rightarrow D_{A}$) and
-$\gamma_{{\rm {BC}}}$ is the SNR on the relay$\rightarrow$sources
-broadcast channel ($R\rightarrow\left(D_{A},\,D_{B}\right)$).
-
-\section{Superposition Modulation Design\label{sec:CTUpp_Euclidean-Distance-based-Constel}}
-
-In this section we summarize the design of constellation mappers $\mathcal{A}^{A},\,\mathcal{A}^{B}$
-as presented in \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}. The
-output constellation is created as
-\begin{equation}
-s=\mathcal{A}\left(\left[\mathbf{d}^{b};\mathbf{d}^{s}\right]\right)=\sum_{n_{s}=0}^{N_{s}-1}L_{n_{s}}^{s}(2d_{n_{s}}^{s}-1)+\sum_{n_{b}=0}^{N_{b}-1}L_{n_{b}}^{b}(2d_{n_{b}}^{b}-1),\label{eq:CTUpp_superpositionModulation}
-\end{equation}
-where $L_{n}^{b},\,L_{n}^{s}$ are \emph{Superposition Modulation}
-\cite{Hoeher-Wo_2011-IEEE-M-COM} \emph{scaling coefficients.}
-
-The coefficients $L_{n}^{b},\,L_{n}^{s}$ (\ref{eq:CTUpp_superpositionModulation})
-are generally taken from the set of complex numbers. However, for
-the sake of simplicity we limit the scaling coefficients $L_{n}^{b},\,L_{n}^{s}$
-to a purely imaginary or real numbers. Even though that this simplified
-approach can potentially result in a sub-optimal performance in fading
-channels (complex channel coefficients $h_{iR}$, $i\in\{A,B\}$ can
-rotate the component superposition constellations), we follow this
-simplification to show the basic ideas of the proposed superposition
-modulation design. The extension to general complex $L_{n}^{b},\,L_{n}^{s}$
-can naturally embrace the source phase pre-rotation \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008},
-which virtually reverts the fading channel to the conventional Additive
-White Gaussian Noise (AWGN) channel with $\varangle h_{ij}=0$.
-
-As shown in Table~\ref{tab:CTUpp_SC-relaying-scheme}, the basic
-and superposed parts of the source information are processed in a
-different way through the system and so we will discuss the constellation
-design for these two specific information streams separately. We briefly
-introduce the incentives and main ideas of the design for the superposed
-and basic parts, and then we summarize the complete multi-source constellation
-design in a systematic algorithm.
-
-\subsection{Constellation Design: Basic part\label{sub:CTUpp_basic-part}}
-
-A specific WNC function $f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})$
-has to be decoded by the relay (Table~\ref{tab:CTUpp_SC-relaying-scheme})
-and hence some overlapping of symbols in the superimposed constellation
-(observed by the relay node) can be allowed, resulting in improved
-Euclidean distance properties. More precisely, two (or more) pairs
-of basic information symbols $\left(\mathbf{d}_{A}^{b},\,\mathbf{d}_{B}^{b}\right)$,
-$\left(\mathbf{d'}_{A}^{b},\,\mathbf{d'}_{B}^{b}\right)$ can be allowed
-to fall into the same point in the superimposed constellation:
-\begin{equation}
-s_{A}\left(\mathbf{d}_{A}^{b}\right)+s_{B}\left(\mathbf{d}_{B}^{b}\right)=s'_{A}\left(\mathbf{d'}_{A}^{b}\right)+s'_{B}\left(\mathbf{d'}_{B}^{b}\right),\label{eq:CTUpp_exclusive-law}
-\end{equation}
-if and only if they belong to the same WNC function output, i.e. iff
-$f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})=f(\mathbf{d'}_{A}^{b},\mathbf{d'}_{B}^{b})$,
-where $f(\centerdot,\centerdot)$ is the hierarchical WNC function\cite{Sykora-Burr_2011-TVT}.
-In this case the overlapping symbols produce the \emph{same hierarchical
-output}, which can be successfully resolved by the destination, if
-matching HSI information is available (Table~\ref{tab:CTUpp_SC-relaying-scheme}).
-The particular choice of the scaling coefficients $L_{A,n}^{b},\,L_{B,n}^{b}$
-generally depends on the particular choice of the hierarchical WNC
-function\footnote{Modulo-sum \cite{Hekrdla-Sykora_2013,Prochazka-Uricar-Halls-Sykora_2015-ICC,Prochazka-2016}
-and bit-wise exclusive-or (XOR) \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew-Lu_2012}
-hierarchical functions are commonly discussed in the WNC literature,
-however, unlike the bit-wise XOR, implementation of channel coding
-for the Modulo-sum mapping is a standalone research problem and hence
-it is out of the scope of this paper.}. In the rest of this paper we discuss the constellation design for
-the \emph{bit-wise exclusive-or} WNC function ($f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})=\mathbf{d}_{A}^{b}\oplus\mathbf{d}_{B}^{b}$,
-where $\oplus$ is the bit-wise XOR operation) \cite{Zhang-Liew-Lu_2012}.
-
-Suitable overlapping of constellation symbols at the relay is provided
-by letting both sources transmit at the same power level, i.e. $L_{A,n}^{b}=L_{B,n}^{b}$
-\cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}. It can be easily shown
-that if these superposition modulation (\ref{eq:CTUpp_superpositionModulation})
-coefficients are chosen as $L_{A,n}^{b}=L_{B,n}^{b}=3^{\left\lfloor n/2\right\rfloor }$
-(for even $n$) and $L_{A,n}^{b}=L_{B,n}^{b}=\jj3^{\left\lfloor n/2\right\rfloor }$
-(for odd $n$), the received superimposed constellation at the relay
-will have overlaps only among those constellation symbols (\ref{eq:CTUpp_exclusive-law})
-which have the same hierarchical WNC output i.e.
-$f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})=f(\mathbf{d'}_{A}^{b},\mathbf{d'}_{B}^{b})=\mathbf{d}_{A}^{b}\oplus\mathbf{d}_{B}^{b}=\mathbf{d'}_{A}^{b}\oplus\mathbf{d'}_{B}^{b}$.
-
-\subsection{Constellation Design: Superposed part\label{sub:CTUpp_superposed-part}}
-
-The superposed information given by $\mathbf{d}_{A}^{s},\,\mathbf{d}_{B}^{s}$
-has to be decoded separately by the relay (Table~\ref{tab:CTUpp_SC-relaying-scheme}),
-and hence a source constellation avoiding all potential overlaps in
-the superimposed constellation (observed by the relay node) is desirable.
-In an AWGN channel ($h_{AR}=h_{BR}=1$ in Fig.~\ref{fig:CTUpp_Information_flows})
-this can be simply achieved by mapping the information bits to the
-real-valued Amplitude Shift Keying (ASK) constellation at $S_{A}$
-and purely imaginary-valued ASK constellation at $S_{B}$ (or vice
-versa). Hence, in AWGN, the resulting superimposed constellation at
-the relay will form a regular QAM constellation without any overlapping
-of constellation symbols. For the assumed superposition modulation
-(\ref{eq:CTUpp_superpositionModulation}), this can be easily achieved
-by setting the coefficients as $L_{A,n}^{s}=2^{n}$ and $L_{B,n}^{s}=\jj\cdot2^{n}$.
-\begin{algorithm}[H]
-\input{alg4_final_TWC.tex}\caption{Constellation design for fixed $N_{b},\,N_{s}$.\label{alg:CTUpp_ButterflyConstellationDesign} }
-\end{algorithm}
-
-\subsection{Systematic Constellation Design Algorithm\label{sub:CTUpp_const_design}}
-
-To accommodate both the basic and superposed information streams into
-a joint source constellation, the scaling coefficients of basic information
-streams ($L_{n}^{b}$) must be pre-scaled by a factor $2^{N_{s}}$
-to ensure that they lie above the largest scaling coefficient of the
-superposed part. The basic stream (WNC) is thus preferred over the
-superposed one (routing) in order to maximize the overall throughput
-of the system. The systematic constellation design for arbitrary $N_{b},\,N_{s}$
-is summarized in Algorithm~\ref{alg:CTUpp_ButterflyConstellationDesign}.
-
-The basic principle of source constellation design is illustrated
-in Fig.~\ref{fig:CTUpp_ConstellationDesignExample} ($N_{b}=2,\,N_{s}=1$)
-and some example sets of source constellations with constant $N_{b}+N_{s}=2$
-are depicted in Fig.~\ref{fig:CTUpp_ConstellationDesign_NbNs2}.
-
-\section{Performance Analysis I: Uncoded System\label{sec:CTUpp_Performance-Analysis-Uncoded}}
-
-For the sake of simplicity of the theoretical performance analysis,
-we assume that source$\rightarrow$relay channels in WBN are AWGN\footnote{Note that this also includes the system with perfect source phase
-prerotation \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008},
-which can be obtained by a generalization of the scaling coefficients
-as $L'_{n}=L_{n}e^{-\jj\measuredangle h_{SR}}$, where $h_{SR}$ is
-the corresponding source$\rightarrow$relay channel.} (i.e. $h_{iR}=1$ for $i\in\{A,B\}$). We evaluate the throughput
-analytically as $(N_{b}+N_{s})\cdot(1-P_{e}^{\mathrm{FER}})$, where
-$P_{e}^{\mathrm{FER}}$ denotes the frame error rate. Due to the system
-symmetry we evaluate the throughput of $S_{A}\to D_{A}$ only. We
-set the frame length to $M=768$ symbols (to match the HW evaluation)
-and the relay output mapper $\mathcal{A}^{R}$ will be defined as
-a conventional ($2^{N_{b}+2N_{s}}$$)$-QAM constellation. All performance
-metrics in the symmetric WBN are evaluated as a function of the actual
-SNRs ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}},\,\gamma_{{\rm {BC}}}$).
 \begin{figure*}
@@
 \end{figure*}
+
 \begin{figure*}
@@
 
-\subsection{Analytical Performance Evaluation\label{sub:CTUpp_Numerical_Evaluation_uncoded}}
-
-Since all constellations points lie on a regular QAM grid, it is straightforward
-to evaluate the exact Symbol Error Rate (SER) for all channels analytically.
-The symbol error probability $P_{e}^{\mathrm{SER}}$ can be approximated
-by its upper-bound\footnote{The evaluated $P_{e,\mathrm{UB}}^{SER}$ is an upper-bound of $P_{e}^{\mathrm{SER}}$,
-since an error in MA/BC phase does not necessarily induce an error
-in the overall communication chain of the uncoded system. This is
-especially true if the error occurs in the superposed bits $\mathbf{d}_{B}^{s}$
-used for interference cancellation processing at $D_{A}$.} $P_{e,\mathrm{UB}}^{\mathrm{SER}}=1-((1-P_{e}^{{\rm MAC}})(1-P_{e}^{{\rm HSI}})(1-P_{e}^{\mathrm{BC}}))$,
-where $P_{e}^{{\rm MAC}}$, $P_{e}^{{\rm HSI}}$ and $P_{e}^{{\rm BC}}$
-are the probabilities of symbol error in the MAC, HSI and BC channels
-(respectively). Since the system is memoryless, the overall FER is
-given by $P_{e}^{\mathrm{FER}}=1-(1-P_{e}^{\mathrm{SER}})^{M}$, which
-can be approximated by $P_{e,\mathrm{UB}}^{\mathrm{FER}}=1-(1-P_{e,\mathrm{UB}}^{\mathrm{SER}})^{M}$.
-Nearest neighbor pairwise error approximation can be used for efficient
-error rate evaluation. The lower-bound of the throughput can be then
-evaluated analytically as:
-\begin{equation}
-T_{\mathrm{LB}}=(N_{b}+N_{s})\cdot(1-P_{e,\mathrm{UB}}^{\mathrm{FER}}).\label{eq:CTUpp_T-LB}
-\end{equation}
-
-\subsection{Hardware Implementation\label{sub:CTUpp_Hardware_Verification}}
-
-In addition to the analytical evaluation of throughput, we validate
-the results in a real-world setup. The hardware performance is evaluated
-using Ettus Research Universal Software Radio Peripherals (USRPs)
-which are computer-hosted Software Defined Radios (SDRs). The USRPs
-connect to a host computer via a Gigabit Ethernet link, which the
-host-based software uses to receive and transmit the baseband IQ stream.
-The host controls the USRP using USRP Hardware Driver (UHD) commands,
-including setting parameters such as amplifier gain. The USRP then
-performs the necessary baseband processing then up/down-conversion
-and transmission/reception. The Ettus Research N210 USRP is used,
-which consists of a motherboard and a Radio Frequency (RF) daughterboard;
-more details can be found in \cite{Ettus_flyer}. In these experiments
-the XCVR2450 daughterboards are used, these are dual-band transceivers
-with 100 mW output at 2.4 - 2.5 GHz and 50 mW output at 4.9 - 5.85
-GHz. In this paper GNURadio \cite{GNURadio}, which is an open-source
-tool-kit, is used as the host-processing software.
 \begin{figure}
@@
 
-\subsubsection{OFDM Parameters}
-
-An OFDM solution is employed with $N_{FFT}=64$ subcarriers. There
-are 48 data subcarriers, with a DC carrier, 11 guard carriers and
-4 pilot carriers at -21, -7, 7 and 21. A CP of $\frac{1}{4}$, i.e.
-16 samples, is employed and a center frequency of $f_c=2.4$GHz is
-used. The USRP N210 is limited (by the Gigabit Ethernet link) to support
-an RF bandwidth up to 25 MHz with 14-bit resolution, though a 1 MHz
-bandwidth, i.e. 1 MS/s sampling rate, is used here. Each packet contains
-16 OFDM symbols of payload with 48 data carriers per symbol and constellation
-parameters $N_{b}$,~$N_{s}$ are set to the desired values. The
-payload is random data and no channel coding is currently implemented
-in the system.
-
-\subsubsection{Node Placement, Synchronization and Channel Estimation\label{sub:CTUpp_frame-1-2}}
-
-A 5-node, 2x1x2 topology with two sources, one relay and two destinations,
-is used as shown in Fig. \ref{fig:CTUpp_HW_setup}. The USRPs each
-have a single 3dBi omni-directional antenna (at 2.4 - 2.5 GHz and
-4.9 - 5.85 GHz). The first source transmitter ($S_A$) USRP is connected
-to a powerful Core i7 laptop, running a single instance of GNURadio,
-by a Gigabit Ethernet link. The second source transmitter ($S_B$)
-USRP is connected to the first by the MIMO expansion cable. This provides
-the second transmitter with baseband data from GNURadio as well as
-synchronization signals from the first transmitter. The relay, $D_{A}$
-and $D_{B}$ USRPs are connected to further laptops running GNURadio
-by Gigabit Ethernet links. More details about synchronization, carrier
-frequency offset and timing offset estimation can be found in \cite{Hynek-etal_2014-EW}.
-In this paper, the MIMO cable is used to synchronize the frequency
-of the two source USRPs, as well as to achieve sample-level timing
-synchronization. The latter avoids asynchronism in the superimposed
-constellations at the relays; more details about the impact of asynchronism
-in WNC can be found in \cite{Diwine_D512}. Furthermore an Ettus Octoclock
-clock distribution system \cite{Ettus_OctoClock} is used to provide
-external frequency synchronization signals to all nodes. This allows
-us to show system performance, and compare with the theoretical and
-simulation cases, without the impact of asynchronism affecting the
-results. Results with additional real-world impairments are a focus
-for future work, as discussed in the final section of this paper.
-Channel tracking using pilots is implemented as detailed in \cite{Hynek-etal_2014-EW},
-however, due to the static indoor environment (used to mimic the AWGN
-channel used in the theoretical work as closely as possible) the channel
-does not change significantly over the frame duration. The USRPs are
-closely located in line-of-sight to ensure the channel between them
-is fairly static, without fading, thus mimicking the channel used
-in the theoretical work. Moreover as cabled synchronisation is used,
-it is desirable to minimize the cable length. Low SNRs are achieved
-between the USRPs using low transmit powers.
-
-\subsection{Uncoded System Throughput}
-
-To analyze the performance of the proposed constellations, we evaluate
-the throughput for fixed $\gamma_{{\rm {MAC}}}$ and $\gamma_{{\rm {BC}}}$
-as a function of $\gamma_{{\rm {HSI}}}$. We analyze all permissible
-constellations for a fixed $N_{b}+N_{s}=2$ (see Fig.~\ref{fig:CTUpp_ConstellationDesign_NbNs2})
-and compare their performance with the throughput $T_{\mathrm{ref}}$
-of the \emph{reference} ``conventional\textquotedbl{} multi-user
-detection with regular QAM constellation. Note again that the hierarchical
-function is set to the bit-wise XOR, i.e. $f\left(\mathbf{d}_{A}^{b},\,\mathbf{d}_{B}^{b}\right)=\mathbf{d}_{A}^{b}\oplus\mathbf{d}_{B}^{b}$
-in the evaluations.
-
-In addition to the analytically evaluated throughput (lower-bound)
-$T_{\mathrm{LB}}$ (\ref{eq:CTUpp_T-LB}) we also include the result
-of a numerical Monte-Carlo evaluation of throughput ($T_{\mathrm{sim}}$)
-over $10^{4}$ frames (Figs.~\ref{fig:CTUpp_Throughput16_20},~\ref{fig:CTUpp_Throughput17_17},~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16})
-and throughput $T_{\mathrm{USRP}}$ evaluated by the HW
-real world setup (Figs.~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16}).
-The particular related assumptions employed in the evaluations are
-summarized in Table~\ref{tab:UncodedSystemSummary} to improve the
-reader's perception. One can see that the reference scenario with
-conventional QPSK (4-QAM) provides zero throughput ($T_{\mathrm{ref}}$)
-in the whole range of analyzed SNRs in all plots\footnote{In AWGN channel, the resulting superimposed constellation has too
-many overlaps for the reference source QPSK constellations, preventing
-a successful multi-user decoding of both of the separate user data
-streams in the uncoded system.}. The performance of conventional WNC (in the specific 4-ary case
-the conventional WNC constellations are identical to $(N_{b},N_{s})=(2,0)$
-\cite{Koike-Popovski-Tarokh_2008}) is, on the other hand, inevitably
-limited to high $\gamma_{{\rm {HSI}}}$ regions in WBN as it requires
-perfect HSI to enable the decoding of WNC functions at the destination
-nodes \cite{Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}. Remarkably, the
-novel proposed constellations provide a \emph{non-zero throughput}
-even in the \emph{low-to-medium SNR} region of HSI channels. The resulting
-SNR and throughput gains are highlighted in Figs.~\ref{fig:CTUpp_Throughput16_20},~\ref{fig:CTUpp_Throughput17_17},~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16}.
-Note also extremely close agreement of HW performance evaluation $T_{\mathrm{USRP}}$
-in all cases (Figs.~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16}).
-Even in this simple case ($N_{b}+N_{s}$ fixed to $2$) there are
-several interesting phenomena which can be observed in the throughput
-performance:
-\begin{table*}
-\begin{centering}
-{\small{}}%
-\begin{tabular}{|l|c|c|c|}
-\cline{2-4} 
-\multicolumn{1}{l|}{} & {\small{}$T_{\mathrm{LB}}$ } & {\small{}$T_{\mathrm{sim}}$} & {\small{}$T_{\mathrm{USRP}}$ }\tabularnewline
-\hline 
-{\small{}Communication channel} & {\small{}AWGN} & {\small{}AWGN} & {\small{}Wireless channel}\tabularnewline
-\hline 
-{\small{}Time synchronization} & {\small{}Perfect} & {\small{}Perfect} & {\small{}External (Octoclock)}\tabularnewline
-\hline 
-{\small{}Phase pre-rotation} & {\small{}Perfect} & {\small{}Perfect} & {\small{}Feedback channel (UDP)}\tabularnewline
-\hline 
-{\small{}Direct link} & {\small{}Not considered} & {\small{}Not considered} & {\small{}Bridged by cable}\tabularnewline
-\hline 
-{\small{}Channel symmetry} & {\small{}Perfect} & {\small{}Perfect} & {\small{}Node placement}\tabularnewline
-\hline 
-{\small{}Throughput evaluation} & {\small{}Lower bound} & {\small{}Numerical} & {\small{}Numerical}\tabularnewline
-\hline 
-\end{tabular}{\small{}\vspace{1ex}
-}
-\par\end{centering}{\small \par}
-
-\caption{Summary of assumptions in the uncoded system analysis.\label{tab:UncodedSystemSummary}}
-{\small{}\vspace*{-3ex}
-}{\small \par}
-\end{table*}
-
-\begin{itemize}
-\item The constellations with ($N_{b}=0,\,N_{s}>0$) assume full multi-user
-detection at the relay and hence they do not exploit the HSI channels
-(Table~\ref{tab:CTUpp_SC-relaying-scheme}). Consequently, their
-throughput does not depend on $\gamma_{{\rm {HSI}}}$. However, their
-performance worsens with decreasing $\gamma_{{\rm {MAC}}}$ (compare
-Figs.~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput16_20})
-and deteriorates quite dramatically with decreasing $\gamma_{{\rm {BC}}}$
-(compare Figs.~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16}).
-\item The constellations with ($N_{b}>0,\,N_{s}=0$) require a reliable
-HSI channel and hence their throughput is zero for low $\gamma_{{\rm {HSI}}}$
-and grows up to $N_{b}$ for high $\gamma_{{\rm {HSI}}}$ and sufficiently
-high $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$ (all Figs.~\ref{fig:CTUpp_Throughput16_20},~\ref{fig:CTUpp_Throughput17_17},~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16}).
-\item The performance of all constellations with ($N_{b}>0,\,N_{s}>0$)
-is influenced by all system SNRs ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$).
-Remarkably, for some particular values of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$
-these constellations significantly outperform those with $N_{b}=0$
-or $N_{s}=0$ in the medium $\gamma_{{\rm {HSI}}}$ region (Figs.~\ref{fig:CTUpp_Throughput17_17},~\ref{fig:CTUpp_Throughput20_16}).
-Note that this is a direct consequence of superior $\rho_{\mathrm{HSI}}^{2}$
-performance of these constellations\footnote{It can be shown that for constant $N_{b}+N_{s}$ the minimum Euclidean
-distance $\rho_{\mathrm{HSI}}^{2}$ grows with decreasing $N_{b}$,
-resulting in a more efficient utilization of \textquotedbl{}imperfect\textquotedbl{}
-HSI channels \cite{Uricar-Sykora_2012,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}
-and consequently in a more reliable overheard HSI for the constellations
-with lower (non-zero) $N_{b}$.} for constant $N_{b}+N_{s}$, i.e. for constant bits/constellation
-symbol transmitted by the sources.
 \begin{figure}
 \begin{centering}
-\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC16_BC20_N2}\vskip-2ex
+\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC16_BC20_N2}
 \par\end{centering}
@@
 \end{figure}
+
 \begin{figure}
 \begin{centering}
-\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC17_BC17_N2}\vskip-2ex
+\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC17_BC17_N2}
 \par\end{centering}
@@
 \end{figure}
+
 \begin{figure}
 \begin{centering}
-\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC20_N2}\vskip-2ex
+\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC20_N2}
 \par\end{centering}
@@
 \end{figure}
+
 \begin{figure}
 \begin{centering}
-\hspace*{-0.04\columnwidth}\includegraphics[clip,width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC16_N2}\vskip-2ex
+\hspace*{-0.04\columnwidth}\includegraphics[clip,width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC16_N2}
 \par\end{centering}
@@
 
-\end{itemize}
-
-\section{Adaptive Constellation Design\label{sec:CTUpp_Adaptive-Constellation-Design}}
-
-As discussed in the previous section, the throughput of the system
-depends heavily on the actual SNR conditions (given by $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$).
-By itself, this observation calls naturally for an\emph{ adaptive
-constellation design}. To generate a multi-source constellation able
-to \emph{maximize the throughput} given the current SNR conditions
-in the WBN system, the source nodes $S_{A},\,S_{B}$ must be acquainted
-with the particular mapping operation $(\hat{\gamma}_{{\rm {MAC}}},\,\hat{\gamma}_{{\rm {BC}}},\,\hat{\gamma}_{{\rm {HSI}}})\mapsto(N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}),$
-providing the constellation parameters $N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}$
-(input arguments to the Algorithm~\ref{alg:CTUpp_ButterflyConstellationDesign})
-for the given (available) SNR estimates\footnote{The estimated SNR parameters ($\hat{\gamma}_{{\rm {MAC}}},\,\hat{\gamma}_{{\rm {BC}}},\,\hat{\gamma}_{{\rm {HSI}}}$)
-must be delivered to both sources by a feedback channel from the relay
-and/or destinations. The particular implementation of this feedback
-transmission is beyond the scope of this paper and hence (for the
-sake of simplicity) we assume that these parameters are made available
-at both sources by a genie. Note that in the HW evaluation, the required
-feedback is provided via UDP connection.} ($\hat{\gamma}_{{\rm {MAC}}},\,\hat{\gamma}_{{\rm {BC}}},\,\hat{\gamma}_{{\rm {HSI}}}$).
-The desired \emph{SNR mapping regions} (a three-dimensional look-up
-table in WBN) can be generated numerically in advance and stored at
-both source nodes to enable the adaptive constellation mapping.
-
-Due to the numerical complexity of Monte-Carlo evaluation of throughput
-$T_{\text{sim}}$ we use the analytically evaluated lower bound $T_{\text{LB}}$
-(\ref{eq:CTUpp_T-LB}) to generate the SNR mapping regions for a wide
-range of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$.
-The optimal constellation parameters (maximizing the throughput $T_{\mathrm{LB}}$
-for a given SNR triplet $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$)
-are found by performing an exhaustive search over the constellation
-parameters as $(N_{b}^{{\rm I}},\,N_{s}^{{\rm I}})=\arg\max_{(N_{b},N_{s})}T_{\mathrm{LB}}(\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}})$.
-
-The SNR mapping regions, including the resulting throughput for the
-optimal choice of $N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}$, are shown
-as a function of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$ for
-$\gamma_{{\rm {BC}}}\in\{15\,\mathrm{dB},\,17\,\mathrm{dB},20\,\mathrm{dB},25\,\mathrm{dB}\}$
-in Fig.~\ref{fig:CTUpp_SNR_map_BC15-17-20-25}. Several interesting
-phenomenas can be again observed in the figure:
-\begin{itemize}
-\item Since the transmission schemes with ($N_{b}=0,\,N_{s}>0$) constellations
-can ignore the HSI channels (Table~\ref{tab:CTUpp_SC-relaying-scheme}),
-these constellations are optimal in the low $\gamma_{{\rm {HSI}}}$
-region ($\gamma_{{\rm {HSI}}}<8\,\mathrm{dB}$), regardless of the
-other channels' SNRs $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$.
-\item The constellations with ($N_{b}>0,\,N_{s}=0$) provide the best performance
-in a substantial part of the medium-to-high $\gamma_{{\rm {HSI}}}$
-regions, depending on the actual $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$.
-\item The \textquotedbl{}combined\textquotedbl{} constellations ($N_{b}>0,\,N_{s}>0$)
-provide the maximal throughput (for sufficiently high $\gamma_{{\rm {BC}}}$)
-in relatively large regions of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$
-(see the dominant throughput regions of $(N_{b}^{{\rm I}},\,N_{s}^{{\rm I}})=(2,1)$
-for $\gamma_{{\rm {BC}}}=\left\{ 20\,\mathrm{dB},\,25\,\mathrm{dB}\right\} $).
-Note that these constellations have a great potential for application
-in systems with limited or partial HSI (see \cite{Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}).
 \begin{figure*}
@@
 
-\item The BC channel SNR ($\gamma_{{\rm {BC}}}$) can significantly limit
-the performance of the system, even in the case where both $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$
-are relatively high (compare the results for $\gamma_{{\rm {BC}}}=15\,\mathrm{dB}$
-and $\gamma_{{\rm {BC}}}=20\,\mathrm{dB}$ for $\gamma_{{\rm {MAC}}}=\gamma_{{\rm {HSI}}}\apprge15\,\mathrm{dB}$).
-This behavior originates in the fact that $\rho_{\mathrm{BC}}^{2}$
-decreases with growing $N_{b}+2N_{s}$ and hence low $\gamma_{{\rm {BC}}}$
-essentially limits the maximum efficiently applicable cardinality
-of the relay output ($2^{N_{b}+2N_{s}}$-QAM) constellation. Equivalently,
-the optimal source constellation parameters ($N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}$)
-can become limited by the bottleneck induced by weak relay$\rightarrow$destination
-(BC) channels. 
-\item The constellations with odd $N_{b}$ are rarely dominant over the
-other strategies with identical $N_{b}+N_{s}$. This is a direct consequence
-of their relatively poor $\rho_{\mathrm{MAC}}^{2}$ Euclidean distance
-properties.
-\end{itemize}
-To support a viability of the adaptive constellation mapping scheme,
-we again evaluate the system performance in the HW real world setup.
-Since the HW evaluation is heavily time-consuming, we analyze the
-throughput $T_{\mathrm{USRP}}$ only for $\gamma_{{\rm {BC}}}=20\,\mathrm{dB}$
-and $0\,\mathrm{dB}\leq\gamma_{{\rm {MAC}}},\gamma_{{\rm {HSI}}}\leq30\,\mathrm{dB}$
-with a step-size $3\,\mathrm{dB}$. The measured $T_{\mathrm{USRP}}$
-performance is available in Fig.~\ref{fig:CTUpp_SNR_map_BC20_USRP}.
-Close agreement between the $T_{\mathrm{USRP}}$ and $T_{\text{LB}}$
-can be observed again in the whole range of analyzed $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$
-(see Fig.~\ref{fig:CTUpp_SNR_map_BC20_USRP}).
-
-\section{Channel Coding\label{sec:CTUpp_Channel-Coding}}
-
-We have shown that Algorithm~\ref{alg:CTUpp_ButterflyConstellationDesign}
-is a strong tool for the design of source constellations suitable
-for arbitrary channel SNRs in the WBN system. However, even though
-the proposed constellations provide promising performance in the uncoded
-scenario, the extension to a coded system is desirable for practical
-wireless applications.
-
-Considering the communication in uncoded WBNs (Fig.~\ref{fig:CTUpp_Information-flow-uncoded-block-scheme}),
-there are many ways to improve its reliability through channel coding.
-In this paper we propose one particular solution, based on the assumption
-that each source node splits its data into the basic and superposed
-part and then encodes these parts separately by two constituent channel
-encoders\footnote{In a more general approach, each source data word is split into $N_{b}+N_{s}$
-parallel data sub-words that are encoded separately using the principles
-of multilevel coding (see e.g. \cite{Wachsmann-Fischer-Huber-1999-IEEE-T-IT}).
-However, the development of a general multilevel coding scheme for
-WBN is beyond the scope of this paper.}. We believe that this approach provides the best insight into the
-channel-coding extension of WBN systems and hence we focus on its
-development in the rest of this section.
-
-\subsection{Per-link Channel Coding Scheme for Symmetric WBN
-with Superposition Modulations}
-
-In general, it is desirable to protect\emph{ all individual transmissions}
-in the system with error correction coding\footnote{Alternatively, a primitive end-to-end coding scheme can be designed,
-performing the channel coding solely at sources $S_{A},\,S_{B}$ and
-channel decoding (potentially computationally intensive) solely at
-destinations $D_{A},\,D_{B}$, while leaving the relay $R$ to operate
-on a symbol-by-symbol basis (as in the uncoded system). Unfortunately,
-this approach is only sub-optimal, as in this case the particular
-transmissions on source$\rightarrow$relay and relay$\rightarrow$destination
-channels are not individually protected by channel coding.}. Accordingly, the relay node has to decode the desired data (including
-the particular WNC function) from its observation and then it should
-perform an additional re-encoding in order to protect the subsequent
-relay$\rightarrow$destinations transmission. The resulting channel
-coding scheme (see Fig.~\ref{fig:CTUpp_Information-flow-coded-block-scheme})
-is introduced in the following text.
-
-\subsubsection{Source processing}
-
-Source $S_{A}$ (likewise for $S_{B}$) wants to transmit a binary
-data word $\mathbf{D}_{A}$ of length $\left|\mathbf{D}_{A}\right|=\left|\mathbf{D}_{B}\right|=k_{\mathbf{D}}$
-to its respective destination $D_{A}$. Each data word $\mathbf{D}_{A}$
-is split into the basic and superposed part (similarly as in the uncoded
-case), i.e.: 
-\[
-\mathbf{D}_{A}=[\mathbf{D}_{A}^{b},\mathbf{D}_{A}^{s}]=[d_{A,0}^{b},d_{A,1}^{b},\dots d_{A,k_{\mathbf{D}}^{b}-1}^{b},d_{A,0}^{s},d_{A,1}^{s},\dots d_{A,k_{\mathbf{D}}^{s}-1}^{s}],
-\]
-where $d_{A,n}^{b},\,d_{A,n}^{s}\in\left\{ 0,1\right\} $ and $k_{\mathbf{D}}^{b},\,k_{\mathbf{D}}^{s}$
-are the lengths of the basic and superposed data sub-words $\mathbf{D}_{A}^{b},\,\mathbf{D}_{A}^{s}$
-(respectively).
-
-Subsequently, individual $\mathbf{D}_{A}^{b},\mathbf{\,D}_{A}^{s}$
-are encoded by two separate linear binary encoders $\mathcal{C}_{b}(\centerdot),\,\mathcal{C}_{s}(\centerdot)$
-(assumed identical at both sources), producing the constituent codewords
-as:
-\begin{align}
-\mathcal{C}_{b}(\mathbf{D}_{A}^{b}) & =\mathbf{C}_{A}^{b}=[\mathbf{c}_{A,0}^{b},\mathbf{c}_{A,1}^{b},\dots,\mathbf{c}_{A,\mathcal{N}-1}^{b}],\\
-\mathcal{C}_{s}(\mathbf{D}_{A}^{s}) & =\mathbf{C}_{A}^{s}=[\mathbf{c}_{A,0}^{s},\mathbf{c}_{A,1}^{s},\dots,\mathbf{c}_{A,\mathcal{N}-1}^{s}],
-\end{align}
-where $\mathcal{N}$ is the number of codeword symbols (equivalently
-the number of channel uses required to transmit the codeword) and
-$$\mathbf{c}_{A,j}^{b}=[c_{A,j_{0}}^{b},\dots,c_{A,j_{N_{b}-1}}^{b}],$$
-$$\mathbf{c}_{A,j}^{s}=[c_{A,j_{0}}^{s},\dots,c_{A,j_{N_{s}-1}}^{s}]$$
-are codeword symbols of length $N_{b}$ (respectively $N_{s}$) bits.
-The dimensionality of binary codewords is thus $\left|\mathbf{C}_{A}^{b}\right|=\left|\mathbf{C}_{B}^{b}\right|=n_{\mathbf{C}}^{b}=\mathcal{N}\cdot N_{b}$,
-$\left|\mathbf{C}_{A}^{s}\right|=\left|\mathbf{C}_{B}^{s}\right|=n_{\mathbf{C}}^{s}=\mathcal{N}\cdot N_{s}$.
-
-The constituent codewords \textbf{$\mathbf{C}_{A}^{b},\,\mathbf{C}_{A}^{s}$}
-are then forwarded to the joint constellation mapper $\mathcal{A}^{A}\left(\centerdot\right)$
-(provided by Algorithm~\ref{alg:CTUpp_ButterflyConstellationDesign}),
-which produces a sequence of $(N_{s}+N_{b})$-bit constellation symbols
-$s_{A,j}=\mathcal{A}^{A}\left(\left[\mathbf{c}_{A,j}^{b};\mathbf{c}_{A,j}^{s}\right]\right)$.
-Note that in the encoded system it is the codeword symbols that are
-mapped to the desired constellation (instead of data symbols), but
-since $\left|\mathbf{c}_{A}^{b}\right|=\left|\mathbf{c}_{B}^{b}\right|=N_{b}$
-and $\left|\mathbf{c}_{A}^{s}\right|=\left|\mathbf{c}_{B}^{s}\right|=N_{s}$,
-it is sufficient to formally substitute the codeword symbol $\mathbf{c}_{i}=\left[\mathbf{c}_{i}^{b};\mathbf{c}_{i}^{s}\right]$
-for the data symbol $\mathbf{d}_{i}=\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]$
-in Algorithm~\ref{alg:CTUpp_ButterflyConstellationDesign} (lines~\ref{alg_line:CTUpp_input_data},~\ref{alg_line:CTUpp_const_symbols}).
-The resulting constellation symbols are successively transmitted by
-$S_{A}$ (simultaneously with $s_{B,j}$ from $S_{B}$) towards the
-relay node.
-
-\subsubsection{Relay processing}
-
-The crucial part of the encoded WBN system processing is based at
-the relay node. Like the uncoded case, the relay must decode jointly
-the \emph{superposed} data sub-words ($\mathbf{D}_{A}^{s},\,\mathbf{D}_{B}^{s}$)
-along with the \emph{WNC function }of \emph{basic} data sub-words
-($f(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})=\mathbf{D}_{A}^{b}\oplus\mathbf{D}_{B}^{b}$).
-Whilst both $\mathbf{D}_{A}^{s},\,\mathbf{D}_{B}^{s}$ can be decoded
-straightforwardly by the relay (using conventional single user decoders
-$\mathcal{C}_{s}^{-1}$), the fundamental question is how to decode
-the WNC function $f(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})$ since
-both $\mathbf{D}_{A}^{b},\,\mathbf{D}_{B}^{b}$ are encoded separately
-at sources $S_{A},\,S_{B}$\footnote{Note that separate decoding of $\mathbf{D}_{A}^{b},\,\mathbf{D}_{B}^{b}$
-and subsequent evaluation of $f(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})$
-(i.e. conventional joint/multi-user decoding concatenated with traditional
-network coding\cite{Yeung-Li-etal_NetworkCodingTheory}) can significantly
-limit the performance of the system \cite{Sykora-Burr_2011-TVT}.}. Fortunately, as proven in \cite{Sykora-Burr_2011-TVT}, the WNC
-function $f(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})$ can be decoded
-directly from the relay observation (\ref{eq:CTUpp_relay-received}),
-if the particular source data words are encoded by the same linear
-encoder $\mathcal{C}_{b}$, since
-\begin{align}
-\mathcal{C}_{b}\left(f(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})\right) & =\mathcal{C}_{b}\left(\mathbf{D}_{A}^{b}\oplus\mathbf{D}_{B}^{b}\right)\nonumber \\
- & =\mathcal{C}_{b}(\mathbf{D}_{A}^{b})\oplus\mathcal{C}_{b}(\mathbf{D}_{B}^{b})\nonumber \\
- & =\mathbf{C}_{A}^{b}\oplus\mathbf{C}_{B}^{b},
-\end{align}
-where $\mathbf{C}_{A}^{b}\oplus\mathbf{C}_{B}^{b}$ itself is again
-a valid codeword and hence the WNC function $f(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})$
-can be decoded directly from the relay observation (using a conventional
-single user decoder $\mathcal{C}_{b}^{-1}$).
-
-After decoding all required data streams ($\mathbf{\hat{D}}_{A}^{s},\,\hat{\mathbf{D}}_{B}^{s},\,\hat{f}(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})$),
-the relay creates a joint data word $\mathbf{D}_{R}=[\mathbf{\hat{D}}_{A}^{s},\hat{\mathbf{D}}_{B}^{s},\hat{f}(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})]$
-and re-encodes it as $\mathcal{C}_{R}(\mathbf{D}_{R})=\mathbf{C}_{R}=[\mathbf{c}_{R,0},\mathbf{c}_{R,1},\dots,\mathbf{c}_{R,\mathcal{N}-1}]$.
-The encoded data are then mapped to the output $2^{N_{R}}$-QAM (where
-$N_{R}=2N_{s}+N_{b}$) constellation symbols $s_{R,j}=\mathcal{A}^{R}\left(\mathbf{c}_{r,j}\right)$,
-$j\in\{0,1,\dots,\mathcal{N}-1\}$ and broadcast by the relay to both
-destination nodes.
 \begin{figure*}
@@
 
-\subsubsection{Destination processing}
-
-As in the uncoded case, destinations $D_{A},\,D_{B}$ firstly store
-the signal received in the MA phase, and then, after decoding the
-relay data word $\mathbf{D}_{R}$ (from the signal received in the
-BC phase), both destinations can perform IC to remove the unintended
-superposed codewords from the MA phase signal to get the desired HSI
-and then finally recover the desired data (see Fig.~\ref{fig:CTUpp_Information-flow-coded-block-scheme}
-for the details).
-
-\subsection{Analysis of Transmission Rates}
-
-The last step in the design of a feasible modulation and coding scheme
-for WBN (see Fig.~\ref{fig:CTUpp_Information-flow-coded-block-scheme})
-is to identify the range of permissible transmission rates for the
-basic ($r_{b}$), superposed ($r_{s}$) and relay output ($r_{R}$)
-data streams. To achieve this goal, we analyze the Constellation Constrained
-(CC) capacities \cite{Biglieri_CodWirelessChan} of the proposed source
-constellations, including the CC capacity of the conventional relay
-output $2^{N_{R}}$-QAM alphabets (used in the BC phase of communication).
-
-The transmission rates are defined in bits per channel use, and hence
-$r_{i}=N_{i}\cdot\nicefrac{k_{\mathbf{D}}^{i}}{n_{\mathbf{C}}^{i}}$,
-where $N_{i}$ is the number of bits per channel symbol/use in the
-data stream $i,$ $i\in\{b,s,R\}$. In accordance with the definition
-of source and relay codewords, we assume that each communication round
-requires $2\mathcal{N}$ channel uses, where the length of both MA
-and BC phase is set to $\mathcal{N}$ channel uses. Note that the
-assumption that BC and MA phases have identical length is generally
-only suboptimal (see e.g. \cite{Popovski-Yomo_2007a,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}),
-but nevertheless it is a common assumption in practical systems and
-hence we limit our attention to this particular case.
-
-\subsubsection{Relay observation}
-
-After splitting the source data streams, the whole system can be interpreted
-as a 4-user system where the relay has to decode the data $\mathbf{D}_{A}^{s},\,\mathbf{D}_{B}^{s},\,f(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})$
-from the \emph{virtual 3-user }($S_{A}^{s},\,S_{B}^{s},\,S_{AB}^{b}$)
-\emph{multiple-access channel} observation (see Fig.~\ref{fig:CTUpp_Information-flow-coded-block-scheme}).
-Unfortunately, since one of the users ($S_{AB}^{b}$) is only virtual,
-we cannot simply claim that the region of achievable rates in this
-virtual channel can be derived directly from the conventional cut-set
-bound analysis (see e.g. \cite{Cover-Thomas_ElemInfTheory,Harshan-Rajan-2011-IEEE-T-IT}),
-but rather a careful information-theoretic analysis would be required
-to identify the exact rate region. However, such analysis is far beyond
-the scope of this paper, and hence, for simplicity reasons, we only
-conjecture that the eligible source rates ($r_{b},\,r_{s}$) are limited
-by the conventional CC multiple-access capacity region \cite{Cover-Thomas_ElemInfTheory,Harshan-Rajan-2011-IEEE-T-IT},
-which can be defined by the following set of mutual informations $I(\centerdot;\centerdot)$:
-\begin{align}
-2r_{s}+r_{b} & \leq I(x;\mathbf{c}_{A}^{s},\mathbf{c}_{B}^{s},f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})),\label{eq:CTUpp_CSB_3}\\
-2r_{s} & \leq I(x;\mathbf{c}_{A}^{s},\mathbf{c}_{B}^{s}|f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})),\label{eq:CTUpp_CSB_2a}\\
-r_{s}+r_{b} & \leq I(x;\mathbf{c}_{A}^{s},f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})|\mathbf{c}_{B}^{s}),\label{eq:CTUpp_CSB_2b}\\
-r_{s}+r_{b} & \leq I(x;\mathbf{c}_{B}^{s},f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})|\mathbf{c}_{A}^{s}),\label{eq:CTUpp_CSB_2c}\\
-r_{s} & \leq I(x;\mathbf{c}_{A}^{s}|\mathbf{c}_{B}^{s},f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})),\label{eq:CTUpp_CSB_1a}\\
-r_{s} & \leq I(x;\mathbf{c}_{B}^{s}|\mathbf{c}_{A}^{s},f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})),\label{eq:CTUpp_CSB_1b}\\
-r_{b} & \leq I(x;f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})|\mathbf{c}_{A}^{s},\mathbf{c}_{B}^{s}),\label{eq:CTUpp_CSB_1c}
-\end{align}
-where (\ref{eq:CTUpp_CSB_3}), (\ref{eq:CTUpp_CSB_2a})-(\ref{eq:CTUpp_CSB_2c})
-and (\ref{eq:CTUpp_CSB_1a})-(\ref{eq:CTUpp_CSB_1c}) are the corresponding
-third, second and first order cut-set bounds (respectively). As we
-show later, the CC MAC region (as defined by (\ref{eq:CTUpp_CSB_3})-(\ref{eq:CTUpp_CSB-HSI-A}))
-provides a reasonable estimate of the maximal achievable source transmission
-rate pair ($r_{b},\,r_{s}$) in WBN.
-
-Since the superposed data sub-words $\mathbf{D}_{A}^{s},\,\mathbf{D}_{B}^{s}$
-are mapped to orthogonal ASK sets (Algorithm~\ref{alg:CTUpp_ButterflyConstellationDesign}),
-the 2nd order cut-set bound $I(x;\mathbf{c}_{A}^{s},\mathbf{c}_{B}^{s}|f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b}))$
-(\ref{eq:CTUpp_CSB_2a}) is equivalent to $I(x;\mathbf{c}_{A}^{s}|\mathbf{c}_{B}^{s},f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b}))+I(x;\mathbf{c}_{B}^{s}|\mathbf{c}_{A}^{s},f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b}))$
-(defined in eqs. (\ref{eq:CTUpp_CSB_1a}) and (\ref{eq:CTUpp_CSB_1b})),
-which can be proven easily by the chain rule for mutual information
-of orthogonal signal sets (see \cite{Cover-Thomas_ElemInfTheory}).
-Moreover, due to the assumed WBN system symmetry, the cut-set bounds
-defined in equations (\ref{eq:CTUpp_CSB_1a}), (\ref{eq:CTUpp_CSB_1b})
-are identical, and the same is true for the pair of cut-set bounds
-defined in (\ref{eq:CTUpp_CSB_2b}), (\ref{eq:CTUpp_CSB_2c}). Consequently,
-the CC multiple-access capacity region is completely defined by the
-four inequalities in (\ref{eq:CTUpp_CSB_3}), (\ref{eq:CTUpp_CSB_2b}),
-(\ref{eq:CTUpp_CSB_1a}) and (\ref{eq:CTUpp_CSB_1c}).
-
-\subsubsection{Effective HSI channels}
-
-In addition to the successful relay decoding, the transmission rate
-of the basic information stream $r_{b}$ must guarantee that the HSI
-(given by the unintended data sub-words $\mathbf{D}_{A}^{b}$ at $D_{B}$
-and $\mathbf{D}_{B}^{b}$ at $D_{A}$) can be decoded at both destinations
-(after perfect IC of superposed data codewords $\mathbf{C}_{A}^{s}$
-at $D_{B}$ and $\mathbf{C}_{B}^{s}$ at $D_{A}$ from the stored
-MA phase signal). Note that since we assume that the relay has already
-successfully decoded $f(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})$ at
-this step, it can be efficiently exploited in the decoding process,
-resulting in the following upper-bounds on the source rate $r_{b}$:
-\begin{align}
-r_{b} & \leq I(z_{B}^{\text{IC}};\mathbf{c}_{A}^{b}|f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})),\label{eq:CTUpp_CSB-HSI-B}\\
-r_{b} & \leq I(z_{A}^{\text{IC}};\mathbf{c}_{B}^{b}|f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})),\label{eq:CTUpp_CSB-HSI-A}
-\end{align}
-where $z_{A}^{\text{IC}},\,z_{B}^{\text{IC}}$ are the efficient HSI
-observations (after perfect IC) at $D_{A},\,D_{B}$ (respectively)
-\textendash{} see Fig.~\ref{fig:CTUpp_Information-flow-coded-block-scheme}.
-Both (\ref{eq:CTUpp_CSB-HSI-B}), (\ref{eq:CTUpp_CSB-HSI-A}) are
-identical in the symmetric WBN system.
 \begin{figure*}
@@
 
-\subsubsection{Relay broadcast channel}
-
-The relay rate $r_{R}$ must guarantee that its data word $\mathbf{D}_{R}=[\mathbf{\hat{D}}_{A}^{s},\hat{\mathbf{D}}_{B}^{s},\hat{f}(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})]$
-with length $\left|\mathbf{D}_{R}\right|=2k_{\mathbf{D}}^{s}+k_{\mathbf{D}}^{b}=\mathcal{N}(2r_{s}+r_{b})$
-can be sent to both destinations in $\mathcal{N}$ channel uses. In
-addition to this, to enable successful decoding of the relay data
-at both destinations, the relay transmission rate $r_{R}$ must be
-below the CC capacities of the corresponding relay$\rightarrow$destination
-channels. Thus, the relay rate should be set to $r_{R}=r_{b}+2r_{s}$,
-which gives us the last two inequalities for $r_{b},\,r_{s}$:
-\begin{align}
-r_{R}=2r_{s}+r_{b} & \leq I(y_{A};\mathbf{c}_{R}),\label{eq:CTUpp_CSB-D_A}\\
-r_{R}=2r_{s}+r_{b} & \leq I(y_{B};\mathbf{c}_{R}),\label{eq:CTUpp_CSB-D_B}
-\end{align}
-where both cut-set bounds (\ref{eq:CTUpp_CSB-D_A}), (\ref{eq:CTUpp_CSB-D_B})
-are identical due to the system symmetry.
-
-\subsection{Transmission Rate Region for Fixed Source Constellation\label{sub:CTUpp_Transmission-Rate-Region}}
-
-To identify the region $\left(r_{b},\,r_{s}\right)\in\mathcal{R}^{(N_{b},N_{s})}$
-of eligible transmission rates for a fixed $(N_{b},N_{s})$ source
-constellation, we can evaluate numerically\footnote{The (conditional) probability density function $p(x|\mathbf{c}_{A}^{s},\mathbf{c}_{B}^{s},f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b}))$
-which is required for the evaluation of particular mutual information
-in (\ref{eq:CTUpp_CSB_3})-(\ref{eq:CTUpp_CSB-HSI-A}) can be obtained
-by a proper marginalization operation $p(x|\mathbf{c}_{A}^{s},\mathbf{c}_{B}^{s},f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b}))=\mathrm{Pr}\left\{ f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})\right\} \cdot\sum_{\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b}:f(\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})}p\left(x|\mathbf{c}_{A}^{s},\mathbf{c}_{B}^{s},\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b}\right)$,
-where $p(x|\mathbf{c}_{A}^{s},\mathbf{c}_{B}^{s},\mathbf{c}_{A}^{b},\mathbf{c}_{B}^{b})$
-is the likelihood function. For more details on the evaluation of
-CC capacity for finite input constellations see e.g. \cite{Harshan-Rajan-2011-IEEE-T-IT,Sykora-Burr_2011-TVT}.} the set of relevant cut-set bounds (i.e. (\ref{eq:CTUpp_CSB_3}),
-(\ref{eq:CTUpp_CSB_2b}), (\ref{eq:CTUpp_CSB_1a}), (\ref{eq:CTUpp_CSB_1c}),
-(\ref{eq:CTUpp_CSB-HSI-B}) and (\ref{eq:CTUpp_CSB-D_A})) for given
-SNR conditions in the symmetric WBN system ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$).
-An example analysis of the source transmission rate region $\mathcal{R}^{(2,1)}$
-for the $(N_{b}=2,\,N_{s}=1)$ source constellation is visualized
-in Fig.~\ref{fig:CTUpp_CSB_eval} for two different SNR setups. The
-cut-set bound rate region $\mathcal{R}^{(N_{b},N_{s})}$ is emphasized
-by the shaded area and the rate pair with maximal $r_{b}+r_{s}$ is
-identified in the figure. We have assumed that the source$\rightarrow$relay
-channels are AWGN (or equivalently that perfect source phase prerotation
-\cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008}
-is implemented) in the numerical evaluation.
-
-\section{Performance Analysis II: Adaptive Encoded System\label{sec:CTUpp_Performance-Analysis-Coded}}
-
-As shown in Fig.~\ref{fig:CTUpp_CSB_eval}, the performance of the
-encoded WBN system is, like in the uncoded case, influenced by the
-immediate SNR conditions (given by $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$)
-and hence an \emph{adaptive modulation and coding scheme }is again
-of interest. However, before we introduce the\emph{ SNR mapping operation}
-for the encoded system, we show that the cut-set bound rate regions
-$\mathcal{R}^{(N_{b},N_{s})}$ (as introduced in the preceding section)
-provide a reasonable approximation of achievable source transmission
-rate pairs in the symmetric WBN system. In the whole section we assume
-(for simplicity reasons) that perfect source phase prerotation \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008}
-is implemented in the system, virtually reverting the source$\rightarrow$relay
-channels to the AWGN case.
-
-\subsection{Numerical Simulation of Encoded WBN System Throughput\label{sub:Numerical-Simulation-of}}
-
-We implement all constituent channel encoders in the WBN system (see
-Fig.~\ref{fig:CTUpp_Information-flow-coded-block-scheme}) as parallel
-concatenated turbo codes with random interleavers of length $\mathcal{N}=10^{5}$
-symbols. By proper puncturing \cite{Schlegel-Perez_TrellisTurboCoding}
-of the channel encoders' outputs we are able to set the source transmission
-rates (separately for the basic and superposed streams) to an almost
-arbitrary value in the range ($\nicefrac{1}{3}\rightarrow1$). We
-set the initial source transmission rates to the maximum $r_{b}+r_{s}\in\mathcal{R}^{(N_{b},N_{s})}$
-(as evaluated in Fig.~\ref{fig:CTUpp_CSB_eval}) and by proper adjustment
-of the puncturing operation we successively decrease the source transmission
-rates $r_{b},\,r_{s}$ until the SER performance drops to zero. As
-one can see in Fig.~\ref{fig:CTUpp_CSB_eval}, the achieved transmission
-rate pairs are relatively close to the maximal permissible values
-and hence we can consider the cut-set bound rate region $\mathcal{R}^{(N_{b},N_{s})}$
-(as discussed in Section \ref{sub:CTUpp_Transmission-Rate-Region})
-to be a reasonable approximation of the achievable source transmission
-rate region.
-
-\subsection{Maximal Throughput of the Adaptive Modulation-Coding Scheme\label{sub:Maximal-Throughput-of}}
-
-As in the uncoded case, the source nodes $S_{A},\,S_{B}$ in the adaptive
-modulation-coding WBN system must be aware of the particular mapping
-operation $(\hat{\gamma}_{{\rm {MAC}}},\,\hat{\gamma}_{{\rm {BC}}},\,\hat{\gamma}_{{\rm {HSI}}})\mapsto\left(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}};\,r_{b}^{\mathrm{II}},\,r_{s}^{\mathrm{II}}\right),$
-providing the set of optimal (in the sense of maximal throughput)
-constellation/encoder parameters for the given SNR conditions ($\hat{\gamma}_{{\rm {MAC}}},\,\hat{\gamma}_{{\rm {BC}}},\,\hat{\gamma}_{{\rm {HSI}}}$).
-Note that, in general, all adaptive system parameters are functions
-of the actual SNR conditions in the system. However, we mostly omit
-the explicit notation in the following text for to aid readability.
-
-The desired adaptive system parameters can be obtained in the following
-two-step procedure. First of all, we analyze the cut-set bound rate
-regions $\mathcal{R}^{(N_{b},N_{s})}$ (as discussed in Section \ref{sub:CTUpp_Transmission-Rate-Region})
-to identify the maximal encoded system throughput $T_{C}^{(N_{b},N_{s})}$
-for a fixed source constellation $(N_{b},N_{s})$:
-\begin{align}
-T_{C}^{(N_{b},N_{s})}(\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}) & =\max_{r_{b},r_{s}\in\mathcal{R}^{(N_{b},N_{s})}}(r_{b}+r_{s}),\\
- & =r_{b}^{\mathrm{max}}(N_{b},N_{s})+r_{s}^{\mathrm{max}}(N_{b},N_{s}).\label{eq:CTUpp_opt_rates}
-\end{align}
- Then, an exhaustive search over the constellation parameters $N_{b},\,N_{s}$
-can be performed to find the maximum encoded system throughput $T_{C}^{\mathrm{max}}$
-for the given SNR conditions ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$):
-\begin{equation}
-T_{C}^{\mathrm{max}}(\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}})=T_{C}^{(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}})}=\max_{(N_{b},N_{s})}T_{C}^{(N_{b},N_{s})},\label{eq:CTUpp_Throughput_encoded}
-\end{equation}
-where $(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}})$ are the \emph{optimal
-source constellation parameters}. The corresponding \emph{optimal
-source transmission rates} (\ref{eq:CTUpp_opt_rates}) are given simply
-by \emph{$r_{b}^{\mathrm{II}}=r_{b}^{\mathrm{max}}(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}})$,
-$r_{s}^{\mathrm{II}}=r_{s}^{\mathrm{max}}(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}})$.}
 \begin{figure*}
@@
 
-The SNR mapping regions (including the throughput $T_{C}^{\mathrm{max}}$)
-for the adaptive modulation and coding scheme in WBN are evaluated
-as a function of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$ in
-Fig.~\ref{fig:CTUpp_Coded_SNR_map} for $\gamma_{{\rm {BC}}}\in\{7.5\,\mathrm{dB},\,15\,\mathrm{dB}\}$.
-As one can see in Fig.~\ref{fig:CTUpp_Coded_ThroughputGain}, the
-increased reliability of transmissions on all individual channels
-in WBN (as compared to the uncoded system) translates directly into
-a significant enhancement of throughput performance in the whole range
-of observed SNRs. This observation justifies the viability of the
-proposed channel coding scheme.
-
-\subsection{Robustness Analysis}
-
-In this section we show that the proposed modulation and coding scheme
-is viable even if the real world conditions induce some deviations
-from the system model assumed in this paper. From a practical point
-of view, we would be interested mainly in the situation, where a direct
-channel between a source and its desired destination is present (see
-Fig.~\ref{fig:CTUpp_DirectChannel}). Even though that this \textquotedbl{}direct\textquotedbl{}
-channel can be relatively weak, it inevitably affects the destinations'
-HSI observations. In addition to this, we analyse the system where
-source phase pre-rotation is switched off (or ineffective due to rapid
-channel dynamics), and thus the relay faces a multiple-access channel
-with a varying source channel phase offset. This assumption is valid
-for a practical system where the applicability of source phase pre-rotation
-is limited due to the unavailable ideal feedback channel or because
-of the undesirable delay induced by the feedback in the pre-rotation
-operation. To demonstrate the robustness of the proposed modulation
-and coding strategy, we compare the WBN performance results achieved
-by the Monte-Carlo numerical evaluation (see section \ref{sub:Numerical-Simulation-of})
-with USRP HW measurements. While in the numerical evaluation we still
-keep the idealized assumptions as defined by our system model (i.e.
-no direct source$\rightarrow$destination channels, perfect channel
-phase pre-rotation), in the HW measurements we now let all data communication
-to be performed through real wireless channels (compare with the HW
-setup in section~\ref{sub:CTUpp_Hardware_Verification}), introducing
-inevitably some direct channel observation at both destinations. In
-addition, we allow the source phase pre-rotation to be switched off
-in the HW measurements. The channel SNRs $\gamma_{{\rm {MAC}}},\gamma_{{\rm {HSI}}}$
-in the HW measurements can be controlled by the source transmit power
-adjustment and similarly, particular values of $\gamma_{{\rm {BC}}}$
-can be set up by the adjustment of the relay transmit power.
 \begin{figure}
@@
 
-To perform a comparison of the idealized numerical evaluation with
-the HW robustness measurements, we evaluate the range of SNRs where
-a zero error rate performance can be achieved for fixed constellations
-and channel encoder rates $(N_{b},N_{s},r_{b},r_{s})$. To achieve
-this, we identify the triplet of SNRs ($\gamma_{{\rm {MAC}}},\gamma_{{\rm {HSI}}}$,
-$\gamma_{{\rm {BC}}}$) providing a zero-error rate performance at
-both destinations. This SNR triplet then defines the lower-most corner
-of the SNR region where a zero error rate performance can be achieved
-(see Fig. \ref{fig:CTUpp_Robustenss_analysis}). We can conclude that:
-\begin{itemize}
-\item The presence of direct links requires only a slightly increased values
-of ($\gamma_{{\rm {MAC}}},\gamma_{{\rm {HSI}}}$, $\gamma_{{\rm {BC}}}$)
-to ensure a zero error-rate performance for the fixed $(N_{B},N_{S},r_{b},r_{s})$.
-However, it is evident that a modification of the proposed modulation
-and coding scheme could be desirable to fully harness the information
-transmitted over direct source destination channels.
-\item The source channel phase asynchrony in the system with direct links
-further degrades the performance on the sources$\rightarrow$relay
-channel and thus an additional increase of the source transmission
-power (and consequently $\gamma_{{\rm {MAC}}}$) is required to provide
-a zero-error rate. However, $\gamma_{{\rm {BC}}}$ is not affected
-in this case, as the channel pre-rotation does not have any impact
-on the relay$\rightarrow$destination performance.
-\end{itemize}
-
-\section{Conclusions and Future Work\label{sec:CTUpp_DiscussionConclusions-etc}}
-
-In this paper we have proposed a systematic algorithm for the design
-of two-source constellations in the WBN system. The Algorithm~\ref{alg:CTUpp_ButterflyConstellationDesign}
-allows the matching of the constellation parameters to virtually any
-SNR conditions in the system, enabling a direct implementation of
-the adaptive constellation mapping scheme. The viability of the proposed
-constellation design was verified by a means of numerical analysis
-and simulations and also by a real-world HW experiment (based on Ettus
-Research USRPs), including a HW-based robustness analysis.
-
-Even in the uncoded scenario, the proposed constellations are able
-to significantly boost the WBN system throughput, and hence even their
-uncoded implementation can be interesting, especially in some basic
-wireless networks where channel coding is avoided to reduce complexity
-(e.g. in sensor networks). Furthermore, we have shown that the proposed
-source constellation design can be readily extended with appropriately
-designed channel encoding/decoding operations, significantly improving
-the reliability (including the throughput) of the resulting adaptive
-modulation-coding scheme.
-
-In future work, we would like to focus on a full adaptive HW implementation
-of the proposed system, where the impact of several other parameters
-(e.g. channel fading and dynamics, asymmetry of channel gains etc.)
-can significantly affect the system performance and possibly even
-require some modifications of the adaptive system design.
 \begin{figure*}
@@
 
-\pagebreak{}
-
-\section*{Declarations}
-
-This work was partly reported in IEEE ICC \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}.
-
-\section*{Funding}
-
-This work has been performed in the framework of the European research
-project DIWINE, which is partly funded by the European Union under
-its FP7 ICT Objective 1.1 - The Network of the Future. Work of Pavel
-Prochazka and Tomas Uricar was also partially supported by the Grant
-Agency of the Czech Technical University in Prague, SGS project SGS16/094/OHK3/1T/13.
-
-\bibliographystyle{ieeetr}
-\bibliography{bib/bib,bib/uricar,bib/uricar-papers,bib/uricar-books,bib/sykora,bib/books}
-
 \end{document}

### 2017-05-19 scripts/cite_extraction.py

@@ -1,0 +1,56 @@
+import bibtexparser
+from bibtexparser.bwriter import BibTexWriter
+from bibtexparser.bibdatabase import BibDatabase
+
+infile = open('Const_design.tex', 'r')
+#outfile = open('citations', 'w')
+cits = []
+bibfiles = []
+for line in infile:
+    if 'cite' in line:
+        while True:
+            ind = line.find('cite')
+            if ind >= 0:
+                line = line[(ind + 4):]
+                i_e = line.find('}')
+                items = line[1:i_e]
+                cits += items.split(',')
+                line = line[(i_e + 1):]
+                #outfile.write("\n\n")
+            else:
+                break
+    if 'bibliography{' in line:
+        ind = line.find('{')
+        i_e = line.find('}')
+        items = line[(ind+1):i_e]
+        bibfiles += items.split(',')
+
+
+infile.close()
+
+cits_uniq = []
+for c in cits:
+    if not c in cits_uniq:
+        cits_uniq.append(c)
+
+for i, c in enumerate(cits_uniq):
+    print i, c
+
+res_dir = []
+for c in cits_uniq:
+    for f in bibfiles:
+        with open(f+'.bib') as bibtex_file:
+            bib_database = bibtexparser.load(bibtex_file)
+            if c in bib_database.entries_dict.keys():
+                res_dir.append(bib_database.entries_dict[c])
+                break
+
+db = BibDatabase()
+db.entries = res_dir
+
+writer = BibTexWriter()
+with open('bib/res_bib.bib', 'w') as bibfile:
+    bibfile.write(writer.write(db))
+
+        
+#outfile.close()

### 2017-05-19 scripts/extractor.py

@@ -1,0 +1,23 @@
+infile = open('Const_design.tex', 'r')
+outfile_fig = open('all_figures.tex', 'w')
+outfile_tab = open('all_tables.tex', 'w')
+extract_block_fig = False
+extract_block_tab = False
+for line in infile:
+    if ('begin{figure}' in line) or ('begin{figure*}' in line):
+        extract_block_fig = True
+    if 'begin{table}' in line:
+        extract_block_tab = True
+    if extract_block_fig:
+        outfile_fig.write(line)
+    if extract_block_tab:
+        outfile_tab.write(line)
+    if ('end{figure}' in line) or ('end{figure*}' in line):
+        extract_block_fig = False
+        outfile_fig.write("\n\n")
+    if 'end{table}' in line:
+        extract_block_tab = False
+        outfile_tab.write("\n\n")
+infile.close()
+outfile_fig.close()
+outfile_tab.close()

### 2017-05-19 scripts/fig_remover.py

@@ -1,0 +1,13 @@
+infile = open('Const_design.tex', 'r')
+outfile = open('Const_design_final.tex', 'w')
+fig_list = open('fig_list', 'w')
+for line in infile:
+    if not 'includegraphics' in line:
+        outfile.write(line)
+    else:
+        st_ind = line.find('fig')
+        act_fig = line[st_ind:-2]+'\n'
+        fig_list.write(act_fig)
+infile.close()
+outfile.close()
+fig_list.close()

### 2017-05-22 response_letter/response_letter.tex
Added supporting Python code - requires Turbo-lib that can be found at https://github.com/ProchazkaPavel/commlib/tree/master/Turbo_lib

@@
   possible to generalize to other similar networks where linear codes yield a good performance.}
-  \item A: We should stress that the modulation design covers both
+  \item A2-1: We should stress that the modulation design covers both
   wireless network coding and processing the signal from multiple stages. Join generalization of
-  both phenomenons in the way we did would be extremely challenging, because of synchronization,
-  pre-rotation, etc. Also note that our approach is basically a practical instance of a well known
+  both techniques in the way we did would be extremely challenging, because of time 
+  synchronization, pre-rotation, etc. Also note that our approach is basically a 
+  practical instance of a well known
   theoretical principle with application of WNC to approximately equal power levels and
   interference cancellation on significantly different power levels. So that its generalization in
-  theoretical level is already known. This answers also general comments.
+  theoretical level is already known. 
 \end{itemize}
@@
   constellation and explain why the challenges to apply to other linear networks.}
-  \item A: The intuition beyond the design could be partly found in ICC (TODO)
+  \item A: The intuition beyond the design could be partly found in ICC.  
 \end{itemize}
@@
 \begin{itemize}
-  \item Q: \emph{-It might be useful to the reader to add a figure for the butterfly network in the
+  \item Q: \emph{It might be useful to the reader to add a figure for the butterfly network in the
   setting of algebraic network coding for comparison.}
   \item A: see A2
+\end{itemize}
+
+\begin{itemize}
+  \item Q: \emph{It might be useful to the reader to add a figure for the butterfly network in the
+  setting of algebraic network coding for comparison.}
+  \item A: see A2
+\end{itemize}
+
+\begin{itemize}
+  \item Q: \emph{Since real world networks are usually more complicated, I think it would be really interesting if this systematic design can be generalized to all linear network coding schemes (e.g.
+random linear network coding).}
+  \item A: see A2
+\end{itemize}
+\begin{itemize}
+  \item Q: \emph{If it cannot be easily generalized, it could be helpful to explain what are the
+  difficulties in applying it to other coding schemes.}
+  \item A: 
 \end{itemize}

### 2017-05-22 python/coded/test_decoders_BICM.py

@@ -1,0 +1,1857 @@
+import os, sys, inspect
+sys.path.insert(0,'lib')
+from rew import *
+import LDPC_lib 
+import GFq_LDPC_lib
+from GFq_LDPC_lib import  *
+from compare_QPSK import QAM,const_design_XOR, const_superposed
+from Turbo_lib import *
+
+
+import _Turbo_lib
+import _GFq_LDPC_lib
+import _LDPC_dec_lib
+
+def const_map(bits):
+  '''
+  Conversion of N-bit binary data streams - (n * M x N) array to integer prepared for modulation.
+
+  Parameters:
+  -----------
+  M : int
+      Number of frames.
+  n : int
+      Length of frame.
+  N : int
+      Number of bits in constellation.
+  bits : array of ints
+      (n * M x N) 2D numpy array with binary data.
+
+  Returns: 
+  --------
+  inds : array of ints
+       (M * n) 1D numpy array with integer prepared to be modulated
+
+  See Also:
+  ---------
+  soft_demap
+
+  Examples:
+  ---------
+  
+  '''
+  [x, N] = np.shape(bits)
+  res = np.zeros(x, int)
+  for i in range(N):
+    res += bits[:, i] * (2 ** (N - i - 1))
+
+  return res
+  
+def demod(x, const, sigma2w, h = 1, norming = 0):
+  '''
+  Demodulation related to a given N-bit modulator. Assuming a P2P channel with Gaussian noise with
+  varianve sigma2w.
+
+  Parameters:
+  -----------
+  x : array of complex
+      Observation vector given by s + w, where s is modulated signal and w is iid. AWGN with variance
+      sigma2w.
+  const : array of complex
+      The one (complex) dimensional signal space mapping such that s = const[c_int], where c_int is
+      the index of carrying the information.
+  sigma2w : complex
+      Variance related to Gaussian noise in AWGN.
+  h : complex or array of complex
+      Fading coefficient. One can consider no fading (default value h = 1), block fading h = any
+      complex number or fast fading, where h can be also a complex array with the sime size as x      
+  norming : int
+      Flag if the resulting message should be normalized to pmf (i.e. the sum of each line of
+      resulting soft output should be 1)
+
+  Returns: 
+  --------
+  mu : array of floats
+       (M * n) x 2**N 2D numpy array, where 2**N is length of const. The matrix is soft metric for
+       decodign. 
+
+
+  See Also:
+  ---------
+  soft_demap, const_map, AWGN
+
+  Examples:
+  ---------
[…]

### 2017-05-22 python/constdesign/Block_functions.py

@@ -1,0 +1,215 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+def eval_sigma2w(SNR):
+  gammaAdB = float(SNR)
+  gammaA= 10.0**(gammaAdB/10)
+  return 1.0 / (gammaA)
+
+
+def dec2bin(x, num_bits=None): # Convert decimal number to binary narray
+  return np.asarray([int(c)  for c in np.binary_repr(x,width=num_bits)],dtype=int) # dec to bin array
+
+def dec2binvec(vec, num_bits):
+  l = len(vec)
+  bits = np.zeros([num_bits, l],int)
+  for i in range(num_bits): # Reverting the symbols back to bits
+    shift = (1 << i)
+    bits[num_bits - 1 - i, :] = (vec & shift) >> i
+  return bits.flatten(1)
+
+def bin2dec(vec): # Convert binary narray to decimal number
+  return int(np.array_str(vec).strip('[]').replace(' ',''),2)
+
+def bin2decvec(vec, num_bits):
+  l = len(vec)
+  vecr = vec.reshape(l/num_bits, num_bits).transpose()
+  d = np.zeros(l/num_bits, int)
+  for i in range(num_bits): 
+    d += vecr[num_bits - 1 - i, :] * (1 << i)
+  return d
+
+def revbinorder(x, num_bits=None):
+  return bin2dec(dec2bin(x, num_bits)[-1::-1])
+
+def index2vec(index, bits): # Convert a single index to multidimensional vector acording to sizes
+  vec = np.zeros(len(bits), dtype=int)
+  bin_vec = dec2bin(index, np.sum(bits))
+#  print bin_vec
+  start = 0
+  for i in range(0, len(bits)):
+    vec[i] = bin2dec(bin_vec[start:(start+bits[i])])
+    start += bits[i]
+  return vec
+
+def find_levels(i, levels, const, const_el):
+  if (len(levels) == 0):
+    return np.array([0]) # Empty constellation --- zero point
+  else:
+    const_out = np.asarray([c + levels[i] * el for c in const for el in const_el])
+#    print np.sort(const_out)
+    i += 1
+    if (i < len(levels)):
[…]

### 2017-05-22 python/constdesign/Numerical_BER.py

@@ -1,0 +1,296 @@
+import numpy as np
+from analytical_BER import SNR2sigma2w
+from Block_functions import Error_Check_Relay, Demodulator_relay, Modulator_network 
+
+def AWGN(signal, SNR): # Unit power per dimension assumed
+  sigma2w = SNR2sigma2w(SNR)
+  real_noise = np.random.normal(0,np.sqrt(sigma2w),np.shape(signal/2))
+  imag_noise = 1j * np.random.normal(0,np.sqrt(sigma2w),np.shape(signal/2))
+  noise = 1.0/np.sqrt(2)  * (real_noise + imag_noise)
+  return signal + noise
+
+### NUMERICAL PART (BER SIMULATION)
+
+# Numerical BER evaluation for QPSK
+def eval_numerical_BER_QPSK(SNR_vals, N):
+  d = np.random.randint(4,size=N)
+  QPSK = np.exp(1j * (np.pi * np.arange(0,4)/2.0 + np.pi/4))
+  s = QPSK[d]
+  BER = []
+  for SNR in SNR_vals:
+    est_d = np.zeros(N)
+    x = AWGN(s, SNR)
+    est_d[np.intersect1d(np.nonzero(np.real(x) > 0)[0],np.nonzero(np.imag(x) > 0)[0])] = 0
+    est_d[np.intersect1d(np.nonzero(np.real(x) < 0)[0],np.nonzero(np.imag(x) > 0)[0])] = 1
+    est_d[np.intersect1d(np.nonzero(np.real(x) < 0)[0],np.nonzero(np.imag(x) < 0)[0])] = 2
+    est_d[np.intersect1d(np.nonzero(np.real(x) > 0)[0],np.nonzero(np.imag(x) < 0)[0])] = 3
+    BER.append(np.sum(est_d != d))
+  return BER
+
+# Numerical BER evaluation for 8QAM
+def eval_numerical_BER_8QAM(SNR_vals, N):
+  d = np.random.randint(8,size=N)
+  QAM8 = np.asarray([i + 1j * j for i in np.arange(-3,5,2) for j in np.arange(-1,3,2)]) /np.sqrt(6)
+  s = QAM8[d]
+  BER = []
+  for SNR in SNR_vals:
+    est_d = np.zeros(N)
+    x = AWGN(s, SNR)
+    mu = np.asarray([np.abs(x - s0)**2 for s0 in QAM8])
+    est_d = mu.argmin(axis=0)
[…]

### 2017-05-22 python/constdesign/analytical_BER.py

@@ -1,0 +1,408 @@
+import numpy as np
+from scipy.special import erf
+from scipy.special import erfc
+
+# Function returning the value of two independent gaussian CDF(x1, x2)
+def prod_gauss2D(x1, m1, x2, m2, sigma2w):
+  D1 = 0.5 * (1. + erf((x1 - m1) / np.sqrt(sigma2w)))
+  D2 = 0.5 * (1. + erf((x2 - m2) / np.sqrt(sigma2w)))
+  return D1 * D2;
+
+def SNR2sigma2w(SNR):
+  alpha = 10**(float(SNR)/10)
+  return 1.0/alpha
+
+# Analytical BER evaluation for QPSK
+def eval_analytic_BER_QPSK(SNR):
+  sigma2w = SNR2sigma2w(SNR)
+  return 1 - prod_gauss2D(0, -np.sqrt(1./2),0 , -np.sqrt(1./2),sigma2w)
+
+# Analytical BER evaluation for 8PSK
+def eval_analytic_BER_8PSK(SNR):
+  sigma2w = SNR2sigma2w(SNR)
+  Delta = 0.01
+  x = np.arange(0,20,Delta)
+  y = np.tan(np.pi/8) * x
+  p = 0
+  for i in range(0, len(x) - 1):
+    LUu = prod_gauss2D(x[i], 1, y[i + 1], 0,sigma2w)
+    RUu = prod_gauss2D(x[i + 1], 1, y[i + 1], 0,sigma2w)
+
+    LUd = prod_gauss2D(x[i], 1, -y[i + 1], 0,sigma2w)
+    RUd = prod_gauss2D(x[i + 1], 1, -y[i + 1], 0,sigma2w)
+    p += RUu - RUd - (LUu - LUd)    
+  return 1 - p
+
+# Analytical BER evaluation for HDF with QPSK
+def eval_analytic_BER_QPSK_hierarchical(SNR):
+  sigma2w = SNR2sigma2w(SNR)
+  QPSK = np.exp(1j * (np.pi * np.arange(0,4)/2.0 + np.pi/4))
+  const_superposed = np.round(np.asarray([i + j for i in QPSK for j in QPSK]).flatten(),8)
+  con_unique = np.unique(const_superposed)
+  SI_c = np.asarray([(np.real(i), np.imag(i)) for i in con_unique])
+  x_shape = np.array([-np.sqrt(2)/2, np.sqrt(2)/2, np.inf])
[…]

### 2017-05-22 python/constdesign/compare_QPSK.py

@@ -1,0 +1,764 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.cm as cm
+from scipy.special import erf
+from scipy.special import erfc
+
+from analytical_BER import *
+from Numerical_BER import *
+
+def dec2bin(x, num_bits=None): # Convert decimal number to binary narray
+  return np.asarray([int(c)  for c in np.binary_repr(x,width=num_bits)],dtype=int) # dec to bin array
+
+def bin2dec(vec): # Convert binary narray to decimal number
+  return int(np.array_str(vec).strip('[]').replace(' ',''),2)
+
+def revbinorder(x, num_bits=None):
+  return bin2dec(dec2bin(x, num_bits)[-1::-1])
+
+def index2vec(index, bits): # Convert a single index to multidimensional vector acording to sizes
+  vec = np.zeros(len(bits), dtype=int)
+  bin_vec = dec2bin(index, np.sum(bits))
+#  print bin_vec
+  start = 0
+  for i in range(0, len(bits)):
+    vec[i] = bin2dec(bin_vec[start:(start+bits[i])])
+    start += bits[i]
+  return vec
+
+
+
+### Pairwise error approximation
+
+# Approximate the BER using the most probable pairwise error and mean number of neights
+def pair_wise_err(K, sigma2w, rho2):
+  return  K * erfc(np.sqrt(float(rho2)/sigma2w)/2) / 2
+
+# Evaluate BER for given NON-OVERLAPPING constellations
+def eval_pair_wise_err(SNR, const):
+  sigma2w = SNR2sigma2w(SNR)
+  dist = np.round(np.asarray([np.abs(const[i] - const[j])**2 \
+         for i in np.arange(0,len(const)) for j in np.arange(i+1,len(const))]),8)
+  rho2 = dist.min()
+  K = len(np.nonzero(dist == dist.min())[0]) * 2. / len(const) 
+  return pair_wise_err(K, sigma2w, rho2)
+
+# evaluate average number of neighboors and minimal distance for a given constellation
+def eval_num_neigh(const, alpha = 0): # 
[…]

### 2017-05-24 response_letter/response_letter.tex
Added Makefile and updated response
Corrected typo in response letter
Modification of Figures 6-9, improving some responses.

@@
 \begin{itemize}
-  \item CQ1: \emph{Lacking novelty compared to ICC}
+  \item CQ1: \emph{Lacking novelty compared to \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}}
   \item A1: Quoting the part of the cover letter for IEEE transaction submission:\newline
@@
   }
-  I believe that this answer could be enough. (Actualization -TODO)
 \end{itemize}
@@
   possible to generalize to other similar networks where linear codes yield a good performance.}
-  \item A2-1: We should stress that the modulation design covers both
+  \item A2-1: We should stress that the proposed constellation design covers both
   wireless network coding and processing the signal from multiple stages. Join generalization of
@@
   constellation and explain why the challenges to apply to other linear networks.}
-  \item A: The intuition beyond the design could be partly found in ICC.  
+  \item A: The intuition beyond the design could be partly found in \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}.  
+  Particularly, the idea is to consider bit streams that are divided among individual power levels.
+  We need to define 1) the scale of individual levels, 2) the constellation element for all levels.
+  Obviously, this design would differ for basic and superposed streams:
+  \begin{enumerate}
+    \item In case of superposed stream, we need to have both source streams decodable and thus we
+    need some kind of orthogonality. This orthogonality is achieved by considering real and
+    imaginary axis of the constellation space. 
+    \item
+  \end{enumerate}
+  Our solution considers the simplest possible constellation element (BPSK at given level)
 \end{itemize}
@@
 
+\begin{itemize}
+  \item Q: \emph{It might be useful to the reader to add a figure for the butterfly network in the
+	  setting of algebraic network coding for comparison.}
+  \item A: 
+\end{itemize}
+
+\begin{itemize}
+  \item Q: \emph{Might be helpful if mention beforehand that the nomenclature is given at the end of the paper (For
+	  example, HW is throughout the paper and its definition is only given at the end of the paper)}.
+  \item A: The nomenclature is placed according to the EURASIP-author's guidelines.
+\end{itemize}
+
 \subsubsection*{Reviewer 3}
@@
     WBN.}
-  \item A: partly see A2 for join decoding. Partly I remove throughput gain for (1,1) strategy
-  compared to QPSK (TODO) 
+  \item A: See A2. Considering the two time slot communication, there is indeed no state of the art solution
+      for joint decoding, that is the constellation design in sources such that the relay would reliably
+      jointly resolve data\footnote{We assume uncoded data in this context only.} from both sources. 
+      We thus decided to claim the performance of the proposed $N_b=0$, $N_s=2$ compared to the zero
+        throughput QPSK as the throughput gain. Nevertheless, the reviewer has point that it is unfair to claim the
+        performance of the proposed $N_b=1$, $N_s=1$ constellation as throughput gain compared to
+        zero-throughput QPSK, because a conventional wireless network coding with BPSK would give a
+        nonzero throughput in this case. We therefore drop this claim from our Figures 6-9 in
+        manuscript (check Figure \ref{Fig:Throughput_comparison}).
+
 \end{itemize}
@@
 However, it would be more appreciated if a hardware experiment can be done on this aspect.}
-  \item A: It actually is - check Figure 17
+  \item A: We fully understand and agree that the robustness analysis deserves further deep
+      investigation. Nevertheless we provided some basic analysis including the hardware experiment
+        within our work (check Figure 17 in manuscript) giving quite promising results. A more detailed investigation is suited rather
+        for a standalone work than for this resubmission.
 \end{itemize}
@@
 \section{Major Changes Summary}
-\begin{itemize}
-\item
-\end{itemize}
+\begin{figure}
+    %\begin{subfigure}[t]{0.5\textwidth}
+    \includegraphics[width=0.45\linewidth]{fig/old_Throughput_HSI_XOR_MAC16_BC20_N2.eps}
+    \includegraphics[width=0.45\linewidth]{fig/Throughput_HSI_XOR_MAC16_BC20_N2.eps}\\
+    \includegraphics[width=0.45\linewidth]{fig/old_Throughput_HSI_XOR_MAC20_BC20_N2.eps}
+    \includegraphics[width=0.45\linewidth]{fig/Throughput_HSI_XOR_MAC20_BC20_N2.eps}\\
+    \includegraphics[width=0.45\linewidth]{fig/old_Throughput_HSI_XOR_MAC20_BC16_N2.eps}
+    \includegraphics[width=0.45\linewidth]{fig/Throughput_HSI_XOR_MAC20_BC16_N2.eps}\\
+    \includegraphics[width=0.45\linewidth]{fig/old_Throughput_HSI_XOR_MAC17_BC17_N2.eps}
+    \includegraphics[width=0.45\linewidth]{fig/Throughput_HSI_XOR_MAC17_BC17_N2.eps}\\
+	\caption{Uncoded throughputs (old versions left, new versions right).}
+	\label{Fig:Throughput_comparison}
+	%\caption{Old uncoded throughput for $\gamma_{\mathrm{MAC}}=16$,$\gamma_{\mathrm{BC}}=20$.}
+    %\end{subfigure} 
+    %\begin{subfigure}[t]{0.45\textwidth}
+    %\caption{New the uncoded throughput for $\gamma_{\mathrm{MAC}}=16$,$\gamma_{\mathrm{BC}}=20$.}
+    %\end{subfigure} 
+\end{figure}
 
+\bibliographystyle{plain}
+\bibliography{Const_design}
 \end{document}

### 2017-05-24 Const_design.tex
Added new subsection 7.4 - Comparison vs 3-step. Recycled results from DIWINE demo

@@
 \usepackage{setspace}
+
+\graphicspath{{fig/}}
 
@@
 
+\subsection{Three-Step Reference Scenario}
+For a more relevant comparison of the proposed method, we consider two conventional \emph{3-step}
+communication scenarios.
+
+The first scenario is equivalent to a conventional routing, where the sources subsequently transmit
+their data packet towards the relay. Relay then sends a complete source information (no NC coding is
+applied) and thus the HSI channels are completely ignored.
+
+In the second scenario both sources again transmit their information one by one, but the relay is
+allowed to combine the received (fully decoded) data packets into the network coded packet
+$f(d_{A},d_{B})=d_{A}\oplus d_{B}$ and HSI channels are necessary to retrieve the desired
+information at both sources.
+
+To provide a fair comparison, in both reference scenarios we assume that the sources transmit at
+double power, as they transmit time is essentially halved when compared with the 2-step scenarios.
+
+\begin{figure}
+\begin{centering}
+%\includegraphics[width=0.75\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_referenceB}
+\includegraphics[width=0.75\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_referenceB}
+%\input{fig/2-SRN-sc_principle_BC-TWT_referenceB.eps_tex}
+\par\end{centering}
+
+\centering{}\caption{Three-step reference scenario with conventional network coding.\label{fig:CTUpp_ref3stepNC}}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.75\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_referenceB1}
+\par\end{centering}
+
+\centering{}\caption{Three-step reference scenario with conventional routing.\label{fig:CTUpp_ref3stepRouting}}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.75\columnwidth]{fig/scheme_a}
+\par\end{centering}
+\centering{}\caption{Performance comparison .\label{fig:CTUpp_comparison-schemaa}}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.75\columnwidth]{fig/scheme_b}
+\par\end{centering}
+\centering{}\caption{Performance comparison .\label{fig:CTUpp_comparison-schemab}}
+\end{figure}
+
 \section{Conclusions and Future Work\label{sec:CTUpp_DiscussionConclusions-etc}}

### 2017-05-24 results/process_script.py

@@ -1,0 +1,13 @@
+import pandas as pd
+
+#l = ['scheme_b_HW_A1', 'scheme_b_HW_A', 'scheme_b_NS_A', 'scheme_b_TL_A', 'scheme_b_HW_B','scheme_b_NS_B']
+l = ['scheme_a_HW_A1', 'scheme_a_HW_A', 'scheme_a_NS_A', 'scheme_a_TL_A','scheme_a_HW_B','scheme_a_NS_B', 'scheme_a_NS_B1', 'scheme_a_TL_B', 'scheme_a_TL_B1', 'scheme_a_HW_B1']
+
+#writer = ExcelWriter('scheme_b.xlsx')
+writer = pd.ExcelWriter('scheme_a.xlsx')
+for i in l:
+  df = pd.read_csv(i,header=1,sep=',') 
+  df.to_excel(writer,i)
+
+writer.save()
+

### 2017-05-25 Const_design.tex
Redrawn Figures in 3-step comparison and added some comments.

@@
 and the relay output mapper $\mathcal{A}^{R}$ will be defined as
-a conventional ($2^{N_{b}+2N_{s}}$$)$-QAM constellation. All performance
+a conventional $(2^{N_{b}+2N_{s}})$-QAM constellation. All performance
 metrics in the symmetric WBN are evaluated as a function of the actual
@@
 \caption{Throughput enhancement $\Delta T_{C}=T_{C}^{\mathrm{max}}-T_{\mathrm{LB}}$
-{[}bits/channel use{]} of the coded over uncoded WBN system for $\gamma_{{\rm {BC}}}=7.5\,\mathrm{dB}$
+[bits/channel use] of the coded over uncoded WBN system for $\gamma_{{\rm {BC}}}=7.5\,\mathrm{dB}$
 and $\gamma_{{\rm {BC}}}=15\,\mathrm{dB}$. Note that $0.75\leq\Delta T_{C}\leq2$
@@
 
-\subsection{Robustness Analysis}
+\subsection{Robustness Analysis}\label{sub:Robustness_Analysis}
 
@@
 
+\begin{figure*}
+\centering{\includegraphics[width=1\textwidth]{fig/Robust_20}
+\includegraphics[width=1\textwidth]{fig/Robust_21}}
+\caption{Robustness analysis for two fixed $(N_{b},N_{s},r_{b},r_{s})$ scenarios.
+\label{fig:CTUpp_Robustenss_analysis}}
+\end{figure*}
+
 \subsection{Three-Step Reference Scenario}
-For a more relevant comparison of the proposed method, we consider two conventional \emph{3-step}
+For a more advanced comparison of the proposed method, we consider two conventional \emph{3-step}
 communication scenarios.
@@
 their data packet towards the relay. Relay then sends a complete source information (no NC coding is
-applied) and thus the HSI channels are completely ignored.
+applied) and thus the HSI channels are completely ignored (see Figure \ref{fig:CTUpp_ref3stepRouting}).
 
@@
 $f(d_{A},d_{B})=d_{A}\oplus d_{B}$ and HSI channels are necessary to retrieve the desired
-information at both sources.
+information at both sources (see Figure \ref{fig:CTUpp_ref3stepNC}).
 
@@
 
+We compared throughput of the proposed adaptive constellation design from Section
+\ref{sub:Maximal-Throughput-of} on the USRP devices with optimized tuple ($r_b, r_s, N_b, N_s$) for
+each measured point (HW-pre-rotation on) with the reference scenarios in Figures \ref{fig:CTUpp_comparison-schemaa} and
+\ref{fig:CTUpp_comparison-schemab}. We also considered the proposed method with
+pre-rotation turned off as in Section \ref{sub:Robustness_Analysis} for comparison. Finally, we
+added two theoretical limits for the 3-step scenarios, where ideal Gaussian alphabets are assumed.
+
 \begin{figure}
@@
 \par\end{centering}
-\centering{}\caption{Performance comparison .\label{fig:CTUpp_comparison-schemaa}}
+\centering{}\caption{Performance comparison for the setup
+$\gamma_{\mathrm{BC}}\approx\gamma_{\mathrm{MAC}}$ and
+$\gamma_{\mathrm{HSI}}\approx\gamma_{\mathrm{MAC}}$+3dB
+.\label{fig:CTUpp_comparison-schemaa}}
 \end{figure}
@@
 \par\end{centering}
-\centering{}\caption{Performance comparison .\label{fig:CTUpp_comparison-schemab}}
+\centering{}\caption{Performance comparison for the setup
+$\gamma_{\mathrm{BC}}\approx\gamma_{\mathrm{MAC}}$+5dB and
+$\gamma_{\mathrm{HSI}}\approx\gamma_{\mathrm{MAC}}$-1dB
+.\label{fig:CTUpp_comparison-schemab}}
 \end{figure}
+
+One can observe that
 
@@
 require some modifications of the adaptive system design.
-\begin{figure*}
-\centering{\includegraphics[width=1\textwidth]{fig/Robust_20}
-\includegraphics[width=1\textwidth]{fig/Robust_21}}
-\caption{Robustness analysis for two fixed $(N_{b},N_{s},r_{b},r_{s})$ scenarios.
-\label{fig:CTUpp_Robustenss_analysis}}
-\end{figure*}
 

### 2017-05-26 Const_design.tex
Completed section 7.4 and added relevant point to intro

@@
 conditions induce some deviation from the assumed system model.
+\item We compare the proposed design with state of the art reference scherios to highlight its
+superior performance.
 \end{enumerate}
@@
 
-\subsection{Analysis of Transmission Rates}
+\subsection{Analysis of Transmission Rates}\label{Sec:Transmission_Rates}
 
@@
 
-\subsection{Three-Step Reference Scenario}
+\subsection{Benchmarking with the State of the Art Three-Step Scenarios}
 For a more advanced comparison of the proposed method, we consider two conventional \emph{3-step}
@@
 
-The first scenario is equivalent to a conventional routing, where the sources subsequently transmit
+\subsubsection{Reference Three-Step Scenarios}\label{Sec:Reference-3step-models}
+The first scenario both sources again transmit their information one by one, but the relay is
+allowed to combine the received (fully decoded) data packets into the network coded packet
+$f(d_{A},d_{B})=d_{A}\oplus d_{B}$ and HSI channels are necessary to retrieve the desired
+information at both sources, that is the traditional network coding approach (see Figure
+\ref{fig:CTUpp_ref3stepNC}).
+
+In the scenario is equivalent to a conventional routing, where the sources subsequently transmit
 their data packet towards the relay. Relay then sends a complete source information (no NC coding is
@@
 
-In the second scenario both sources again transmit their information one by one, but the relay is
-allowed to combine the received (fully decoded) data packets into the network coded packet
-$f(d_{A},d_{B})=d_{A}\oplus d_{B}$ and HSI channels are necessary to retrieve the desired
-information at both sources (see Figure \ref{fig:CTUpp_ref3stepNC}).
-
+\subsubsection{Implementation Details for Reference Scenarios}
 To provide a fair comparison, in both reference scenarios we assume that the sources transmit at
 double power, as they transmit time is essentially halved when compared with the 2-step scenarios.
+We assume QAM($N$) constellation and adaptively look for $N, r$ maximizing the throughput as in the
+proposed Section \ref{sub:Maximal-Throughput-of}.
+
+\subsubsection{Maximum Transmission Rates for the Three-Step Reference Scenarios}
+The theoretical limits for the considered 3-step scenarios can be easily derived (see
+\cite{Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}) as
+\begin{eqnarray}
+  r^{\mathrm{3step}}_{\mathrm{route}} &\le& \min\left\{\frac{2\mathrm{Ca}(\gamma_{MAC})}{2},\frac{2\mathrm{Ca}(\gamma_{BC})}{2}\right\}\label{eq:cap3strout}\\
+  r^{\mathrm{3step}}_{\mathrm{NC}} &\le& \min\left\{\frac{2\mathrm{Ca}(2\gamma_{MAC})}{2},\frac{2\mathrm{Ca}(\gamma_{HSI})}{2}, \mathrm{Ca}(\gamma_{BC})\right\},\label{eq:cap3stNC}
+\end{eqnarray}
+where $\mathrm{CA}(\gamma)=\log_2(1+\gamma)$ denotes conventional point to point channel capacity for Gaussian
+channel \cite{Cover-Thomas_ElemInfTheory}.
+
+These bounds serve as an initial step for the tuple (rate, alphabet cardinality) optimization as in
+Section \ref{Sec:Transmission_Rates} but also as an ultimate theoretical bound of the individual
+reference strategies.
 
@@
 
-We compared throughput of the proposed adaptive constellation design from Section
-\ref{sub:Maximal-Throughput-of} on the USRP devices with optimized tuple ($r_b, r_s, N_b, N_s$) for
-each measured point (HW-pre-rotation on) with the reference scenarios in Figures \ref{fig:CTUpp_comparison-schemaa} and
-\ref{fig:CTUpp_comparison-schemab}. We also considered the proposed method with
-pre-rotation turned off as in Section \ref{sub:Robustness_Analysis} for comparison. Finally, we
-added two theoretical limits for the 3-step scenarios, where ideal Gaussian alphabets are assumed.
+\subsubsection{Numerical Results}
+Within this experiment, we evaluated on our USRP platform the following situations:
+\begin{itemize}
+  \item The proposed adaptive constellation design from Section \ref{sub:Maximal-Throughput-of} 
+  with optimized tuple ($r_b, r_s, N_b, N_s$) for each measured point
+  (HW-pre-rotation on).
+  \item The proposed adaptive constellation design with violated assumptions (pre-rotation off)
+  \item Both 3-step reference scenarios introduced in Section \ref{Sec:Reference-3step-models}.
+  \item Fundamental theoretical limits for the conventional reference 3-step scenarios.
+\end{itemize}
+
+We considered two setups:
+\begin{itemize}
+  \item Strong HSI and equal MA and BC. This scenario is suited for standard wireless network
+  coding, because it can efficiently utilize the strong HSI channel. See Figure
+  \ref{fig:CTUpp_comparison-schemaa} for the corresponding result. As one can see, the proposed
+  framework significantly outperforms both reference 3-step scenarios as well the corresponding
+  theoretical limits even if the pre-rotation is off! The bottleneck for the 3-step routing is BC
+  channel, because it needs to pass twice amount of data from relay to destinations compared to
+  all other schemes. The 3-step NC approach does not suffer from this and therefore its performance
+  is a bit better, nevertheless we pay for orthogonality in the MA stage. The proposed performance
+  of the proposed framework is superior to both reference models.
+  \item Strong BC channel refers (among others) to a case with high relay power. The result is shown
+  in Figure \ref{fig:CTUpp_comparison-schemab}. The 3-step routing works much better compared to the previous
+  case, because of the strong BC channel. The conventional 3-step network coding suffers from weak
+  HSI channel. The proposed design again significantly outperforms both reference 3-step scenarios.
+  We should stress, that the performance gain is also caused by a \emph{partial usage} of the weak
+  HSI channel.
+\end{itemize}
 
@@
 \end{figure}
-
-One can observe that
 

### 2017-05-29 Const_design.tex
Finished section 7.4 (to internal review)

@@
 \subsubsection{Reference Three-Step Scenarios}\label{Sec:Reference-3step-models}
-The first scenario both sources again transmit their information one by one, but the relay is
+In the first scenario both sources transmit their information one by one, but the relay is
 allowed to combine the received (fully decoded) data packets into the network coded packet
@@
 
-In the scenario is equivalent to a conventional routing, where the sources subsequently transmit
+The second scenario is equivalent to a conventional routing, where the sources subsequently transmit
 their data packet towards the relay. Relay then sends a complete source information (no NC coding is
@@
 \subsubsection{Numerical Results}
-Within this experiment, we evaluated on our USRP platform the following situations:
+Within this experiment, we evaluated the following situations on our \emph{USRP platform}:
 \begin{itemize}
   \item The proposed adaptive constellation design from Section \ref{sub:Maximal-Throughput-of} 
-  with optimized tuple ($r_b, r_s, N_b, N_s$) for each measured point
+  with based on the optimized tuple ($r_b, r_s, N_b, N_s$) for each measured point
   (HW-pre-rotation on).
-  \item The proposed adaptive constellation design with violated assumptions (pre-rotation off)
+  \item The proposed adaptive constellation design with violated assumptions (pre-rotation off).
   \item Both 3-step reference scenarios introduced in Section \ref{Sec:Reference-3step-models}.
@@
 \end{itemize}
+In all measured cases, we manually selected the tuple maximizing the throughput. Our starting
+point was the theoretical analysis, but this analysis does not take into account the imperfect
+channel code and available discrete channel code rates (0.4, 0.5, \dots, 0.9). We also considered
+$N_b
+\le 2$, $N_s \le 1$ for simplicity\footnote{The higher order strategies like $(N_b=4, N_s=0)$
+performed similarly as considered $(N_b=2, N_s=1)$ in our simulations. Note that much stronger
+solution based
+on the modulo-sum channel coding and wireless network coding function is available
+\cite{Prochazka-2016}, nevertheless implementation of the 
+non-binary channel code suitable for the USRP is challenging.}.
 
@@
   all other schemes. The 3-step NC approach does not suffer from this and therefore its performance
-  is a bit better, nevertheless we pay for orthogonality in the MA stage. The proposed performance
+  is a bit better, nevertheless we pay for orthogonality in the MA stage. The performance
   of the proposed framework is superior to both reference models.
@@
 
+The saturation of the reference 3-step strategies for high SNRs is a consequence of weaker
+performance of the underlaying channel code, where the rate of the code is adjusted by means of
+puncturing technique.
+
 \begin{figure}
@@
 $\gamma_{\mathrm{BC}}\approx\gamma_{\mathrm{MAC}}$ and
-$\gamma_{\mathrm{HSI}}\approx\gamma_{\mathrm{MAC}}$+3dB
-.\label{fig:CTUpp_comparison-schemaa}}
+$\gamma_{\mathrm{HSI}}\approx\gamma_{\mathrm{MAC}}$+3dB. The numbers in boxes correspond with a
+particular values (first row:$(N_b, r_b)$, second row:$(N_s, r_s)$) 
+achieving a given maximal throughput. 
+\label{fig:CTUpp_comparison-schemaa}}
 \end{figure}
@@
 $\gamma_{\mathrm{BC}}\approx\gamma_{\mathrm{MAC}}$+5dB and
-$\gamma_{\mathrm{HSI}}\approx\gamma_{\mathrm{MAC}}$-1dB
-.\label{fig:CTUpp_comparison-schemab}}
+$\gamma_{\mathrm{HSI}}\approx\gamma_{\mathrm{MAC}}$-1dB.
+The numbers in boxes correspond with a
+particular values (first row:$(N_b, r_b)$, second row:$(N_s, r_s)$)
+achieving a given maximal throughput.
+\label{fig:CTUpp_comparison-schemab}}
 \end{figure}

### 2017-05-30 response_letter/response_letter.tex
Added new subsection 7.4 - Comparison vs 3-step. Recycled results from DIWINE demo
Minor change in the manuscript (enlarging fonts for figure 13) + some work on response letter

@@
 \begin{document}
+\title{Response Letter for EURASIP Journal on Wireless Communications and Networking 
+JWCN-D-17-00004 \vskip 1ex
+Design of Adaptive Constellations and Error Protection Coding for
+Wireless Network Coding in 5-node Butterfly Networks}
+\author{Pavel Prochazka, Tomas Uricar, David Halls and Jan Sykora}
+\date{\today}
+\maketitle
+\newpage
+
+We would like to thank all the reviewers for their valuable comments and suggestions. We first reply
+to the most common and important questions and then we answer the individual questions and comments
+individually.
 
@@
 \begin{itemize}
-  \item CQ1: \emph{Lacking novelty compared to \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}}
-  \item A1: Quoting the part of the cover letter for IEEE transaction submission:\newline
-  \sc{Compared with the conference version, the major contributions and differences of this submitted manuscript are summarized as follows:
+  \item CQ1: \emph{Lacking novelty compared to \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}.}
+  \item A1: Compared with the conference version \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}, the major contributions and differences of this submitted manuscript are summarized as follows:
   \begin{enumerate} 
@@
   \item We perform a simple robustness analysis, demonstrating that the proposed modulation and coding strategy is viable even in the case when the real world condition induce some deviations from the mathematical system model assumed in the paper.
+  \item We conducted a comparison with the state of the art reference scenarios (traditional network
+  coding and routing) for the proposed channel coded adaptive constellation design.
   \end{enumerate}
-  }
 \end{itemize}
@@
 \begin{itemize}
-  \item CQ2: \emph{Better reference scenario?}
-  \item A2: Related with two-step vs 3(4) step comparison requiring additional derivations (TODO)
+  \item CQ2: \emph{Better reference scenario.}
+  \item A2: We definitely agree that the zero throughput uncoded QPSK reference scenario is not a very good
+  to demonstrate the performance gain of the proposed constellation design. 
+  Although, the 2-step scenario does not offer other state of the art solution, we
+  decided to consider a comparison with traditional network coding and routing strategies. These
+  strategies require 3 steps and therefore some attention is required to provide a fair comparison
+  with the proposed 2-step framework. We added a completely new section 7.4 into the manuscript
+  dedicated to this comparison  with the conventional techniques.
+
+  Within this new section, we shown that
+  the HW implementation of the proposed adaptive constellation design outperforms the reference
+  scenarios even with the relaxed assumption (pre-rotation off). In addition we shown that the
+  performance of the proposed framework is even above the corresponding reference theoretical limits.
 \end{itemize}
@@
 \begin{itemize}
-  \item CQ2: \emph{Typos and Formating Issues?}
-  \item A3: We have proofreaded the manuscript for typos. Regarding the formating issues, we prefer
-  to clean final version of the manuscript. (TODO)
+  \item CQ3: \emph{Typos and Formatting Issues}
+  \item A3: The manuscript was carefully proofread by native speaker for typos. Regarding the
+  formatting issues, we searched and corrected the issues we found. Nevertheless, we should stress
+  that the manuscript will be transformed to the EURASIP template prior publishing and there will
+  be time for final tuning of these issues.
+\end{itemize}
+
+\begin{itemize}
+  \item CQ4: \emph{Generalization of the proposed Adaptive Constellation Design}
+  \item A4:
 \end{itemize}
@@
   possible to generalize to other similar networks where linear codes yield a good performance.}
-  \item A2-1: We should stress that the proposed constellation design covers both
+  \item A: See A4.  We should stress that the proposed constellation design covers both
   wireless network coding and processing the signal from multiple stages. Join generalization of
@@
 \section{Major Changes Summary}
+\begin{itemize}
+  \item New section 7.4 containing a more advanced comparison of the proposed framework with the
+  state of the art strategies.
+  \item Redrawn Figures (see changes in Figures \ref{Fig:Throughput_comparison} and
+  \ref{Fig:AchievedRates}).
+\end{itemize}
 \begin{figure}
@@
 
+\begin{figure}
+    %\begin{subfigure}[t]{0.5\textwidth}
+    \includegraphics[width=0.45\linewidth]{fig/old_Rate_Regions_XOR_map_BC10_MAC12_HSI8.eps}
+    \includegraphics[width=0.45\linewidth]{../fig/Rate_Regions_XOR_map_BC10_MAC12_HSI8.eps}\\
+    \includegraphics[width=0.45\linewidth]{fig/old_Rate_Regions_XOR_map_BC5_MAC5_HSI0.eps}
+    \includegraphics[width=0.45\linewidth]{../fig/Rate_Regions_XOR_map_BC5_MAC5_HSI0.eps}\\
+	\caption{Enlarged fonts -- Figure 13 in the manuscript (old versions left, new versions right).}
+	\label{Fig:AchievedRates}
+	%\caption{Old uncoded throughput for $\gamma_{\mathrm{MAC}}=16$,$\gamma_{\mathrm{BC}}=20$.}
+    %\end{subfigure} 
+    %\begin{subfigure}[t]{0.45\textwidth}
+    %\caption{New the uncoded throughput for $\gamma_{\mathrm{MAC}}=16$,$\gamma_{\mathrm{BC}}=20$.}
+    %\end{subfigure} 
+\end{figure}
 \bibliographystyle{plain}
-\bibliography{Const_design}
+\bibliography{bib/Const_design}
 \end{document}

### 2017-05-30 notebooks/capacity_eval.py

@@ -1,0 +1,623 @@
+import numpy as np
+import time
+import subprocess
+import matplotlib.pyplot as plt
+from joblib import Parallel, delayed
+import os, sys, inspect
+import mpmath as mp
+from compare_QPSK import const_design_XOR, QAM, const_superposed
+import pickle
+import matplotlib.pyplot as plt
+from scipy.optimize import linprog
+#import _capacity_eval_lib
+
+def eval_sigma2w(SNR):
+  gammaAdB = float(SNR)
+  gammaA= 10.0**(gammaAdB/10)
+  return 1.0 / (gammaA)
+
+def eval_sigma2w_gen(SNR, const):
+  M = len(const) # Cardinality
+  Es = float(np.sum(np.abs(const)**2)) / M # Energy per symbol (complex envelope)
+  Eb = float(Es)/np.log2(M) # Energi per bit (complex envelope)
+  gammaAdB = SNR
+  gammaA= 10.0**(gammaAdB/10)
+  return Eb / (gammaA)
+
+def cap_eval_Gauss(SNR):
+  sigma2w = eval_sigma2w(SNR)
+  return np.log2(1 + 1./sigma2w)
+
+def cap_eval_ef(SNR, const, M):
+  sigma2w = eval_sigma2w(SNR)
+  Md = len(const)
+  px = np.zeros(Md * M, dtype=float)
+  pxd = np.zeros(Md * M, dtype=float)
+  d = np.zeros(Md * M, dtype=complex)
+  for i in range (0, Md):
+    d[(i * M):((i + 1) * M)] = np.repeat(const[i], M)
+  w = np.sqrt(sigma2w/2) * (np.random.normal(size=M * Md) + 1j * np.random.normal(size = M * Md))
+  x = d + w
+  ex = np.zeros([Md, Md * M], dtype=float)
+  for i in range (0, Md):
+    ex[i,:] = 1.0 / (np.pi * sigma2w) * np.exp(-np.abs(x - const[i])**2/(sigma2w));
+  px = ex.sum(axis=0) / Md
+  for i in range (0, Md):
+    pxd[(i * M):((i + 1) * M)] = ex[i, (i * M):((i + 1) * M)]
+  Hx = - 1.0/M/Md * np.sum(np.log2(px)); 
[…]

### 2017-05-30 response_letter/response_letter.tex
Few new lines in response letter

@@
   the HW implementation of the proposed adaptive constellation design outperforms the reference
-  scenarios even with the relaxed assumption (pre-rotation off). In addition we shown that the
-  performance of the proposed framework is even above the corresponding reference theoretical limits.
+  scenarios even with the relaxed assumption (pre-rotation off). The good performance of the proposed
+  design without pre-rotation is very important, because the
+  pre-rotation stands for an implementation challenge requiring the feedback channel. Finally we shown that the
+  performance of the proposed framework is even above the corresponding 3-step reference theoretical limits.
 \end{itemize}
@@
   \item CQ4: \emph{Generalization of the proposed Adaptive Constellation Design}
-  \item A4:
+  \item A4: The proposed constellation design is indeed suited for the butterfly network. Regarding
+  the generalization, we can take the idea beyond the constellation design also for other
+  topologies. For instance, the design of the basic part only is relevant for the two-way relay
+  channel (actually)
 \end{itemize}
@@
   setting of algebraic network coding for comparison.}
-  \item A: see A2
-\end{itemize}
-
-\begin{itemize}
-  \item Q: \emph{It might be useful to the reader to add a figure for the butterfly network in the
-  setting of algebraic network coding for comparison.}
-  \item A: see A2
+  \item A: see A2 and the new section 7.4 in the manuscript
 \end{itemize}
@@
 random linear network coding).}
-  \item A: see A2
-\end{itemize}
-\begin{itemize}
   \item Q: \emph{If it cannot be easily generalized, it could be helpful to explain what are the
@@
 \begin{itemize}
-  \item Q: \emph{It might be useful to the reader to add a figure for the butterfly network in the
-	  setting of algebraic network coding for comparison.}
-  \item A: 
-\end{itemize}
-
-\begin{itemize}
   \item Q: \emph{Might be helpful if mention beforehand that the nomenclature is given at the end of the paper (For
 	  example, HW is throughout the paper and its definition is only given at the end of the paper)}.
-  \item A: The nomenclature is placed according to the EURASIP-author's guidelines.
+  \item A: The nomenclature is placed according to the EURASIP-author's guidelines. The HW
+  abbreviation was overlooked - it is now defined also in its first appearance within the text.
 \end{itemize}
@@
   difference. }
-  \item A: The channel quality index is 3-dimensional (MAC, BC and HSI) in our case and we
-    have it basically presented in the manuscript in form some cuts shown in figures. Its comparison
-    with P2P case can be conducted in multiple ways (e.g. one can consider 4-step conventional P2P),
-    but we solve again the problem two-step versus 4-step stage (see A2).
+  \item A: The channel quality index is 3-dimensional (MAC, BC and HSI) in the current state. Its
+  evaluation can be easily done according to the theoretical analysis. Nevertheless we observed that 
+  Although this table would undoubtedly much simplify the implementation, based on our experience,
+  we 
 \end{itemize}

### 2017-05-30 response_letter/response_letter.tex
Almost completed response letter

@@
 \usepackage{bm}
+\usepackage{url}
 \usepackage{amsmath}
@@
 
-We would like to thank all the reviewers for their valuable comments and suggestions. We first reply
+First of all, we would like to thank all the reviewers for their valuable comments and suggestions
+that help to improve our manuscript. We first reply
 to the most common and important questions and then we answer the individual questions and comments
@@
   \item CQ1: \emph{Lacking novelty compared to \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}.}
-  \item A1: Compared with the conference version \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}, the major contributions and differences of this submitted manuscript are summarized as follows:
+  \item A1: Compared with the conference paper \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}, the major contributions and differences of this submitted manuscript are summarized as follows:
   \begin{enumerate} 
@@
   design without pre-rotation is very important, because the
-  pre-rotation stands for an implementation challenge requiring the feedback channel. Finally we shown that the
+  pre-rotation stands for a serious implementation challenge requiring the feedback channel. Finally we shown that the
   performance of the proposed framework is even above the corresponding 3-step reference theoretical limits.
@@
 \begin{itemize}
-  \item CQ4: \emph{Generalization of the proposed Adaptive Constellation Design}
-  \item A4: The proposed constellation design is indeed suited for the butterfly network. Regarding
-  the generalization, we can take the idea beyond the constellation design also for other
-  topologies. For instance, the design of the basic part only is relevant for the two-way relay
-  channel (actually)
+  \item CQ4: \emph{Motivation beyond the proposed Adaptive Constellation Design and its
+  Generalization}
+  \item A4: We answer this question in two levels. We split the problem to 1) the wireless
+  aware network coding, that is to determine the information flow within the network
+  \cite{Uricar-Hynek-Prochazka-Sykora_2013} and 2) the particular constellations 
+  design suited for a given information stream. Note that the motivation can be found also in
+  \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}.
+
+  The network information flow within the butterfly network can be seen as a combination of the
+  cases, when a) all information is passed through the relay b) maximal information is passed
+  through the site links as it is explained in \cite{Prochazka_Tutorial_WNC}. Finding a proper
+  network information flow within a general wireless network can be a nutshell. Intuitively, the
+  wireless network paradigm should be exploited as much as possible due to its higher spectral
+  efficiency. To the best of our knowledge, no such approach is available for a general network
+  in the current state of the art. The random network coding does not take advantage to be 
+  "wireless aware" due to its randomness. There remains a white space for research to bring light
+  into a proper network information flow design within a general network.
+
+  The second part of the design assumes a given network information flow and the goal is to find
+  the best possible constellation design across the nodes within the network for the given flow.
+  Within this design, we consider two building blocks  for multiple access channel, that is: 
+  i) orthogonal constellation design enabling resulting to non-overlapping superimposed
+  constellation in the receiving node enabling joint (full) decoding and ii) hierarchical
+  constellation design allowing some overlaps in the received constellation, such that only a
+  network function of the data can be recovered (not both individual data streams). Finally, one
+  needs to properly combine the aforementioned building blocks.
+
+  In case of the orthogonal design, we chosen ASK source constellations shifted by $\pi/2$ to 
+  form the QAM constellation in the received node. The hierarchical design depends on a particular
+  network function (exclusive OR in our case). Prior explaining the composition of the 
+  hierarchical constellation, we clarify our goal, that is the received constellation with maximal
+  minimum distance between the \emph{network coded data}. To provide a simple example, consider
+  two BPSK constellations $s\in\{-1,1\}$.
+
+  Within the butterfly network, the orthogonal stream is called \emph{superposed} stream and the
+  hierarchical as \emph{basic} stream. Since the basic stream is needed in destinations, it is
+  placed at higher power level compared to the superposed stream. Please see Figures 3,4 in the
+  manuscript for demonstration.
+
+  Regarding to the generalization of the principle to general network, one can of cause consider
+  with advantage the proposed building blocks or even try to generalize them for more than two
+  sources. A design of some useful rules for the proposed building block utilization in general 
+  network stands for a white space for further research. One should also keep in mind that the
+  severity of the synchronization and pre-rotation issues would dramatically grow with the network
+  size.
+
 \end{itemize}
@@
   possible to generalize to other similar networks where linear codes yield a good performance.}
-  \item A: See A4.  We should stress that the proposed constellation design covers both
-  wireless network coding and processing the signal from multiple stages. Join generalization of
-  both techniques in the way we did would be extremely challenging, because of time 
-  synchronization, pre-rotation, etc. Also note that our approach is basically a 
-  practical instance of a well known
-  theoretical principle with application of WNC to approximately equal power levels and
-  interference cancellation on significantly different power levels. So that its generalization in
-  theoretical level is already known. 
+  \item A: See A4.  
 \end{itemize}
@@
   constellation and explain why the challenges to apply to other linear networks.}
-  \item A: The intuition beyond the design could be partly found in \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}.  
-  Particularly, the idea is to consider bit streams that are divided among individual power levels.
-  We need to define 1) the scale of individual levels, 2) the constellation element for all levels.
-  Obviously, this design would differ for basic and superposed streams:
-  \begin{enumerate}
-    \item In case of superposed stream, we need to have both source streams decodable and thus we
-    need some kind of orthogonality. This orthogonality is achieved by considering real and
-    imaginary axis of the constellation space. 
-    \item
-  \end{enumerate}
-  Our solution considers the simplest possible constellation element (BPSK at given level)
+  \item A: See A4
 \end{itemize}
@@
 random linear network coding).}
+  \item A: see A4 
   \item Q: \emph{If it cannot be easily generalized, it could be helpful to explain what are the
   difficulties in applying it to other coding schemes.}
-  \item A: 
+  \item A: see A4 
 \end{itemize}
@@
     WBN.}
-  \item A: See A2. Considering the two time slot communication, there is indeed no state of the art solution
-      for joint decoding, that is the constellation design in sources such that the relay would reliably
-      jointly resolve data\footnote{We assume uncoded data in this context only.} from both sources. 
-      We thus decided to claim the performance of the proposed $N_b=0$, $N_s=2$ compared to the zero
-        throughput QPSK as the throughput gain. Nevertheless, the reviewer has point that it is unfair to claim the
-        performance of the proposed $N_b=1$, $N_s=1$ constellation as throughput gain compared to
-        zero-throughput QPSK, because a conventional wireless network coding with BPSK would give a
-        nonzero throughput in this case. We therefore drop this claim from our Figures 6-9 in
-        manuscript (check Figure \ref{Fig:Throughput_comparison}).
+  \item A: See A2 for the coded case. Considering the two time slot communication, there is 
+  indeed no state of the art solution for joint decoding, that is the constellation design in 
+  sources such that the relay would reliably jointly resolve data\footnote{We assume uncoded data
+  in this context only.} from both sources. We thus decided to claim the performance of the 
+  proposed $N_b=0$, $N_s=2$ compared to the zero throughput QPSK as the throughput gain.
 
+  Nevertheless, the reviewer has point that it is unfair to claim the performance of the proposed
+  $N_b=1$, $N_s=1$ constellation as throughput gain compared to the zero-throughput QPSK, because
+  the proposed constellation design uses the site link and it should be rather compared with some
+  reference that is able to use the site link as well. For this purpose, the conventional wireless
+  network coding with BPSK constellation with nonzero throughput can be considered for instance,
+  however to keep the figure readable, we decided not to add another curve into the plot, because 
+  the BPSK performs similarly as  $(N_b=2, N_s=0)$ strategy already shown in the figures.
+  Therefore the performance gain statement between $N_b=1$, $N_s=1$ and the
+  reference QPSK is omitted in Figures 6-9 in the revised manuscript. Check Figure 
+  \ref{Fig:Throughput_comparison}) in this response letter to see the change in the figure. 
 \end{itemize}
@@
   difference. }
-  \item A: The channel quality index is 3-dimensional (MAC, BC and HSI) in the current state. Its
-  evaluation can be easily done according to the theoretical analysis. Nevertheless we observed that 
-  Although this table would undoubtedly much simplify the implementation, based on our experience,
-  we 
+  \item A: The channel quality index is 3-dimensional (MAC, BC and HSI) within our model. Although
+  its evaluation can be easily done according to the theoretical analysis, its practical impact is
+  questionable, because of more degrees of freedom that comes into
+  the consideration in real scenario, like a concrete code, violation of the symmetry 
+  assumption, strength of the
+  direct link, etc. Within our experiment, we manually found some "optimal" table values for a 
+  small collection of  SNR tuples in the new section 7.4 (Figures 20, 21), but we would be 
+  careful to fix the parameters $(N_b, N_s, r_b r_s)$ purely according to the SNR triplet in 
+  other experiment.
 \end{itemize}
@@
 If some initial results on the fading channel case can be added into the paper, it would be better.}
-  \item A: TODO (possible to play with in the tutorial)
+  \item A: We agree that the investigation of the behavior in the fading channels is an important
+  step. We have already some initial results available, because without the 
+  pre-rotation, we face efficiently to the (phase only) fading channel. 
+  A more detailed analysis of the proposed constellation design fading channels will be
+  investigated in further work.
 \end{itemize}
@@
 
-\section{Major Changes Summary}
-\begin{itemize}
-  \item New section 7.4 containing a more advanced comparison of the proposed framework with the
-  state of the art strategies.
-  \item Redrawn Figures (see changes in Figures \ref{Fig:Throughput_comparison} and
-  \ref{Fig:AchievedRates}).
-\end{itemize}
 \begin{figure}

### 2017-05-31 response_letter/response_letter.tex
prerelease of the response letter

@@
 
-  In case of the orthogonal design, we chosen ASK source constellations shifted by $\pi/2$ to 
-  form the QAM constellation in the received node. The hierarchical design depends on a particular
-  network function (exclusive OR in our case). Prior explaining the composition of the 
-  hierarchical constellation, we clarify our goal, that is the received constellation with maximal
-  minimum distance between the \emph{network coded data}. To provide a simple example, consider
-  two BPSK constellations $s\in\{-1,1\}$.
+  In case of the orthogonal design, we chosen ASK source constellations mutually shifted by $\pi/2$
+  to form the QAM constellation in the received node. This assumes exactly two transmitting nodes.
+  For generalization to more sources, some way to preserve join decodability must be found, for
+  instance additional resources.  
+  The hierarchical design depends on a particular
+  network function (exclusive OR in our case). The goal is the received constellation with maximal
+  minimum distance between the \emph{network coded data}, where overlaps within the network function
+  are allowed. Actually these overlaps enable to improve the minimal distance compared to the
+  orthogonal design. Since both ASK and the proposed hierarchical constellation can be written as
+  composition of properly scaled BPSK constellations, the constellations are fully determined by 
+  scaling level for individual bit streams.
 
@@
   hierarchical as \emph{basic} stream. Since the basic stream is needed in destinations, it is
-  placed at higher power level compared to the superposed stream. Please see Figures 3,4 in the
-  manuscript for demonstration.
+  placed at higher power level compared to the superposed stream. Please find Figures 3,4 in the
+  manuscript for demonstration of this composition.
 
-  Regarding to the generalization of the principle to general network, one can of cause consider
+  Regarding to the generalization of the principle to a general network, one can of cause consider
   with advantage the proposed building blocks or even try to generalize them for more than two
   sources. A design of some useful rules for the proposed building block utilization in general 
-  network stands for a white space for further research. One should also keep in mind that the
-  severity of the synchronization and pre-rotation issues would dramatically grow with the network
-  size.
+  network stands for a white space for further research. However one should also keep in mind that 
+  severity of the real world issues as the synchronization and pre-rotation would dramatically grow
+  with the network size.
 

### 2017-05-31 response_letter/response_letter.tex
Corrected typos

@@
   \item We introduce additional performance analysis results for constellations in an uncoded system and an in-depth discussion of the observed results.
-  \item We extend the section dealing with the adaptive constellation design in an uncoded system and we supplement additional HW evaluation results for the adaptive system in the whole range of observed channel SNRs.
-Again a close agreement between between the analytic and measurement results is shown.
+  \item We extend the section dealing with the adaptive constellation design in an uncoded system
+  and we supplement additional HW evaluation results for the adaptive system in the whole range of
+  observed channel SNRs. Again, a close agreement between the analytic and measurement results is shown.
   \item We show how the channel coding can be integrated into the proposed constellation design, including the cut-set bound analysis of proper source transmission rates, which provides a hint for the setup of all channel encoders' rates in the system.
@@
     respect to the uncoded system.
-  \item We perform a simple robustness analysis, demonstrating that the proposed modulation and coding strategy is viable even in the case when the real world condition induce some deviations from the mathematical system model assumed in the paper.
+  \item We perform a simple robustness analysis, demonstrating that the proposed modulation and
+  coding strategy is viable even in the case when the real-world conditions induce some deviations from the mathematical system model assumed in the paper.
   \item We conducted a comparison with the state of the art reference scenarios (traditional network
@@
   \item CQ2: \emph{Better reference scenario.}
-  \item A2: We definitely agree that the zero throughput uncoded QPSK reference scenario is not a very good
-  to demonstrate the performance gain of the proposed constellation design. 
-  Although, the 2-step scenario does not offer other state of the art solution, we
+  \item A2: We definitely agree that the zero throughput uncoded QPSK reference scenario is not
+  ideal for the performance gain demonstration of the proposed constellation design. 
+  There are no equivalent 2-step state of the art strategies, so we
   decided to consider a comparison with traditional network coding and routing strategies. These
   strategies require 3 steps and therefore some attention is required to provide a fair comparison
-  with the proposed 2-step framework. We added a completely new section 7.4 into the manuscript
+  with the proposed 2-step framework. We added a completely new section, 7.4, into the manuscript
   dedicated to this comparison  with the conventional techniques.
@@
   formatting issues, we searched and corrected the issues we found. Nevertheless, we should stress
-  that the manuscript will be transformed to the EURASIP template prior publishing and there will
-  be time for final tuning of these issues.
+  that the manuscript will be transformed to the EURASIP template prior to publishing and there will
+  be time for fine tuning.
 \end{itemize}
@@
     WBN.}
-  \item A: See A2 for the coded case. Considering the two time slot communication, there is 
-  indeed no state of the art solution for joint decoding, that is the constellation design in 
-  sources such that the relay would reliably jointly resolve data\footnote{We assume uncoded data
+  \item A: See A2 for the coded case. Considering the two time slot communication schemes, there is 
+  indeed no state of the art solution for joint decoding, whereby the constellation design at the 
+  sources is such that the relay would reliably jointly resolve data\footnote{We assume uncoded data
   in this context only.} from both sources. We thus decided to claim the performance of the 
@@
 
-  Nevertheless, the reviewer has point that it is unfair to claim the performance of the proposed
+  Nevertheless, the reviewer has a point that it is unfair to claim the performance of the proposed
   $N_b=1$, $N_s=1$ constellation as throughput gain compared to the zero-throughput QPSK, because
@@
   questionable, because of more degrees of freedom that comes into
-  the consideration in real scenario, like a concrete code, violation of the symmetry 
+  the consideration in real scenario, like a particular channel code, violation of the idealistic symmetry 
   assumption, strength of the
@@
   \item A: We agree that the investigation of the behavior in the fading channels is an important
-  step. We have already some initial results available, because without the 
-  pre-rotation, we face efficiently to the (phase only) fading channel. 
-  A more detailed analysis of the proposed constellation design fading channels will be
-  investigated in further work.
+  step. We have already some initial results available, because we face efficiently to the fading
+  channel without the pre-rotation, where the amplitude is close (but not equal) to 1.   
+  A more detailed analysis of the proposed constellation design in fading channels is postponed for further work.
 \end{itemize}
@@
   \item A: We fully understand and agree that the robustness analysis deserves further deep
-      investigation. Nevertheless we provided some basic analysis including the hardware experiment
+      investigation. Nevertheless, we provided some basic analysis including the hardware experiment
         within our work (check Figure 17 in manuscript) giving quite promising results. A more detailed investigation is suited rather
@@
   coded throughput as a function of SNRs is much smoother (Figure 14) and therefore their difference
-  induces peeks and valleys
+  induces peaks and valleys
 \end{itemize}

### 2017-05-31 Const_design.tex
Few new lines in response letter
Corrected typos

@@
 \begin{abstract} % abstract
-In this paper we focus on the design of a reliable communication scheme
+In this paper, we focus on the design of a reliable communication scheme
 for generic 5-node Wireless Butterfly Networks (WBN). Since the WBN
@@
 channel, we follow the paradigm of \emph{Wireless Physical Layer Network
-Coding} and we show that the design of novel adaptive constellations\emph{
-} is desirable to exploit the promising performance of wireless network coding in WBN.
+Coding} and we show that the design of novel adaptive constellations
+ is desirable to exploit the promising performance of wireless network coding in WBN.
 We introduce a \emph{systematic constellation design} algorithm and
@@
 
-The invention of Wireless Network Coding\emph{ }(WNC) has indeed provided
+The invention of Wireless Network Coding\emph{ }(WNC) has provided
 a means for a significant enhancement in wireless system performance
@@
 on the constellations' properties and characteristics (see e.g. \cite{Uricar-Sykora_2011,Prochazka-Uricar-Halls-Sykora_2015-ICC}).
-Generally we can declare \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
+Generally, we can declare \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
 that any constellation suitable for the specific nature of WNC processing
@@
 
-In this paper we extend the communication scheme from \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
+In this paper, we extend the communication scheme from \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
 by appending appropriate \emph{error protection coding} to the system,
@@
 regions} for adaptive WBN relaying\emph{.}
-\item We validate the proposed design in a \emph{real-world HW setup}, including
+\item We validate the proposed design in a \emph{real-world hardware (HW) setup}, including
 the HW evaluation of adaptive system performance.
@@
 conditions induce some deviation from the assumed system model.
-\item We compare the proposed design with state of the art reference scherios to highlight its
+\item We compare the proposed design with state of the art reference scenarios to highlight its
 superior performance.
@@
 Section~\ref{sec:CTUpp_Performance-Analysis-Coded}, including a
-simple robustness analyzis. Concluding remarks are summarized in Section~\ref{sec:CTUpp_DiscussionConclusions-etc}.
+simple robustness analysis. Concluding remarks are presented in Section~\ref{sec:CTUpp_DiscussionConclusions-etc}.
 
@@
 are generally taken from the set of complex numbers. However, for
-the sake of simplicity we limit the scaling coefficients $L_{n}^{b},\,L_{n}^{s}$
-to a purely imaginary or real numbers. Even though that this simplified
+the sake of simplicity, we limit the scaling coefficients $L_{n}^{b},\,L_{n}^{s}$
+to purely imaginary or real numbers. Even though this simplified
 approach can potentially result in a sub-optimal performance in fading
@@
 $P_{e}^{\mathrm{FER}}$ denotes the frame error rate. Due to the system
-symmetry we evaluate the throughput of $S_{A}\to D_{A}$ only. We
+symmetry, we evaluate the throughput of $S_{A}\to D_{A}$ only. We
 set the frame length to $M=768$ symbols (to match the HW evaluation)
@@
 constellations at the relays; more details about the impact of asynchronism
-in WNC can be found in \cite{Diwine_D512}. Furthermore an Ettus Octoclock
+in WNC can be found in \cite{Diwine_D512}. Furthermore, an Ettus Octoclock
 clock distribution system \cite{Ettus_OctoClock} is used to provide
@@
 is fairly static, without fading, thus mimicking the channel used
-in the theoretical work. Moreover as cabled synchronisation is used,
+in the theoretical work. Moreover, as cabled synchronisation is used,
 it is desirable to minimize the cable length. Low SNRs are achieved
@@
 in Fig.~\ref{fig:CTUpp_SNR_map_BC15-17-20-25}. Several interesting
-phenomenas can be again observed in the figure:
+phenomena can be again observed in the figure:
 \begin{itemize}
@@
 of the actual SNR conditions in the system. However, we mostly omit
-the explicit notation in the following text for to aid readability.
+the explicit notation in the following text to aid readability.
 
@@
 channel between a source and its desired destination is present (see
-Fig.~\ref{fig:CTUpp_DirectChannel}). Even though that this \textquotedbl{}direct\textquotedbl{}
+Fig.~\ref{fig:CTUpp_DirectChannel}). Even though this \textquotedbl{}direct\textquotedbl{}
 channel can be relatively weak, it inevitably affects the destinations'
-HSI observations. In addition to this, we analyse the system where
+HSI observations. In addition to this, we analyze the system where
 source phase pre-rotation is switched off (or ineffective due to rapid
@@
 no direct source$\rightarrow$destination channels, perfect channel
-phase pre-rotation), in the HW measurements we now let all data communication
+phase pre-rotation), in the HW measurements we now allow all data communication
 to be performed through real wireless channels (compare with the HW
@@
 \begin{itemize}
-\item The presence of direct links requires only a slightly increased values
+\item The presence of direct links requires only slightly increased values
 of ($\gamma_{{\rm {MAC}}},\gamma_{{\rm {HSI}}}$, $\gamma_{{\rm {BC}}}$)
@@
 $f(d_{A},d_{B})=d_{A}\oplus d_{B}$ and HSI channels are necessary to retrieve the desired
-information at both sources, that is the traditional network coding approach (see Figure
+information at both sources. This is the traditional network coding approach (see Figure
 \ref{fig:CTUpp_ref3stepNC}).
 
-The second scenario is equivalent to a conventional routing, where the sources subsequently transmit
-their data packet towards the relay. Relay then sends a complete source information (no NC coding is
+The second scenario is equivalent to conventional routing, where the sources subsequently transmit
+their data packet towards the relay. The relay then sends complete source information (no NC coding is
 applied) and thus the HSI channels are completely ignored (see Figure \ref{fig:CTUpp_ref3stepRouting}).
@@
 \subsubsection{Implementation Details for Reference Scenarios}
-To provide a fair comparison, in both reference scenarios we assume that the sources transmit at
-double power, as they transmit time is essentially halved when compared with the 2-step scenarios.
+To provide a fair comparison, in both reference scenarios we assume that the sources transmit with
+twice the power, as their transmit time is essentially halved when compared with the 2-step scenarios.
 We assume QAM($N$) constellation and adaptively look for $N, r$ maximizing the throughput as in the
@@
 \subsubsection{Maximum Transmission Rates for the Three-Step Reference Scenarios}
-The theoretical limits for the considered 3-step scenarios can be easily derived (see
+The theoretical limits for the considered 3-step scenarios can easily be derived (see
 \cite{Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}) as
@@
 \end{eqnarray}
-where $\mathrm{CA}(\gamma)=\log_2(1+\gamma)$ denotes conventional point to point channel capacity for Gaussian
-channel \cite{Cover-Thomas_ElemInfTheory}.
+where $\mathrm{CA}(\gamma)=\log_2(1+\gamma)$ denotes the conventional point-to-point channel capacity for Gaussian
+channels \cite{Cover-Thomas_ElemInfTheory}.
 
@@
   \item The proposed adaptive constellation design from Section \ref{sub:Maximal-Throughput-of} 
-  with based on the optimized tuple ($r_b, r_s, N_b, N_s$) for each measured point
+  based on the optimized tuple ($r_b, r_s, N_b, N_s$) for each measured point
   (HW-pre-rotation on).
-  \item The proposed adaptive constellation design with violated assumptions (pre-rotation off).
+  \item The proposed adaptive constellation design with assumptions violated (pre-rotation off).
   \item Both 3-step reference scenarios introduced in Section \ref{Sec:Reference-3step-models}.
@@
   framework significantly outperforms both reference 3-step scenarios as well the corresponding
-  theoretical limits even if the pre-rotation is off! The bottleneck for the 3-step routing is BC
-  channel, because it needs to pass twice amount of data from relay to destinations compared to
+  theoretical limits even if the pre-rotation is off! The bottleneck for the 3-step routing is the BC
+  channel, because it needs to pass twice the amount of data from relay to destinations compared to
   all other schemes. The 3-step NC approach does not suffer from this and therefore its performance
@@
   \item Strong BC channel refers (among others) to a case with high relay power. The result is shown
-  in Figure \ref{fig:CTUpp_comparison-schemab}. The 3-step routing works much better compared to the previous
-  case, because of the strong BC channel. The conventional 3-step network coding suffers from weak
+  in Figure \ref{fig:CTUpp_comparison-schemab}. The 3-step routing works much better when compared to the previous
+  case, because of the strong BC channel. The conventional 3-step network coding scheme suffers
+  with a weak
   HSI channel. The proposed design again significantly outperforms both reference 3-step scenarios.
-  We should stress, that the performance gain is also caused by a \emph{partial usage} of the weak
+  We should stress, that the performance gain is also achieved with \emph{partial usage} of the weak
   HSI channel.
@@
 $\gamma_{\mathrm{BC}}\approx\gamma_{\mathrm{MAC}}$ and
-$\gamma_{\mathrm{HSI}}\approx\gamma_{\mathrm{MAC}}$+3dB. The numbers in boxes correspond with a
+$\gamma_{\mathrm{HSI}}\approx\gamma_{\mathrm{MAC}}$+3dB. The numbers in boxes correspond with 
 particular values (first row:$(N_b, r_b)$, second row:$(N_s, r_s)$) 
@@
 $\gamma_{\mathrm{HSI}}\approx\gamma_{\mathrm{MAC}}$-1dB.
-The numbers in boxes correspond with a
+The numbers in boxes correspond with 
 particular values (first row:$(N_b, r_b)$, second row:$(N_s, r_s)$)
@@
 the adaptive constellation mapping scheme. The viability of the proposed
-constellation design was verified by a means of numerical analysis
-and simulations and also by a real-world HW experiment (based on Ettus
+constellation design was verified by means of numerical analysis,
+ simulations and through real-world HW experiments (based on Ettus
 Research USRPs), including a HW-based robustness analysis.

### 2017-05-31 response_letter/response_letter.tex
pre-release versio

@@
   Within this design, we consider two building blocks  for multiple access channel, that is: 
-  i) orthogonal constellation design enabling resulting to non-overlapping superimposed
+  i) orthogonal constellation design forming a non-overlapping superimposed
   constellation in the receiving node enabling joint (full) decoding and ii) hierarchical
@@
   network function of the data can be recovered (not both individual data streams). Finally, one
-  needs to properly combine the aforementioned building blocks.
+  needs to properly combine the aforementioned building blocks by means of superposition coding.
 
@@
   For generalization to more sources, some way to preserve join decodability must be found, for
-  instance additional resources.  
-  The hierarchical design depends on a particular
-  network function (exclusive OR in our case). The goal is the received constellation with maximal
-  minimum distance between the \emph{network coded data}, where overlaps within the network function
+  instance additional resources. The hierarchical design depends on a particular
+  network function (exclusive OR in our case). The goal is a received constellation with maximal
+  free distance between the \emph{network coded data}, where overlaps within the network function
   are allowed. Actually these overlaps enable to improve the minimal distance compared to the
@@
   composition of properly scaled BPSK constellations, the constellations are fully determined by 
-  scaling level for individual bit streams.
+  scaling levels\footnote{Determination of those levels can be found in Algorithm 1, line 3 for
+  superposed part and lines 6,7 for basic part.} for individual bit streams.
 
@@
   small collection of  SNR tuples in the new section 7.4 (Figures 20, 21), but we would be 
-  careful to fix the parameters $(N_b, N_s, r_b r_s)$ purely according to the SNR triplet in 
+  careful to fix the parameters $(N_b, N_s, r_b, r_s)$ purely according to the SNR triplet in 
   other experiment.
@@
   step. We have already some initial results available, because we face efficiently to the fading
-  channel without the pre-rotation, where the amplitude is close (but not equal) to 1.   
+  channel without the pre-rotation, where the amplitude of the fading coefficients related to the sources
+  to relay links is almost (but not completely) equal\footnote{It can be not intuitive that the
+  superimposed constellation is determined by relative fading given by the ratio $h=h_A/h_B$ in the 2-step
+  setup. The absolute value of fading coefficients can be equally modelled by a corresponding SNR
+  value modification.}.   
   A more detailed analysis of the proposed constellation design in fading channels is postponed for further work.

### 2017-05-31 response_letter/response_letter.tex
some corrections in response letter

@@
 \usetikzlibrary[arrows,decorations.pathmorphing,backgrounds,positioning,fit,petri]
+%\usepackage{lineno}
+%\linenumbers
 
@@
 First of all, we would like to thank all the reviewers for their valuable comments and suggestions
-that help to improve our manuscript. We first reply
+that have helped to significantly improve our manuscript. We first reply
 to the most common and important questions and then we answer the individual questions and comments
@@
   and we supplement additional HW evaluation results for the adaptive system in the whole range of
-  observed channel SNRs. Again, a close agreement between the analytic and measurement results is shown.
+  observed channel SNRs. Again, close agreement between the analytic and measurement results is shown.
   \item We show how the channel coding can be integrated into the proposed constellation design, including the cut-set bound analysis of proper source transmission rates, which provides a hint for the setup of all channel encoders' rates in the system.
@@
   \item We perform a simple robustness analysis, demonstrating that the proposed modulation and
-  coding strategy is viable even in the case when the real-world conditions induce some deviations from the mathematical system model assumed in the paper.
+  coding strategy is viable even in the case when real-world conditions induce some deviations from the mathematical system model assumed in the paper.
   \item We conducted a comparison with the state of the art reference scenarios (traditional network
@@
 
-  Within this new section, we shown that
+  In this new section, we show that
   the HW implementation of the proposed adaptive constellation design outperforms the reference
@@
   design without pre-rotation is very important, because the
-  pre-rotation stands for a serious implementation challenge requiring the feedback channel. Finally we shown that the
+  pre-rotation represents a serious implementation challenge, requiring channel feedback. Finally we shown that the
   performance of the proposed framework is even above the corresponding 3-step reference theoretical limits.
@@
   that the manuscript will be transformed to the EURASIP template prior to publishing and there will
-  be time for fine tuning.
+  be time for fine-tuning.
 \end{itemize}
@@
   Generalization}
-  \item A4: We answer this question in two levels. We split the problem to 1) the wireless
+  \item A4: We answer this question in two parts. We split the problem to 1) wireless
   aware network coding, that is to determine the information flow within the network
-  \cite{Uricar-Hynek-Prochazka-Sykora_2013} and 2) the particular constellations 
+  \cite{Uricar-Hynek-Prochazka-Sykora_2013} and 2) the particular constellation 
   design suited for a given information stream. Note that the motivation can be found also in
@@
   cases, when a) all information is passed through the relay b) maximal information is passed
-  through the site links as it is explained in \cite{Prochazka_Tutorial_WNC}. Finding a proper
-  network information flow within a general wireless network can be a nutshell. Intuitively, the
+  through the side links as is explained in \cite{Prochazka_Tutorial_WNC}. Intuitively, the
   wireless network paradigm should be exploited as much as possible due to its higher spectral
   efficiency. To the best of our knowledge, no such approach is available for a general network
-  in the current state of the art. The random network coding does not take advantage to be 
-  "wireless aware" due to its randomness. There remains a white space for research to bring light
-  into a proper network information flow design within a general network.
+  in the current state of the art. Random network coding cannot be 
+  "wireless aware" due to its randomness. There remains scope for searching proper network
+  information flow design within a general network.
 
@@
   the best possible constellation design across the nodes within the network for the given flow.
-  Within this design, we consider two building blocks  for multiple access channel, that is: 
+  Within this design, we consider two building blocks  for the multiple access channel, that is: 
   i) orthogonal constellation design forming a non-overlapping superimposed
-  constellation in the receiving node enabling joint (full) decoding and ii) hierarchical
-  constellation design allowing some overlaps in the received constellation, such that only a
+  constellation at the receiving node enabling joint (full) decoding and ii) a hierarchical
+  constellation design that allow some overlaps in the received constellation, such that only a
   network function of the data can be recovered (not both individual data streams). Finally, one
@@
 
-  In case of the orthogonal design, we chosen ASK source constellations mutually shifted by $\pi/2$
+  In case of the orthogonal design, we chose ASK source constellations mutually shifted by $\pi/2$
   to form the QAM constellation in the received node. This assumes exactly two transmitting nodes.
-  For generalization to more sources, some way to preserve join decodability must be found, for
-  instance additional resources. The hierarchical design depends on a particular
+  To generalize to more sources, some way to preserve join decodability must be found.
+  The hierarchical design depends on a particular
   network function (exclusive OR in our case). The goal is a received constellation with maximal
   free distance between the \emph{network coded data}, where overlaps within the network function
-  are allowed. Actually these overlaps enable to improve the minimal distance compared to the
-  orthogonal design. Since both ASK and the proposed hierarchical constellation can be written as
+  are allowed. Actually these overlaps allow an improvement in the minimal distance compared to the
+  orthogonal design. Since both ASK and the proposed hierarchical constellation can be written as a
   composition of properly scaled BPSK constellations, the constellations are fully determined by 
@@
 
-  Within the butterfly network, the orthogonal stream is called \emph{superposed} stream and the
-  hierarchical as \emph{basic} stream. Since the basic stream is needed in destinations, it is
-  placed at higher power level compared to the superposed stream. Please find Figures 3,4 in the
+  Within the butterfly network, the orthogonal stream is called the \emph{superposed} stream and the
+  hierarchical as the \emph{basic} stream. Since the basic stream is needed at the destinations, it is
+  given a higher power level compared to the superposed stream. Please find Figures 3,4 in the
   manuscript for demonstration of this composition.
 
-  Regarding to the generalization of the principle to a general network, one can of cause consider
-  with advantage the proposed building blocks or even try to generalize them for more than two
-  sources. A design of some useful rules for the proposed building block utilization in general 
-  network stands for a white space for further research. However one should also keep in mind that 
-  severity of the real world issues as the synchronization and pre-rotation would dramatically grow
-  with the network size.
+  Regarding the generalization of the principle to a general network, one can of course consider
+  the advantage of the proposed building blocks or even try to generalize them for more than two
+  sources. A design of some useful rules for the proposed building block utilization is an open
+  problem. In addition, one should also keep in mind that 
+  the severity of the real world issues such as synchronization and pre-rotation would dramatically grow
+  with network size.
 
@@
   \item A: The nomenclature is placed according to the EURASIP-author's guidelines. The HW
-  abbreviation was overlooked - it is now defined also in its first appearance within the text.
+  abbreviation was overlooked - it is now defined before its first appearance within the text.
 \end{itemize}
@@
   $N_b=1$, $N_s=1$ constellation as throughput gain compared to the zero-throughput QPSK, because
-  the proposed constellation design uses the site link and it should be rather compared with some
-  reference that is able to use the site link as well. For this purpose, the conventional wireless
-  network coding with BPSK constellation with nonzero throughput can be considered for instance,
-  however to keep the figure readable, we decided not to add another curve into the plot, because 
-  the BPSK performs similarly as  $(N_b=2, N_s=0)$ strategy already shown in the figures.
+  the proposed constellation design uses the side link and it should be rather compared with some
+  reference that is able to use the side link as well. For this purpose, the conventional wireless
+  network coding with a BPSK constellation with non-zero throughput can be considered for instance.
+  However, to keep the figure readable, we decided not to add another curve into the plot, because 
+  BPSK performs similarly to the  $(N_b=2, N_s=0)$ strategy already shown in the figures.
   Therefore the performance gain statement between $N_b=1$, $N_s=1$ and the
-  reference QPSK is omitted in Figures 6-9 in the revised manuscript. Check Figure 
-  \ref{Fig:Throughput_comparison}) in this response letter to see the change in the figure. 
+  zero-throughput reference QPSK is omitted in Figures 6-9 in the revised manuscript. Check Figure 
+  \ref{Fig:Throughput_comparison}) in this response letter. 
 \end{itemize}
@@
   difference. }
-  \item A: The channel quality index is 3-dimensional (MAC, BC and HSI) within our model. Although
+  \item A: The channel quality index is 3-dimensional (MAC, BC and HSI) in our model. Although
   its evaluation can be easily done according to the theoretical analysis, its practical impact is
   questionable, because of more degrees of freedom that comes into
-  the consideration in real scenario, like a particular channel code, violation of the idealistic symmetry 
+  consideration in real scenarios, like a particular channel code, violation of the idealistic symmetry 
   assumption, strength of the
   direct link, etc. Within our experiment, we manually found some "optimal" table values for a 
-  small collection of  SNR tuples in the new section 7.4 (Figures 20, 21), but we would be 
-  careful to fix the parameters $(N_b, N_s, r_b, r_s)$ purely according to the SNR triplet in 
-  other experiment.
+  small collection of  SNR tuples in the new section 7.4 (Figures 20, 21), but care should be taken
+  before applying the parameters $(N_b, N_s, r_b, r_s)$ directly to other experimental setups.
 \end{itemize}
@@
 If some initial results on the fading channel case can be added into the paper, it would be better.}
-  \item A: We agree that the investigation of the behavior in the fading channels is an important
-  step. We have already some initial results available, because we face efficiently to the fading
-  channel without the pre-rotation, where the amplitude of the fading coefficients related to the sources
+  \item A: We agree that the investigation of the behavior of fading channels is an important
+  step. We already have some initial results available for a fading
+  channel without pre-rotation (check green line in Figures 20, 21), where the amplitude of the fading coefficients related to the sources
   to relay links is almost (but not completely) equal\footnote{It can be not intuitive that the
@@
   value modification.}.   
-  A more detailed analysis of the proposed constellation design in fading channels is postponed for further work.
+  A more detailed analysis of the proposed constellation design in fading channels is an area for further work.
 \end{itemize}

### 2017-05-31 response_letter/response_letter.tex
Final version of response letter

@@
   in the current state of the art. Random network coding cannot be 
-  "wireless aware" due to its randomness. There remains scope for searching proper network
+  "wireless aware" due to its randomness. There remains scope for researching proper network
   information flow design within a general network.
@@
   constellation at the receiving node enabling joint (full) decoding and ii) a hierarchical
-  constellation design that allow some overlaps in the received constellation, such that only a
+  constellation design that allows some overlaps in the received constellation, such that only a
   network function of the data can be recovered (not both individual data streams). Finally, one
@@
   Within the butterfly network, the orthogonal stream is called the \emph{superposed} stream and the
-  hierarchical as the \emph{basic} stream. Since the basic stream is needed at the destinations, it is
+  hierarchical is called the \emph{basic} stream. Since the basic stream is needed at the destinations, it is
   given a higher power level compared to the superposed stream. Please find Figures 3,4 in the
@@
   the advantage of the proposed building blocks or even try to generalize them for more than two
-  sources. A design of some useful rules for the proposed building block utilization is an open
+  sources. A design of some useful rules for the proposed building block utilization in a
+  generalized network is an open
   problem. In addition, one should also keep in mind that 
-  the severity of the real world issues such as synchronization and pre-rotation would dramatically grow
+  the severity of the real-world issues such as synchronization and pre-rotation would dramatically grow
   with network size.

### 2017-05-31 Const_design_final.tex
Resubmission

@@
 
+\graphicspath{{fig/}}
+
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
@@
 conditions induce some deviation from the assumed system model.
+\item We compare the proposed design with state of the art reference scenarios to highlight its
+superior performance.
 \end{enumerate}
@@
 $P_{e}^{\mathrm{FER}}$ denotes the frame error rate. Due to the system
-symmetry we evaluate the throughput of $S_{A}\to D_{A}$ only. We
+symmetry, we evaluate the throughput of $S_{A}\to D_{A}$ only. We
 set the frame length to $M=768$ symbols (to match the HW evaluation)
 and the relay output mapper $\mathcal{A}^{R}$ will be defined as
-a conventional ($2^{N_{b}+2N_{s}}$$)$-QAM constellation. All performance
+a conventional $(2^{N_{b}+2N_{s}})$-QAM constellation. All performance
 metrics in the symmetric WBN are evaluated as a function of the actual
@@
 
+\begin{figure*}
+\caption{Robustness analysis for two fixed $(N_{b},N_{s},r_{b},r_{s})$ scenarios.
+\label{fig:CTUpp_Robustenss_analysis}}
+\end{figure*}
+
+\subsection{Benchmarking with the State of the Art Three-Step Scenarios}
+For a more advanced comparison of the proposed method, we consider two conventional \emph{3-step}
+communication scenarios.
+
+\subsubsection{Reference Three-Step Scenarios}\label{Sec:Reference-3step-models}
+In the first scenario both sources transmit their information one by one, but the relay is
+allowed to combine the received (fully decoded) data packets into the network coded packet
+$f(d_{A},d_{B})=d_{A}\oplus d_{B}$ and HSI channels are necessary to retrieve the desired
+information at both sources. This is the traditional network coding approach (see Figure
+\ref{fig:CTUpp_ref3stepNC}).
+
+The second scenario is equivalent to conventional routing, where the sources subsequently transmit
+their data packet towards the relay. The relay then sends complete source information (no NC coding is
+applied) and thus the HSI channels are completely ignored (see Figure \ref{fig:CTUpp_ref3stepRouting}).
+
+\subsubsection{Implementation Details for Reference Scenarios}
+To provide a fair comparison, in both reference scenarios we assume that the sources transmit with
+twice the power, as their transmit time is essentially halved when compared with the 2-step scenarios.
+We assume QAM($N$) constellation and adaptively look for $N, r$ maximizing the throughput as in the
+proposed Section \ref{sub:Maximal-Throughput-of}.
+
+\subsubsection{Maximum Transmission Rates for the Three-Step Reference Scenarios}
+The theoretical limits for the considered 3-step scenarios can easily be derived (see
+\cite{Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}) as
+\begin{eqnarray}
+  r^{\mathrm{3step}}_{\mathrm{route}} &\le& \min\left\{\frac{2\mathrm{Ca}(\gamma_{MAC})}{2},\frac{2\mathrm{Ca}(\gamma_{BC})}{2}\right\}\label{eq:cap3strout}\\
+  r^{\mathrm{3step}}_{\mathrm{NC}} &\le& \min\left\{\frac{2\mathrm{Ca}(2\gamma_{MAC})}{2},\frac{2\mathrm{Ca}(\gamma_{HSI})}{2}, \mathrm{Ca}(\gamma_{BC})\right\},\label{eq:cap3stNC}
+\end{eqnarray}
+where $\mathrm{CA}(\gamma)=\log_2(1+\gamma)$ denotes the conventional point-to-point channel capacity for Gaussian
+channels \cite{Cover-Thomas_ElemInfTheory}.
+
+These bounds serve as an initial step for the tuple (rate, alphabet cardinality) optimization as in
+Section \ref{Sec:Transmission_Rates} but also as an ultimate theoretical bound of the individual
+reference strategies.
+
+\begin{figure}
+\begin{centering}
+%\input{fig/2-SRN-sc_principle_BC-TWT_referenceB.eps_tex}
+\par\end{centering}
+
+\centering{}\caption{Three-step reference scenario with conventional network coding.\label{fig:CTUpp_ref3stepNC}}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\par\end{centering}
+
+\centering{}\caption{Three-step reference scenario with conventional routing.\label{fig:CTUpp_ref3stepRouting}}
+\end{figure}
+
+\subsubsection{Numerical Results}
+Within this experiment, we evaluated the following situations on our \emph{USRP platform}:
+\begin{itemize}
+  \item The proposed adaptive constellation design from Section \ref{sub:Maximal-Throughput-of} 
+  based on the optimized tuple ($r_b, r_s, N_b, N_s$) for each measured point
+  (HW-pre-rotation on).
+  \item The proposed adaptive constellation design with assumptions violated (pre-rotation off).
+  \item Both 3-step reference scenarios introduced in Section \ref{Sec:Reference-3step-models}.
+  \item Fundamental theoretical limits for the conventional reference 3-step scenarios.
+\end{itemize}
+In all measured cases, we manually selected the tuple maximizing the throughput. Our starting
+point was the theoretical analysis, but this analysis does not take into account the imperfect
+channel code and available discrete channel code rates (0.4, 0.5, \dots, 0.9). We also considered
+$N_b
+\le 2$, $N_s \le 1$ for simplicity\footnote{The higher order strategies like $(N_b=4, N_s=0)$
+performed similarly as considered $(N_b=2, N_s=1)$ in our simulations. Note that much stronger
+solution based
+on the modulo-sum channel coding and wireless network coding function is available
+\cite{Prochazka-2016}, nevertheless implementation of the 
+non-binary channel code suitable for the USRP is challenging.}.
+
+We considered two setups:
+\begin{itemize}
+  \item Strong HSI and equal MA and BC. This scenario is suited for standard wireless network
+  coding, because it can efficiently utilize the strong HSI channel. See Figure
+  \ref{fig:CTUpp_comparison-schemaa} for the corresponding result. As one can see, the proposed
+  framework significantly outperforms both reference 3-step scenarios as well the corresponding
+  theoretical limits even if the pre-rotation is off! The bottleneck for the 3-step routing is the BC
+  channel, because it needs to pass twice the amount of data from relay to destinations compared to
+  all other schemes. The 3-step NC approach does not suffer from this and therefore its performance
+  is a bit better, nevertheless we pay for orthogonality in the MA stage. The performance
+  of the proposed framework is superior to both reference models.
+  \item Strong BC channel refers (among others) to a case with high relay power. The result is shown
+  in Figure \ref{fig:CTUpp_comparison-schemab}. The 3-step routing works much better when compared to the previous
+  case, because of the strong BC channel. The conventional 3-step network coding scheme suffers
+  with a weak
+  HSI channel. The proposed design again significantly outperforms both reference 3-step scenarios.
+  We should stress, that the performance gain is also achieved with \emph{partial usage} of the weak
+  HSI channel.
+\end{itemize}
+
+The saturation of the reference 3-step strategies for high SNRs is a consequence of weaker
+performance of the underlaying channel code, where the rate of the code is adjusted by means of
+puncturing technique.
+
+\begin{figure}
+\begin{centering}
+\par\end{centering}
+\centering{}\caption{Performance comparison for the setup
+$\gamma_{\mathrm{BC}}\approx\gamma_{\mathrm{MAC}}$ and
+$\gamma_{\mathrm{HSI}}\approx\gamma_{\mathrm{MAC}}$+3dB. The numbers in boxes correspond with 
+particular values (first row:$(N_b, r_b)$, second row:$(N_s, r_s)$) 
+achieving a given maximal throughput. 
+\label{fig:CTUpp_comparison-schemaa}}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\par\end{centering}
+\centering{}\caption{Performance comparison for the setup
+$\gamma_{\mathrm{BC}}\approx\gamma_{\mathrm{MAC}}$+5dB and
+$\gamma_{\mathrm{HSI}}\approx\gamma_{\mathrm{MAC}}$-1dB.
+The numbers in boxes correspond with 
+particular values (first row:$(N_b, r_b)$, second row:$(N_s, r_s)$)
+achieving a given maximal throughput.
+\label{fig:CTUpp_comparison-schemab}}
+\end{figure}
+
 \section{Conclusions and Future Work\label{sec:CTUpp_DiscussionConclusions-etc}}
@@
 require some modifications of the adaptive system design.
-\begin{figure*}
-\caption{Robustness analysis for two fixed $(N_{b},N_{s},r_{b},r_{s})$ scenarios.
-\label{fig:CTUpp_Robustenss_analysis}}
-\end{figure*}
 

### 2017-05-31 all_figures.tex
Resubmission

@@
 \documentclass{article}
-\usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
-\usepackage{array}
-\usepackage{float}
-\usepackage{units}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage[dvips]{graphicx}
-\usepackage{tikz}
-\usetikzlibrary[arrows,calc,decorations.pathmorphing,backgrounds,positioning,fit,petri,shapes,decorations.markings]
-\usepackage{pgfplots}
+\usepackage{graphicx}
 \newcommand{\lyxdot}{.}
-
 \begin{document}
 \begin{figure}
-\centering{}\includegraphics[width=0.6\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_v4}
+\centering{}
+\includegraphics[width=0.6\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_v4}
 \caption{Symmetric WBN model with half-duplex constraint and 2-phase communication.\label{fig:CTUpp_Information_flows}}
@@
 \begin{figure*}
-\centering{}\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_coding_Gain7\lyxdot 5}~~~\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_coding_Gain15\lyxdot 0}\caption{Throughput enhancement $\Delta T_{C}=T_{C}^{\mathrm{max}}-T_{\mathrm{LB}}$
-{[}bits/channel use{]} of the coded over uncoded WBN system for $\gamma_{{\rm {BC}}}=7.5\,\mathrm{dB}$
+\centering{}
+\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_coding_Gain7\lyxdot 5}~~~
+\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_coding_Gain15\lyxdot 0}
+\caption{Throughput enhancement $\Delta T_{C}=T_{C}^{\mathrm{max}}-T_{\mathrm{LB}}$
+[bits/channel use] of the coded over uncoded WBN system for $\gamma_{{\rm {BC}}}=7.5\,\mathrm{dB}$
 and $\gamma_{{\rm {BC}}}=15\,\mathrm{dB}$. Note that $0.75\leq\Delta T_{C}\leq2$
@@
 
+\begin{figure}
+\begin{centering}
+%\includegraphics[width=0.75\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_referenceB}
+\includegraphics[width=0.75\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_referenceB}
+%\input{fig/2-SRN-sc_principle_BC-TWT_referenceB.eps_tex}
+\par\end{centering}
+
+\centering{}\caption{Three-step reference scenario with conventional network coding.\label{fig:CTUpp_ref3stepNC}}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.75\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_referenceB1}
+\par\end{centering}
+
+\centering{}\caption{Three-step reference scenario with conventional routing.\label{fig:CTUpp_ref3stepRouting}}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.75\columnwidth]{fig/scheme_a}
+\par\end{centering}
+\centering{}\caption{Performance comparison for the setup
+$\gamma_{\mathrm{BC}}\approx\gamma_{\mathrm{MAC}}$ and
+$\gamma_{\mathrm{HSI}}\approx\gamma_{\mathrm{MAC}}$+3dB. The numbers in boxes correspond with 
+particular values (first row:$(N_b, r_b)$, second row:$(N_s, r_s)$) 
+achieving a given maximal throughput. 
+\label{fig:CTUpp_comparison-schemaa}}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.75\columnwidth]{fig/scheme_b}
+\par\end{centering}
+\centering{}\caption{Performance comparison for the setup
+$\gamma_{\mathrm{BC}}\approx\gamma_{\mathrm{MAC}}$+5dB and
+$\gamma_{\mathrm{HSI}}\approx\gamma_{\mathrm{MAC}}$-1dB.
+The numbers in boxes correspond with 
+particular values (first row:$(N_b, r_b)$, second row:$(N_s, r_s)$)
+achieving a given maximal throughput.
+\label{fig:CTUpp_comparison-schemab}}
+\end{figure}
+
 \end{document}

### 2017-05-31 scripts/extractor.py

@@ -1,6 +1,6 @@
-infile = open('Const_design.tex', 'r')
-outfile_fig = open('all_figures.tex', 'w')
-outfile_tab = open('all_tables.tex', 'w')
+infile = open('../Const_design.tex', 'r')
+outfile_fig = open('../all_figures.tex', 'w')
+outfile_tab = open('../all_tables.tex', 'w')
 extract_block_fig = False
 extract_block_tab = False
 for line in infile:

### 2017-05-31 scripts/fig_remover.py

@@ -1,5 +1,5 @@
-infile = open('Const_design.tex', 'r')
-outfile = open('Const_design_final.tex', 'w')
+infile = open('../Const_design.tex', 'r')
+outfile = open('../Const_design_final.tex', 'w')
 fig_list = open('fig_list', 'w')
 for line in infile:
     if not 'includegraphics' in line:
